### 2015-03-06 text/research_paper.tex
Try including research paper text into this code base

\documentclass[11pt,a4paper,fleqn]{article}

\usepackage{graphicx,hyperref,amsmath,natbib,bm,url}
\usepackage[utf8]{inputenc} % include umlaute

% -------- Define new color ------------------------------
\usepackage{color}  
\definecolor{darkblue}{rgb}{0.15,0,0.37}
\definecolor{darkred}{rgb}{0.35,0,0.08}
% --------------------------------------------------------

\hypersetup{
colorlinks=true,
hypertexnames=false,
colorlinks,		
linkcolor={black},
citecolor={black},
urlcolor={black},
%ocgcolorlinks, % this option changes the link color to black when the document is printed, for legibility in b/w 
pdfstartview={FitV},
unicode,
breaklinks=true
} 
\usepackage{verbatim} %to be able to comment out by using begin{comment} and end{comment}

\usepackage{microtype,todonotes}
\usepackage[australian]{babel} % change date to to European format
\usepackage[a4paper,text={16.5cm,25.2cm},centering]{geometry} % Change page size
\setlength{\parskip}{1.2ex} % show new paragraphs with a space between lines
\setlength{\parindent}{0em} % get rid of indentation for new paragraph
\clubpenalty = 10000 % prevent "orphans" 
\widowpenalty = 10000 % prevent "widows"

\usepackage{mathpazo} % change font to something close to Palatino

\usepackage{longtable, booktabs, tabularx} % for nice tables
\usepackage{caption,fixltx2e}  % for nice tables
\usepackage[flushleft]{threeparttable}  % for nice tables

\newcommand*{\myalign}[2]{\multicolumn{1}{#1}{#2}} % define new command so that we can change alignment by hand in rows

% -------- For use in the bibliography -------------------
\usepackage{multicol}
\usepackage{etoolbox}
\usepackage{relsize}
\setlength{\columnsep}{1cm} % change column separation for multi-columns
\patchcmd{\thebibliography}
  {\list}
  {\begin{multicols}{2}\smaller\list}
  {}
  {}
\appto{\endthebibliography}{\end{multicols}}
% --------------------------------------------------------

\usepackage[onehalfspacing]{setspace} % Line spacing

\usepackage[marginal]{footmisc} % footnotes not indented
\setlength{\footnotemargin}{0.2cm} % set margin for footnotes (so that the number doesn't stick out)

% -------- Define new line for tables --------------------
\usepackage{array}
\makeatletter  % make line thicker for the table
\newcommand{\thickhline}{%
    \noalign {\ifnum 0=`}\fi \hrule height 1pt
    \futurelet \reserved@a \@xhline
}
\newcolumntype{"}{@{\hskip\tabcolsep\vrule width 1pt\hskip\tabcolsep}}
\makeatother
% --------------------------------------------------------

\usepackage{pdflscape} % for landscape figures

\usepackage[capposition=top]{floatrow} % For notes below figure

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%Title %%%%%%%%%%%%%%%%%%%%%
\vspace*{2cm}

\thispagestyle{empty}

\begin{center}
\thispagestyle{empty}
{\huge Labor Demand Effects of Automation:\\[0.2cm] Developing a New Indicator of Automation \\[0.2cm] Based on Patent Text Search}\\[1cm]
\begin{tabular}{l@{\hskip 0.6in}l}
\textbf{{\large Katja Mann}} & \textbf{{\large Lukas Püttmann}}\\
{\small University of Bonn} & {\small University of Bonn}\\
{\small katja.mann@uni-bonn.de} & {\small lukas.puettmann@uni-bonn.de}\\
\end{tabular}\\[0.7cm]
{\large \today}\\[0.7cm]
\end{center}

\vspace*{1.1cm}
\begin{center}
\begin{minipage}{0.65\textwidth}
\textbf{Abstract.} We propose to develop a new industry-level indicator of automation based on searching patent grant texts for keywords. We show the feasibility of such a project by searching the text of all 5.5 mio. patents granted by the U.S. Patent Office from 1976-2015 for words containing the stem ``automat". The 6.9 mio. such matches exhibit a strong and robust upward trend in absolute and relative terms. We are able to match 40 percent of patents up to 2006 with industries through information on the firms being granted a patent. We aim to improve this exploratory first analysis along several dimensions: by refining our search algorithm, by matching patents to industries through existing patent classifications and by potentially extending the coverage back until 1920. We suggest several research avenues to put our new indicator to use: to contribute to the discussion on automation and reshoring and to test if sector-level technological progress in automation has led to changes in employment in such sectors.
\end{minipage}
\end{center}

%\newpage
%\tableofcontents

\newpage
\section{Introduction}
The rapid technological change of the recent decades has fundamentally altered production processes: it is becoming more widespread to use machines for tasks previously executed by humans. This process has long since attracted the interest of economists. In labor economics, researchers try to assess the effects of automation on labor demand, wages and employment.

In order to carry out meaningful economic analyses on those topics, good measure of automation are needed. So far, research has often equated automation with routinization, arguing that computers and machines are good at carrying out tasks that require little variation, while they fail at complex analytic or manual tasks. A widespread index of automation, proposed by \cite{ALM2003} and further refined by various authors, e.g. \cite{AKK2008} and \cite{AD2013}, uses data on occupational titles (e.g. by the U.S. Occupational Information Network (O*NET) database). However, using the routine task content of a specific occupation as a measure for automation is problematic for several reasons: first, it is purely static, and builds on present-day knowledge on which tasks are automizable. Routine-task indices enable researchers to assess which tasks can be replaced by machines given the level of technological progress that we observe today, but they do not allow for predictions about future automation and its likely effects. Second, there is no way of knowing whether those occupations that experts consider routinizable are indeed prone to be replaced by machines. Whether or not automation is actually carried out depends on many things other than pure technical feasibility, e.g. on cost considerations of firms or on research and development efforts.

We propose to develop a new industry-level indicator of automation based on searching patent grant texts for keywords, which promises to remedy several of these shortfalls. Patents are an objective and transparent measure of technological progress and records on U.S. patent grant texts exist since 1790. This could potentially allow us to test how changes in the technology frontier on automation in an industry affect jobs in that industry.

We illustrate the feasibility of such a project by searching the text of all 5.5 mio. patents granted by the U.S. Patent Office from 1976-2015 for words containing the stem ``automat". The 6.9 mio. such matches exhibit a strong and robust upward trend. We are currently able to match patents with industries drawing on work by \cite{HJT2001} who match patents with the firms that are granted the patents. We aim to improve our matching by using the existing highly detailed technological classifications which link patents to around 400 technical classes and roughly 150'000 subclasses.

To put our new indicator to use in the field of labor economics, we suggest several research avenues: to investigate the effects of sector-level technological progress in automation on employment, and, complementing the automation indicator with indices of offshoring, to contribute to the discussion on reshoring, the relocation of previously offshored production back to the home country.

In what follows, we first present some background information on the use of patent grant texts as an indicator of technological progress, before describing how we construct our automation index based on this data source. We then explain how we assign patents to different industries. In the last part, we propose different research questions that could be answered with the help of the new indicator, and show how these projects could be carried out.

\section{Patent Grant Texts as an Indicator of Technological Progress}
Patent grant texts are a rich publicly-available data source that allows for a measure of technological progress. Patent grant texts are highly standardized and applicants have incentives to provide exact and correct information about their innovations. In return for disclosing the content of the innovation to the public, a temporary intellectual property right is granted.

The patent grant document includes the patent number, the name of the inventor, date, the patent classification, citations to other patents, an abstract, (most importantly) a description and a range of other legal information and drawings, all of which data that can be searched and analyzed.

We are not the first to analyze patent data: \cite{HJT2001} provide data on patent citations and link those to publicly-traded firms on Compustat. A number of papers, such as \cite{AAC2014} and \cite{ABP2015} have made use of patent citations. However, contrary to those papers, we concentrate on the patent's \textit{content}, not on its relation to other patents. As \citep[p.~290]{MVS2010} note, 
\begin{quotation} 
``[...] the majority of studies and analyses undertaken in [patent and publication text search] focus on mere counts and/or quantitative attributes of relevant documents (e.g. number of publications, patents, number of references, number of citations); less attention is paid to analysis in which the content of the underlying documents is the focal point of attention."
\end{quotation}

Text mining and search is starting to be more widely used in empirical social science. \cite{BBD2013} search newspaper articles to measure economic policy uncertainty. \cite{GS2010} analyze search newspapers  for phrases to measure political slant. Advantages of patent texts over newspaper articles are the greater standardization, the incentive to deliver correct information, the precise technical nature allowing for measures of technology and easy public access to these documents. \cite{HMP2014} apply measures of similarities of speak developed in computational linguistics to the records of decision making process of central banks.

In our first explorative analysis we concentrate on the number of appearances of the phrase ``autom", which brings matches such as ``automatic", ``automated", ``automatically" and ``automation". We interpret this as a proxy for the contribution of a patent of enabling the automation of tasks. We admit that this measure is crude and aim to improve our search algorithm by including other phrases such as ``mechanic".

Another way to improve the quality of our matches could be to check for the text surrounding the match. If the surrounding text passages of a patent's matches are all highly alike, the number of matches might not carry much information on the how large the patent's contribution to automation is. As an example of this, look at patent  4649323 ``Microcomputer-controlled light switch" from 1987. Here ``automat" appears 26 times, but the term ``fade[r]" appears in the vicinity (next 2 words) of all of the matches. If the phrase, however, appears in a more diverse surrounding, this could be stronger indication of the patent's content being about automation. An example here would be patent 4648731 ``Error correction member positioning system for a printer" from 1987. In its patent grant text ``automat" appears 17 times, in all cases as ``automatically". The phrase appears in diverse settings such as ``automatically [forwarding, backspacing,  separating, backing, moved, returned]".

We could also take the origin of the applicant into account. Foreign applicants face significantly higher costs, so their patent might be assumed to be of higher value \citep{HS2005}.

\section{Construction of the Indicator}
\subsection{Data source}

The United States Patent and Trademark Office (USPTO) grants and administers patent applications for the United States. Patent grant texts are publicly available and searchable.\footnote{\href{http://patft.uspto.gov/netahtml/PTO/search-bool.html}{The USPTO provides a search interface for this at: \texttt{patft.uspto.gov/netahtml/PTO/search-bool.html}}} Google provides bulk downloads of patent information free of charge.\footnote{\href{www.google.com/googlebooks/uspto-patents.html}{\texttt{google.com/googlebooks/uspto-patents.html}}} The data include US, European and global patents.

Electronic records on patent grant texts exists since 1976. Grants from 1920 onwards have also been transferred to electronic format by optical character recognition. However, the recognition technology makes frequent mistakes, which could lead to wrong classifications. More likely it would lead to far fewer matches. In future work, these files might be included through an algorithm that corrects for mistakes.

There are several changes in the formatting of the files. Until 2001, the files are in ASCII plain text and thereafter in eXtensible Markup Language (XML). There is another formatting change after 2004.

\subsection{Implementation of search algorithm}
We obtain the full grant texts for all US patents of 1976-2015.\footnote{\href{http://www.google.com/googlebooks/uspto-patents-grants-text.html}{\texttt{google.com/googlebooks/uspto-patents-grants-text.html}}}  Every file contains the patents of one week starting Tuesday. The total size of the decompressed files is about 300 gigabytes.\footnote{\cite{F2013} provides some advice how to handle these files.}

We first construct a patent index by searching containing of each number's unique patent number, its position of appearance in the file and its technological classification. We then do a linear case-insensitive regular expression search for the stem ``automat'' for every patent grant text and record the number of matches. We disregard the order in which word in the corpus appear, but focus only on the word counts. This helps to identify \textit{what} a text covers, but now \textit{how}. Stemming our words of interest such as ``automation", ``automated", ``automatic" to ``automat" is a crude, but effective way of searching a large corpus of documents \citep{MRS2009}.

We do plausability checks of our matches by looking at the context in which matches appear. The scale of the search only allows for inspecting a relatively small number of matches. We do this once by searching by matches, e.g. match number 100, 101, and so on. We further randomly draw matches and look at the context in which the matches appear. This first superficial test shows that patents which include the expression ``automat'' provide a good indication of whether a patent contributes to the technological level of automation in a sector. Following \cite{BBD2013}, who use human auditors to check their results, in future analyses we could formalize such testing to ensure a high quality of matches. We exclude the name of the patent holder from our search corpus to eliminate a possible source of errors with names such as ``Automated Truck Systems Inc.''.\footnote{Actually, we have only been able to make this correction for patents until 2001. This biases our number of matches (very slightly) upwards after 2001. We plan to correct this.}

\subsection{Results}
In total, we identify around 5.5 mio. patents. Figure~\ref{fig:keyword_match_over_time} displays the number of weekly matches of the keyword ``automat" from 1976 to 2015. Over the whole period, we find around 6.9 mio. matches of ``automat'' in the patent grant texts. We can observe a clear upward trend from around 1500 matches in the 1970s and 1980s, 4000 around 2001 up to an average of 10100 matches by 2014.

\begin{figure}[tb]
\caption{Number of weekly matches of word stem ``automat" in US patents, 1976-2015}
	\centering
	\includegraphics[trim=1cm 0cm 0cm 0cm, clip=true, totalheight=0.38\textheight]{./figures/keyword_matches_weekly_1976-2015.pdf}
	\floatfoot{\textit{Note:} Every data point displays sum of matches from searching through one file of weekly patent grant texts; total identified patents: 5.5 mio.; total number of keyword matches: 6.9 mio.\\[0.1cm]
	\textit{Source:} USPTO, Google and own calculations.}
	\label{fig:keyword_match_over_time}
\end{figure}

Figure~\ref{fig:summary_stats} shows a summary of the matches. The increase in keyword matches could be due to the general increase in the number of patents (see panel A) from around 70'000 to 320'000 patents.

\begin{figure}[tb]
\caption{Number of identified patents, 1976-2014}
	\includegraphics[trim=0cm 0cm 1cm 0.5cm, clip=true, totalheight=0.25\textheight]{./figures/barchart_identified_patents_1976-2014.pdf}
	\label{fig:summary_stats}
	\floatfoot{\textit{Note:} Identified patents are those found through the search algorithm; the bottom darker-shade bars are the number of distinct patents with at least one match \\[0.1cm]
	\textit{Source:} USPTO, Google and own calculations.}
\end{figure}

However, the mean number of matches has also shifted upwards from around 0.93 to 1.6 (panel C). \footnote{The median is reliably at zero.} Panel D shows that this trend is robust when we exclude the top percentile of matches, which contains outliers of patents that have hundreds of matches. Figure~\ref{fig:match_per_nrpatents} plot the weekly average over average of the number of keyword matches per week which is upwards trending.

\begin{figure}[tb]
\caption{Weekly averages of number of average matches per patent, 1976-2015}
	\centering
	\includegraphics[trim=1cm 0cm 1cm 0cm, clip=true, totalheight=0.4\textheight]{./figures/match_over_nrpatents_weekly_1976-2015.pdf}
	\floatfoot{\textit{Note:} Every data point displays sum of matches from searching through one file of weekly patent grant texts divided by the number of identified patents for that week; the solid line is the HP-filtered trend with $\lambda = 100'000$; the size of markers corresponds to number of patents in week.\\[0.1cm]
	\textit{Source:} USPTO, Google and own calculations.}
	\label{fig:match_per_nrpatents}
\end{figure}

\subsection{Developing an index for automation}
We propose to develop a new sector-level index of automation based on the keyword search. The index should rise in the number of matches, but we want the marginal benefit of an additional match to decrease.  A possible candidate for such an index is $x_i = log(1+m_i)$, where $m_i$ are the number of keyword matches per patent and $x_i$ is the index assigned to patent $i$.

As a further option we could weigh this index by the number of times a patent has been cited by other patents using the data provided by \cite{HJT2001}, however correcting for the fact that older patents have been cited more often. Such a citation-weighted index could take the form $x_i = log(1+m_i) [1+log(1+\frac{c_i}{C_t})]$, where $c_i$ are the patent $i$'s citations over the whole period and $C_t$ are the total number of citations of patents in the same year over the whole period. A potential cost of including patent citations would be limiting the number of patents to the roughly 3 mio. patents and the time up to 2006 that \cite{HJT2001} (and later revisions) cover.

\section{Linking Patent Citations to Industries}
In order to use our patent data for economic analyses other than at the aggregate level, we need to match the patent classes with the industries where these patents are applied. In general, this is not an easy task since the same patent might be of use in various different industries. The industry to which the patent assignee belongs might not be informative in this context because many large companies - which are, in general, those companies most likely to innovate - are active in multiple different fields. Having warned about these possible shortcomings, we still believe that patent-industry matching yields meaningful insights.%\linebreak

There are two ways of doing this: The first is to use the patent's technical class to assign a patent to an industry. The USPTO provides a convergence table that links patent classes with NAICS industries, which has been compiled manually by trained analysts.\footnote{\href{http://www.uspto.gov/web/offices/ac/ido/oeip/taf/data/naics_conc/2013/read_me.txt}{\texttt{http://www.uspto.gov/web/offices/ac/ido/oeip/taf/data/naics\_conc}}} However, it only contains manufacturing industries, and their number is restricted to 26.

The alternative, which we choose for this first analysis, is to make use of the database developed by \cite{HJT2001}. For the years 1976-2006, the authors have matched about 70 percent of all patents granted by patent numbers with assignee names and the corresponding corporations in Compustat, which comprises all U.S. firms that are traded on the stock market. Using this information, we were able to match the Compustat identification number with the number of patent matches which we derived by our algorithm. We used information available on the Compustat website to match companies to NAICS industries.

\begin{figure}[tb]
	\caption{Automation index at first-digit NAICS, 1976-2006}
	\centering
	\includegraphics[trim = 0cm 0.4cm 0cm 0cm, clip=true, totalheight=0.45\textheight]{./figures/automation_naics_firstdigit.pdf}\\
	\floatfoot{\textit{Source}: USPTO, Google and own calculations.}
	\label{fig:automation_naics_firstdigit}
\end{figure}

Figure~\ref{fig:automation_naics_firstdigit} shows our automation index disaggregated for first-digit NAICS industries. As can be seen, the highest increase in automation was in the manufacturing and the IT, finance and real estate sector.

%Table \ref{table:industry_linked2matches2001} shows some examples of matched industries for 2001. This procedure can easily be extended to all years until 2006. In 2001, our automation index is defined for 470 NAICS industries. In 141 of these, no patents with keyword matches were granted.

\begin{comment}
\begin{table}
\begin{small}
  \begin{threeparttable}
    \caption{{\normalsize Examples of matched industries with patents, 2001}}
    \label{table:industry_linked2matches2001}
     \begin{tabular}{llr}
        \toprule
        \textbf{NAICS} & \textbf{Industry name} & \textbf{Number matches}  \tabularnewline
        \midrule
        334413	& Semiconductor and Related Device Manufacturing  & 6'867							\tabularnewline
        511219 	& Other Computer Related Services$^1$				& 6'418									\tabularnewline
        541512 	& Computer Systems Design Services				& 5'692									\tabularnewline
        \myalign{c}{\vdots}	& \myalign{c}{\vdots}			& 		\myalign{r}{\vdots}							\tabularnewline
        3335 	& Motor Vehicle Parts Manufacturing				& 2									\tabularnewline
        3363 	& Metalworking Machinery Manufacturing				& 1									\tabularnewline
        \myalign{c}{\vdots}	& \myalign{c}{\vdots}			& 		\myalign{r}{\vdots}							\tabularnewline
        3112 	& Grain and Oilseed Milling				& 0									\tabularnewline
        \myalign{c}{\vdots}	& \myalign{c}{\vdots}			& 		\myalign{r}{\vdots}							\tabularnewline
        \midrule
        	& Mean matches per industry  & 200.1							\tabularnewline
        	& Total matches linked to industries  & 94'046							\tabularnewline
        	& Total number of matches  & 231'514							\tabularnewline
        	& Share of matches linked to industries  & 41\%							\tabularnewline
        	& Total number of patents identified  & 184'172							\tabularnewline
        \bottomrule
     \end{tabular}
    \begin{tablenotes}
      \footnotesize
      \item $^1$includes software installation services and computer disaster recovery services 
      \item 	\textit{Source:} USPTO, Google and own calculations.
          \end{tablenotes}
  \end{threeparttable}
\end{small}
\end{table}
\end{comment}

\section{Comparison Automation Index - Routine Task Index}

We have described above how our automation index differs from the automation index that is most widely used in the literature, the Routine Task Index (RTI). We are interested in how these indices correlate. This can help us assess the quality of our index, as well as the new value it provides.\\
In order to compare the indices, it is necessary to aggregate the occupation-level RTI on the industry level. This task requires not only that we know which occupations are used in which industry; we also need to be able to weigh them according to their share in labor input in each industry.

To assign occupations to industries, we can make use of the surveys carried out by the U.S. Census Bureau. In the American Community Survey (ACS), the Current Population Survey (CPS), and the Survey of Income and Program Participation (SIPP), to name just the largest ones, survey participants provide information on their occupation as well as on the industrial sector where they work. The Census Bureau has processed this information to generate correspondence tables. The industrial classification used by the Census Bureau is the Census Industry Codes (CIC). These can be matched with NAICS industries using specific industry codes crosswalks, also provided by the Census Bureau.\footnote{Note that these are not one-to-one; often, a CIC is assigned various NAICS or the other way round. Also, CICs differ slightly across surveys, which complicates the assignment to NAICS industries. In general, it is not possible to in this way obtain reliable information on more than the first two NAICS digits.}

\cite{ALM2003} weigh occupations by their respective shares in employment in a CIC industry. Their dataset contains the necessary components to construct the RTI and an assignment of occupations to industries weighted by their 1991 share of employment. We use their quantification of the routine, analytical and manual task components in O*NET data to construct the RTI. We apply the \cite{AD2013} definition of the RTI, which is more widely used than the original one by \cite{ALM2003}. According to \cite{AD2013},
\begin{equation}
 \text{RTI} = ln(\text{routine}) - ln(\text{manual}) - ln(\text{analytical})
\end{equation}

Since \cite{ALM2003} use their data to also carry out analyses for different educational groups, this allows for the creation of separate RTIs for four different educational groups. While our main interest is in comparing our automation index with the aggregate RTI, this additional information is nevertheless helpful in assessing the quality of our index.

Applying the procedure described above, we are able to match the RTI with our automation index at the level of the first two digits of the NAICS classification codes. There are altogether 24 two digit-NAICS industries for which we have observations.

\begin{comment}
\begin{table}[htbp]\centering \small \caption{Cross-correlation table one-digit NAICS\label{corrtable1}}
	\begin{tabular}{l  c  c  c  c  c  c }\hline\hline
		\multicolumn{1}{c}{Variables} &automation\_index&RTI\_all&
		RTI\_HSD&RTI\_HSG&RTI\_SMC&RTI\_CLG\\ \hline
		automation\_index&1.000\\
		RTI\_all&0.607&1.000\\
		RTI\_HSD&0.764&0.878&1.000\\
		RTI\_HSG&0.693&0.935&0.870&1.000\\
		RTI\_SMC&0.541&0.940&0.724&0.921&1.000\\
		RTI\_CLG&-0.418&0.191&-0.212&0.216&0.421&1.000\\
		\hline \hline 
	\end{tabular}
\end{table}
\end{comment}

\vspace{0.5cm}
\begin{table}[htbp]\centering \small \caption{Cross-correlation table two-digit NAICS\label{corrtable2}}
	\begin{tabular}{l  c  c  c  c  c  c }\toprule
		\multicolumn{1}{c}{Variables} &automation\_index&RTI\_all&
		RTI\_HSD&RTI\_HSG&RTI\_SMC&RTI\_CLG\\ \midrule
		automation\_index&1.000\\
		RTI\_all&0.145&1.000\\
		RTI\_HSD&0.364&0.871&1.000\\
		RTI\_HSG&0.414&0.820&0.823&1.000\\
		RTI\_SMC&0.180&0.903&0.715&0.904&1.000\\
		RTI\_CLG&-0.570&0.344&0.003&0.207&0.543&1.000\\
		\bottomrule 
	\end{tabular}
\end{table}
\vspace{0.5cm}

As can be seen, the overall correlation of the automation index with RTI is small but positive, at 0.145. In order to interpret this value, it is insightful to consider the correlations of our index with RTI for different educational groups: Whereas it is largely positive for high school dropouts (HSD) and high school graduates (HSG), it is much smaller for those jobholders that have some college eduation (SMC) and largely negative for those with completed college education (CLG). Thus, it can be said that automation and routinizability describe similar things in lower educational groups, while they diverge for occupations that require a lot of education.

One possible explanation for this is that the type of automation captured by patents is mostly meant to replace low-education routine jobs, for example a patent of a robot working in an assembly line. However, the type of automation technology replacing highly educated employees is likely to be less tangible: it could, for example, be a computer software that facilitates the filing of an electronic tax declaration and thus replaces tax accountants. Note that this software, if patented at all, would also probably be filed in a different sector: not by an accountancy firm but by an IT firm.

\section{Labor Demand Effects of Automation}

\subsection{Direct employment effects}
It is natural to assume that the tremendous increase in patents on automation over the last decades will have major effects on the labor market. While on the one hand, labor productivity in the U.S. economy has been rising continuously, on the other hand, the employment-to-population ratio is lower today than any time in the last 20 years, and the real income of the median worker is lower than in the 1990s \citep[p.~164]{BM2014}.

A growing number of labor economists has focused on the link between automation and employment, see for example \cite{ALM2003}, \cite{GM2007} and \cite{AKK2008}. Mostly on the occupation level, these papers aim to find out whether the technological change induced by new machines is skill-biased (in that it benefits high-skilled workers and harms low-skilled workers) or whether occupations that require a higher degree of routine tasks are more in danger of being replaced by machines than those that comprise non-routine analytic or manual tasks. There are two main reasons why, despite the large number of publications on the subject, we expect our approach to be a novel contribution: first, constructing an indicator without prior restrictions on what we expect automation to be like in the future; second, building an industry-level instead of an occupation-level indicator.

\subsubsection*{Avoiding imposing prior expectations on automation index}
As argued above, existing automation indices often use prior knowledge to assess what we expect machines to be able to do in the future. In particular, the manual part of tasks is often considered to not be automizable. \cite{BM2014} argue that recent advances in robotics suggest otherwise.

\cite{AKK2008} and \cite{AD2013}, building on \cite{ALM2003} construct an automation index as the log of routine task importance divided by the manual task importance. Similarly, \cite{GMS2014} reduce their indicator for those tasks that includes abstract and service task importances. Our approach does not penalize mechanical work aspects, but rather builds an indicator at a deeper level interpreting patents as indicative of technological possibilities.

\subsubsection*{Towards an industry-level indicator of automation}
Second, we construct an industry-level indicator while existing classifications usually work at the occupation level. This offers the possibility to approach the academic debate on automation from a different angle. Having matched our patent counts with NAICS industries, we obtain an industry-time panel dataset. Employment data is also available at the industry level: the U.S. Bureau of Labor statistics (BLS) publishes data for NAICS industries on a monthly basis, which is complete from 1990 onwards, but even goes back as far as the 1930s for some industries. Thus, our dataset will comprise at least 15 years of monthly employment and automation data for around 500 industries. It will allow for a detailed analysis of which industries gain and which lose from automation in terms of employment. The effect of automation on employment is most likely going to be lagged, since the granting of a patent will not immediately result in its widespread application. We could approach the identification of the effect for each industry through time series techniques such as cointegration or VAR analysis. Due to the lagged response of employment, we can use present-day innovations to make predictions about future employment. This could be of strong interest to both researchers and policy-makers.

\subsection{Indirect employment effects through reshoring}
Next to automation, the second major development in labor demand over the last decades has been the relocation of production sites to foreign, mostly less developed countries. ``Offshoring", which is defined by the Palgrave Dictionary of Economics as the ``import of parts or services from related overseas suppliers, such as foreign subsidiaries", has become the research focus of trade as well as labor economists. Studies that analyze the effects of offshoring on employment include those by \cite{FH1999}, \cite{GR2008}, \cite{EHMP2014} and \cite{HJMX2014}), but only few have considered offshoring jointly with automation. A noteworthy exception is \cite{GMS2014}, who estimate which of the two developments has a larger effect on employment in the United States. To the best of our knowledge, no research paper has so far investigated whether automation also affects home-country employment indirectly through offshoring.\footnote{This link is suggested, but not elaborated on, by \cite{BM2014}.} It might be the case that the introduction of automation techniques in the production process affects the offshoring behavior of firms: When machines decrease unit labor costs at home, it might become cheaper for a firm to relocate production back from the foreign country to the home country.\footnote{A necessary condition is that it is cheaper for firms to set up machines where the final market is than in the offshore location. \cite{BMS2014} argue that there will be added value from shortening delivery times and reducing inventory costs, which will offset the cost advantage from having to pay machine operators in the home country higher wages than abroad.}
This process, called ``reshoring", might bring about positive employment effects in the home country.

\subsubsection*{Measuring offshoring}
We have shown above that in order to quantify the effects of automation, it is key to have an appropriate measure at hand; the same argument holds for offshoring. In the literature, different indices have been proposed to measure offshoring.

\cite{B2009} creates an index of offshorability based on information contained in O*NET. By means of a classification tree, occupations are sorted into four different categories that range from ``Non-offshorable" to ``Highly offshorable". He presents a ranking of 291 occupations according to their offshorability, but does not provide a cardinal scale. The same methodology is applied to Germany by \cite{SL2009}, who use the BERUFENET database of the Federal Employment Agency (Bundesagentur für Arbeit).

\cite{BK2013} use worker-level survey data gathered as part of the Princeton Data Improvement Initiative (PDII) to create more nuanced indices of offshorability. The approx. 2,500 survey participants in the U.S. were asked to classify their jobs according to how easily they could be performed from a distant location, and to what extent face-to-face interaction was required. Using this information, \cite{BK2013} create an index of offshorability that distinguishes five different categories.This index is for the occupation level, but the PDII dataset allows for aggregation into NAICS industries as well.

Note that both indices do not grasp the realised offshoring of jobs, but the potential of the jobs still performed at home to be offshored. Neither are those occupations that have already been offshored captured by the indices, nor do they contain any information on how likely it is that these jobs are effectively going to be offshored, or when. In parallel to the argument that was made above for automation indices, such a type of offshorability index describes a potential development from the viewpoint of today's technological advances; it does not describe a certain future.

An alternative index has been proposed by \cite{GMS2014}, who analyze data from the European Restructuring Monitor (part of the Eurofound), which provides summaries of news reports on offshoring plans of European companies. They sum up all events by occupation type of the offshored jobs and rescale to obtain a measure with a distribution of zero mean and unit standard deviation. However, it seems questionable how complete and how reliable the data is.\footnote{Yet another alternative would be to use data on foreign direct investment, but the problem is that there is no means of knowing whether the goods produced in the foreign production site are sold in the home market (which would be required for offshoring) or in the foreign market.}

Given these shortcomings of existing indices, we could try to build a new offshoring through patent text search. The keywords to look for are, however, less clear than in the case of automation. One possibility would be a combination of words that describe geography and production, e.g. the stems ``global", ``international", ``cross-border", ``long-distance", ``foreign" combined with ``value chain", ``investment", ``production site", ``subsidiary", ``transaction costs", ``shipment" or ``intermediate inputs". These are preliminary thoughts only; developing an informative index of offshoring based on patent data is one of the goals of our research paper. Note that this database, in addition to applying a more useful definition of offshoring, also offers the advantage of analyzing changes over time since it could be calculated yearly, monthly or weekly.

\subsubsection*{Offshoring and automation}

In absense of an appropriate measure of offshoring, any analysis of the link between offshoring and automation is necessarily preliminary and incomplete. However, for illustrative purposes, we plot the offshorability measure of \cite{BK2013} against our measure of automation in figure~\ref{fig:offshoring_vs_automation}: on the x-axis, the offshorability index is aggregated at the industry level, ranking from -2 (``not offshorable") to 2 (``easily offshorable"). On the y-axis is the industry sum of automation matches in the patent database for 2001.\footnote{The PDII survey was carried out in 2008, so ideally, we would use patent data of 2008. Since our patent dataset so far reaches only until 2001, we chose the last year available as the one closest to the survey year.} The correlation is positive and significant, but rather small at 0.02.

\begin{figure}
	\centering
	\caption{Automation vs. Offshoring}
	\label{fig:offshoring_vs_automation}
	\includegraphics[totalheight=0.35\textheight]{./figures/automation_vs_offshore.pdf}
	\floatfoot{\textit{Source:} \cite{BK2013}, USPTO, Google and own calculations.}
\end{figure}

It can be seen that there are certain types of industries where a lot of automation has taken place in 2001, but which are not offshorable at all, like ``Support Activities for Oil and Gas Operations". Others, like ``Medical Instrument Manufacturing" are both offshorable and automizable. It will be interesting to think about the potential for reshoring across these different types of industries. Medical Instrument Manufacturing could be a candidate for reshoring if in the production process of these instruments, foreign workers are being replaced by machines once innovations have taken place. But it could as well be that Medical Instrument Manufacturing will never be offshored because the use of machines has decreased production costs in the home country already at an earlier time.

This short discussion makes clear that the timing of offshoring and automation is crucial: Only if offshoring happens first will automation potentially lead to reshoring. Once we have developed a new offshoring index based on patent data, we will be able to detect time trends in the correlation, on the aggregate as well as on the industry level. If the correlation has increased over time, this might be an indicator that foreign labor and machines are becoming ever closer substitutes. It will also be interesting to see for which industries correlation is strong and has increased and for which it is weak and has decreased.

\subsubsection*{Developing model of reshoring}

In order to establish a causal link between automation and offshoring and hence to provide support for the reshoring hypothesis, a theoretical model is needed. We plan to develop such a model, using as a starting point some existing models of offshoring (e.g. \cite{GR2008}) and automation (e.g. \cite{ALM2003}, \cite{L2011}). In this model, complementarity and substitutability of home labor, foreign labor and machines will play a major role. One difficulty will be to transfer the mechanics of the existing occupation-level models to the industry level. The model could be tested empirically once we have the necessary data at hand.

\subsection{Other possible uses of database not linked to employment}
Although not of immediate interest to us in the context of this research project, there are many other possible applications of the automation database, which could be the subject of future research projects: (1) automation and sectoral productivity: does technological change increase (labor) productivity more in some sectors than in others? (2) comparing U.S. automation patents to European automation patents (using additional data from the European Patent Office or other sources): where is automation higher? Are there sector-level differences and do these link to comparative advantage and/or institutional characteristics? (The political economy literature on varieties of capitalism suggests that U.S. firms should innovate more in IT, pharmaceutics, biotechnology and related sectors whereas continental European firms should innovate more in manufacturing.)

%%%%%%%%%%%Bibliography%%%%%%%%%%%
%\newpage
\vspace*{0.5cm}
\setstretch{1} % Set line spacing to 1 for the bibliography.
\begin{thebibliography}{9}

	\bibitem[Acemoglu, Akcigit and Celik(2014)]{AAC2014} \textbf{Acemoglu, Daron, Ufuk Akcigit and Murat Alp Celik} (2014). ``Young, Restless and Creative: Openness to Disruption and Creative Innovations." NBER Working Paper No. 19894

	\bibitem[Arora, Belenzon and Patacconi(2015)]{ABP2015} \textbf{Arora, Ashish, Sharon Belenzon and Andrea Patacconi} (2015). ``Killing the Golden Goose? The Decline of Science in Corporate R\&D." \textit{NBER Working Paper No. 20902}.

	\bibitem[Autor and Dorn(2013)]{AD2013} \textbf{Autor, David H. and David Dorn} (2013). ``The Growth of Low-Skill Service Jobs and the Polarizatio of the US Labor Market." \textit{American Economic Review}, 103(5): 1553-1597

	\bibitem[Autor, Katz and Kearney(2008)]{AKK2008} \textbf{Autor, David H., Lawrence F. Katz and Melissa S. Kearney} (2008). ``Trends in US wage inequality: Revising the revisionists." \textit{The Review of Economics and Statistics}, 90(2): 300-323.

	\bibitem[Autor, Levy and Murnane(2003)]{ALM2003} \textbf{Autor, David H., Frank Levy and Richard J. Murnane} (2003). ``The Skill Content of Recent Technological Change: An Empirical Exploration." \textit{The Quarterly Journal of Economics}, 118(4): 1279-1333.

	\bibitem[Baker, Bloom and Davis(2011)]{BBD2013} \textbf{Baker, Scott R., Nicholas Bloom and Steven J. Davis} (2013). ``Measuring economic policy uncertainty." \textit{Chicago Booth research paper}, 13-02.

%	\bibitem[Banister and Cook(2011)]{BC2011} \textbf{Banister, Judith and George Cook} (2011). ``China's Employment and Compensation Costs in Manufacturing through 2008." \textit{Monthly Labor Review}, 39-52.

	\bibitem[Blinder(2009)]{B2009} \textbf{Blinder, Alan S.} (2009). ``How Many US Jobs Might be Offshorable." \textit{World Economics}, 10: 41-78.

	\bibitem[Blinder and Krueger(2013)]{BK2013} \textbf{Blinder, Alan S. and Alan B. Krueger} (2013). ``Alternative Measures of Offshorability: A Survey Approach." \textit{Journal of Labor Economics}, 31(2): 97-128.

	\bibitem[Brynjolfsson and McAfee(2014)]{BM2014} \textbf{Brynjolfsson, Erik and Andrew McAfee} (2014). \textit{The Second Machine Age: Work, Progress, and Prosperity in a Time of Brilliant Technologies.} WW Norton \& Company.

		\bibitem[Brynjolfsson, McAfee and Spence(2014)]{BMS2014}\textbf{Brynjolfsson, Erik, Andrew McAfee and Michael Spence} (2014). ``New World Order. Labor, Capital, and Ideas in the New Power Law Economy." \textit{Foreign Affairs}, 93(4): 44-53.

	\bibitem[Ebenstein, Harrison, McMillan and Phillips(2014)] {EHMP2014} \textbf{Ebenstein, Avraham, Ann Harrison, Margret McMillan and Shannon Phillips} (2014). ``Estimating the Impact of Trade and Offshroing on American Workers Using the Current Population Surveys." \textit{Review of Economics and Statistics}, 96(4): 581-595.

	\bibitem[Feenstra and Hanson(1999)]{FH1999} \textbf{Feenstra, Robert C. and Gordon H. Hanson} (1999). ``The Impact of Outsourcing and High-Technology Capital on Wages: Estimates for the United States, 1979-1990." \textit{Quarterly Journal of Economics}, 114(3): 907-940.

	\bibitem[Fierro(2013)]{F2013} \textbf{Fierro, Gabe} (2013). ``Extracting and Formatting Patent Data from USPTO XML." \textit{Fung Technical Report} No. 2013.06.16, University of California, Berkeley.

	\bibitem[Gentzkow and Shapiro(2010)]{GS2010} \textbf{Gentzkow, Matthew and Jesse M. Shapiro} (2010). ``What drives media slant? Evidence from US daily newspapers." \textit{Econometrica}, 78(1): 35-71.

	\bibitem[Goos and Manning(2007)]{GM2007} \textbf{Goos, Maarten and Alan Manning} (2007). ``Lousy and Lovely Jobs: The Rising Polarization of Work in Britain." \textit{Review of Economics and Statistics}, 89(1): 118-133.

	\bibitem[Goos, Manning and Salomons(2014)]{GMS2014} \textbf{Goos, Maarten, Alan Manning and Anna Salomons} (2014). ``Explaining Job Polarization: Routine-Biased Technological Change and Offshoring." \textit{American Economic Review}, 104(8): 2509-2526.

	\bibitem[Grossman and Rossi-Hansberg(2008)]{GR2008} \textbf{Grossman, Gene M. and Esteban Rossi-Hansberg} (2008). ``Trading Tasks: A Simple Theory of Offshoring". \textit{American Economic Review}, 98(5): 1978-1997.

	\bibitem[Hall, Jaffe and Trajtenberg(2001)]{HJT2001} \textbf{Hall, Bronwyn H., Adam B. Jaffe and Manuel Trajtenberg} (2001). ``The NBER Patent Citation Data File: Lessons, Insights and Methodologial Tools". \textit{NBER Working Paper No. 8498}.

	\bibitem[Hansen, McMaho and Prat(2014)]{HMP2014} \textbf{Hansen, Stephen, Michael McMahon and Andrea Prat} (2014). ``Transparency and Deliberation within the FOMC:
a Computational Linguistics Approach". CEPR Discussion Paper 9994.

	\bibitem[Hinze and Schmoch(2005)]{HS2005} \textbf{Hinze, Sybille and Ulrich Schmoch} (2005). ``Opening the Black Box." \textit{Handbook of Quantitative Science and Technology Research}, Springer Netherlands, 215-235.

	\bibitem[Hummels, Jørgensen, Munch and Xiang(2014)]{HJMX2014} \textbf{Hummels, David, Rasmus Jørgensen, Jakob Munch and Chong Xiang} (2014). ``The Wage Effects of Offshoring: Evidence from Danish Matched Worker-Firm Data." \textit{American Economic Review}, 104(6): 1597-1629.

	\bibitem[Lewis(2011)]{L2011} \textbf{Lewis, Ethan} (2011). ``Immigration, Skill Mix, and Capital Skill Complementarity." \textit{The Quarterly Journal of Economics}, 126(2): 1029-1069.

%	\bibitem[Marin(2014)]{M2014} \textbf{Marin, Dalia} (2014). ``Globalisation and the Rise of the Robots." \textit{VoxEU.org}, CEPR. \href{http://www.voxeu.org/article/globalisation-and-rise-robots}{\texttt{[link]}}

	\bibitem[Magerman, Van Looy and Song(2010)]{MVS2010} \textbf{Magerman, Tom, Bart Van Looy and Xiaoyan Song} (2010). ``Exploring the feasibility and accuracy of Latent Semantic Analysis based on text mining techniques to detect similarity between patent documents and scientific publication." \textit{Scientometrics}, 82(2): 289-306.

	\bibitem[Manning, Raghavan and Schütze(2009)]{MRS2009} \textbf{Manning, Christopher D., Prabhakar Raghavan and Hinrich Schütze} (2009). \textit{An Introduction to Information Retrieval.}  Cambridge University Press.

	\bibitem[Schrader and Laaser(2009)]{SL2009} \textbf{Schrader, Klaus and Claus-Friedrich Laaser} (2009). ``Globalisierung in der Wirtschaftskrise: wie sicher sind die Jobs in Deutschland." \textit{Kieler Diskussionsbeiträge} No. 465

%	\bibitem[Timmer, Erumban, Los, Stehrer and de Vries(2014)]{TELSdV2014} \textbf{Timmer, Marcel P., Abdul Azeez Erumban, Bart Los, Robert Stehrer and Gaaitzen J. de Vries} (2014). ``Slicing Up Global Value Chains." \textit{Journal of Economic Perspectives}, 28(2): 99-118.

\end{thebibliography}

%\vspace*{0.7cm}
%\begin{appendix}
%\newpage
%\section{Figures}
%\newpage

%\end{appendix}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}

### 2015-03-06 make_figures/make_barchart_nrpatents.m

@@ -74,13 +74,17 @@ set(figureHandle, 'PaperPositionMode', 'Auto', 'PaperUnits', ...
 
 
 %% Add text
-annotation('textbox', [0.135 0.23 0.1 0.1], 'String', '70900', ...
+arrow_x = [0.169, 0.15];
+arrow_y = [0.32, 0.26];
+annotation('textarrow', arrow_x, arrow_y, 'String', '70900', ...
         'FontSize', 12, 'HorizontalAlignment', 'left', ...
-        'EdgeColor', 'none'); % [x y w h]
-
-annotation('textbox', [0.85 0.75 0.1 0.1], 'String', '327000', ...
+        'HeadStyle', 'none'); % [x y w h]
+    
+arrow_x = [0.885, 0.885];
+arrow_y = [0.825, 0.78];
+annotation('textarrow', arrow_x, arrow_y, 'String', '327000', ...
         'FontSize', 12, 'HorizontalAlignment', 'left', ...
-        'EdgeColor', 'none'); % [x y w h]
+        'HeadStyle', 'none'); % [x y w h]
 
 
 

### 2015-03-10 paper/paper.tex
Include two new weeks in 2015

--- 2015-03-06 text/research_paper.tex
@@
 	\includegraphics[trim=1cm 0cm 0cm 0cm, clip=true, totalheight=0.38\textheight]{./figures/keyword_matches_weekly_1976-2015.pdf}
-	\floatfoot{\textit{Note:} Every data point displays sum of matches from searching through one file of weekly patent grant texts; total identified patents: 5.5 mio.; total number of keyword matches: 6.9 mio.\\[0.1cm]
-	\textit{Source:} USPTO, Google and own calculations.}
+	\floatfoot{
+	\begin{minipage}{0.8\textwidth}
+	\textit{Note:} Every data point displays sum of matches from searching through one file of weekly patent grant texts; total identified patents: 5.5 mio.; total number of keyword matches: 6.9 mio.\\[0.1cm]
+	\textit{Source:} USPTO, Google and own calculations.
+	\end{minipage}
+	}
 	\label{fig:keyword_match_over_time}
@@
 	\label{fig:summary_stats}
-	\floatfoot{\textit{Note:} Identified patents are those found through the search algorithm; the bottom darker-shade bars are the number of distinct patents with at least one match \\[0.1cm]
-	\textit{Source:} USPTO, Google and own calculations.}
+	\floatfoot{
+	\begin{minipage}{0.8\textwidth}
+\textit{Note:} Identified patents are those found through the search algorithm; the bottom darker-shade bars are the number of distinct patents with at least one match \\[0.1cm]
+	\textit{Source:} USPTO, Google and own calculations. 
+	\end{minipage}
+		}
 \end{figure}
+
+%\begin{figure}[tb]
+%\caption{Number of identified patents, 1976-2014}
+%	\includegraphics[trim=0cm 0cm 1cm 0.5cm, clip=true, totalheight=0.25\textheight]{./figures/barchart_identified_patents_1976-2014.pdf}
+%	\label{fig:summary_stats}
+%	\floatfoot{\textit{Note:} Identified patents are those found through the search algorithm; the bottom darker-shade bars are the number of distinct patents with at least one match \\[0.1cm]
+%	\textit{Source:} USPTO, Google and own calculations.}
+%\end{figure}
 
@@
 	\includegraphics[trim=1cm 0cm 1cm 0cm, clip=true, totalheight=0.4\textheight]{./figures/match_over_nrpatents_weekly_1976-2015.pdf}
-	\floatfoot{\textit{Note:} Every data point displays sum of matches from searching through one file of weekly patent grant texts divided by the number of identified patents for that week; the solid line is the HP-filtered trend with $\lambda = 100'000$; the size of markers corresponds to number of patents in week.\\[0.1cm]
-	\textit{Source:} USPTO, Google and own calculations.}
+	\floatfoot{
+	\begin{minipage}{0.8\textwidth}
+	\textit{Note:} Every data point displays sum of matches from searching through one file of weekly patent grant texts divided by the number of identified patents for that week; the solid line is the HP-filtered trend with $\lambda = 100'000$; the size of markers corresponds to number of patents in week.\\[0.1cm]
+	\textit{Source:} USPTO, Google and own calculations.
+	\end{minipage}
+	}
 	\label{fig:match_per_nrpatents}

### 2015-03-10 find_patents_part3.m

@@ -10,8 +10,8 @@ addpath('functions');
 
 
 %% Set some inputs
-year_start = 2012;
-year_end = 2012;
+year_start = 2015;
+year_end = 2015;
 
 
 
@@ -26,7 +26,9 @@ for ix_year = year_start:year_end
     % Determine if there are 52 or 53 weeks in year
     week_end = set_weekend(ix_year); 
 
-    build_data_path = horzcat('./data/', num2str(ix_year));
+    % build_data_path = horzcat('./data/', num2str(ix_year));
+    build_data_path = horzcat('T:\Puettmann\patent_data_save\', ...
+        num2str(ix_year));
     addpath(build_data_path);
 
 

### 2015-03-12 paper/paper.tex
Several
Put in new references Bell et al 2015 and Griliches 1998. Check out how ratio of distinct patents with at least one match over total number of patents. Put this in text together with years of min and max.

@@
-\documentclass[11pt,a4paper,fleqn]{article}
+\documentclass[11pt,a4paper]{article}
 
@@
 
-\vspace*{1.1cm}
+\vspace*{0.8cm}
 \begin{center}
-\begin{minipage}{0.65\textwidth}
+\begin{minipage}{0.8\textwidth}
 \textbf{Abstract.} We propose to develop a new industry-level indicator of automation based on searching patent grant texts for keywords.
@@
 patents granted by the U.S.
-Patent Office from 1976-2015 for words containing the stem ``automat".
+Patent Office from 1976-2015 for keywords related to automation.
 The 6.9 mio.
@@
 
-\newpage
+%\newpage
 \section{Introduction}
@@
 
-We are not the first to analyze patent data: \cite{HJT2001} provide data on patent citations and link those to publicly-traded firms on Compustat.
-A number of papers, such as \cite{AAC2014} and \cite{ABP2015} have made use of patent citations.
+We are not the first to analyze patent data: \cite{HJT2001} provide data on patent citations and link those to publicly-traded firms on Compustat..
+A number of papers, such as \cite{AAC2014} , \cite{ABP2015} and \cite{BCJPV2015} have made use of patent citations.
 However, contrary to those papers, we concentrate on the patent's \textit{content}, not on its relation to other patents.
+\cite{G1998} surveys the use of patents in economics and recommends a stronger use of the contents of patent documents, not only its meta information.
 As \citep[p.~290]{MVS2010} note, 
@@
 The increase in keyword matches could be due to the general increase in the number of patents (see panel A) from around 70'000 to 320'000 patents.
+The share of distinct patents with at least one match (the light blue bars in figure~\ref{fig:summary_stats} ) has also steadily risen from 20 in 1991 to 30 percent in 2014.
 
@@
 
+	\bibitem[Bell et al.(2015)]{BCJPV2015} \textbf{Bell, Alex, Raj Chetty, Xavier Jaravel, Neviana Petkova and John Van Reenen} (2015).
+``Innovation Policy and the Lifecycle of Inventors." mimeo, Harvard University, Office of Tax Analysis, CEPR, LSE.
+
 %	\bibitem[Banister and Cook(2011)]{BC2011} \textbf{Banister, Judith and George Cook} (2011).
@@
 ``Explaining Job Polarization: Routine-Biased Technological Change and Offshoring." \textit{American Economic Review}, 104(8): 2509-2526.
+
+	\bibitem[Griliches(1998)]{G1998} \textbf{Griliches, Zvi} (1998).
+``Patent Statistics as Economic Indicators: A Survey." \textit{R&D and Productivity: The Econometric Evidence}, University of Chicago Press, 287-343.
 

### 2015-03-12 make_figures/plot_distct_match_o_nrpatents.m

@@ -1,0 +1,85 @@
+close all
+clear all
+clc
+
+% Define parameters
+year_start = 1976;
+year_end = 2014;
+
+
+
+
+
+%% Load summary data
+build_load_filename = horzcat('patent_match_summary_', num2str(year_start), ...
+    '-', num2str(year_end), '.mat');
+load(build_load_filename)
+
+
+%% Calculate ratio
+ratio_dist_o_nrpatents = patent_match_summary.nr_distinct_patents_hits ./ ...
+    patent_match_summary.nr_patents_yr;
+
+[minratio, ix_min] = min(ratio_dist_o_nrpatents);
+[maxratio, ix_max] = max(ratio_dist_o_nrpatents);
+fprintf('Minimum ratio: %d in year %d.\n', minratio, year_start - 1 + ix_min)
+fprintf('Maximum ratio: %d in year %d.\n', max(ratio_dist_o_nrpatents), year_start - 1 + ix_max)
+
+
+%% Some settings for the plots
+set_ylimit = [0.1 0.4];
+
+plot_time = year_start:year_end;
+color1_pick = [0.7900, 0.3800, 0.500];
+color2_pick = [0.000,0.639,0.561];
+color3_pick = [0.890,0.412,0.525];
+color4_pick = [0.890,0.412,0.525];
+
+
+my_light_gray = [0.95, 0.95, 0.95];
+my_dark_gray = [0.8, 0.8, 0.8];
+
+
+figureHandle = figure;
+
+% Plot total number of identified patents per year
+plot(plot_time, ratio_dist_o_nrpatents, 'Marker', 'o', ...
+    'MarkerEdgeColor', color1_pick, 'MarkerFaceColor', color1_pick, ...
+    'Color', color1_pick)
+
+
+set(gca,'FontSize',12) % change default font size of axis labels
+box off
+set(gca,'TickDir','out'); 
+ylim(set_ylimit)
+set(gca, 'YTickLabel', num2str(get(gca, 'YTick')')) % turn scientific notation off
+
+%get(gca, 'YTickLabel');
+%new_yticks = {'0'; ''; '100000'; ''; '200000'; ''; '300000'; ''; '400000'};
+%set(gca, 'yticklabel', new_yticks); 
+
+
+
+% General settings
+set(gcf, 'Color', 'w');
+
+set(0,'DefaultTextFontName','Palatino') % set font
+set(0,'DefaultAxesFontName','Palatino') % set font
+
+
+
+
[…]

### 2015-03-13 paper/paper.tex
Some more references to Griliches 1998

@@
 
-We are not the first to analyze patent data: \cite{HJT2001} provide data on patent citations and link those to publicly-traded firms on Compustat..
+We are not the first to analyze patent data: \cite{HJT2001} provide data on patent citations and link those to publicly-traded firms on Compustat.
+Patent citations differ from academic citations in that the patent examiner determines determine the novelty of the patent and the citations are therefore likely to be more objective than those in academic publications.
 A number of papers, such as \cite{AAC2014} , \cite{ABP2015} and \cite{BCJPV2015} have made use of patent citations.
 However, contrary to those papers, we concentrate on the patent's \textit{content}, not on its relation to other patents.
-\cite{G1998} surveys the use of patents in economics and recommends a stronger use of the contents of patent documents, not only its meta information.
+\cite{G1998} surveys the use of patents in economics and recommends a stronger use of the contents of patent documents, not only its aggregated meta information.
 As \citep[p.~290]{MVS2010} note, 
@@
 The share of distinct patents with at least one match (the light blue bars in figure~\ref{fig:summary_stats} ) has also steadily risen from 20 in 1991 to 30 percent in 2014.
+\cite{G1998}  remarks that there was a global reduction in patents granted (and only a minor reduction in applications) throughout the 1970s, the end of which can also be seen in our data.
+\cite{G1998} discusses the possibility of this being due to ``bureaucratic cycles".
 
@@
 
-As a further option we could weigh this index by the number of times a patent has been cited by other patents using the data provided by \cite{HJT2001}, however correcting for the fact that older patents have been cited more often.
+\cite{G1998} recommends weighting for the importance of patents.
+A such we could weigh this index by the number of times a patent has been cited by other patents using the data provided by \cite{HJT2001}, however correcting for the fact that older patents have been cited more often.
 Such a citation-weighted index could take the form $x_i = log(1+m_i) [1+log(1+\frac{c_i}{C_t})]$, where $c_i$ are the patent $i$'s citations over the whole period and $C_t$ are the total number of citations of patents in the same year over the whole period.
@@
 In general, this is not an easy task since the same patent might be of use in various different industries.
+\cite{G1998} describes some of the difficulties faced when matching patents to industries.
 The industry to which the patent assignee belongs might not be informative in this context because many large companies - which are, in general, those companies most likely to innovate - are active in multiple different fields.
@@
 \subsection{Other possible uses of database not linked to employment}
-Although not of immediate interest to us in the context of this research project, there are many other possible applications of the automation database, which could be the subject of future research projects: (1) automation and sectoral productivity: does technological change increase (labor) productivity more in some sectors than in others?
-(2) comparing U.S.
+Although not of immediate interest to us in the context of this research project, there are many other possible applications of the automation database, which could be the subject of future research projects:
+\begin{enumerate}
+\item automation and sectoral productivity: does technological change increase (labor) productivity more in some sectors than in others? 
+\item comparing U.S.
 automation patents to European automation patents (using additional data from the European Patent Office or other sources): where is automation higher?
@@
 firms should innovate more in IT, pharmaceutics, biotechnology and related sectors whereas continental European firms should innovate more in manufacturing.)
+\item one could also compare this patent index to aggregate total factor productivity.
+However, \cite{G1998} discusses the use of patents as an  ``output" index (like a technology frontier) vs an ``input" index (for example, to measure a firms research activities) and warns against interpreting changes in patent numbers in the time dimension.
+\end{enumerate}
 

### 2015-03-14 paper/paper.tex
..

@@
 %%%%%%%%%%%Bibliography%%%%%%%%%%%
-%\newpage
+\clearpage
 \vspace*{0.5cm}
@@
 
-	\bibitem[Acemoglu, Akcigit and Celik(2014)]{AAC2014} \textbf{Acemoglu, Daron, Ufuk Akcigit and Murat Alp Celik} (2014).
+	\bibitem[Acemoglu et al.(2014)]{AAC2014} \textbf{Acemoglu, Daron, Ufuk Akcigit and Murat Alp Celik} (2014).
 ``Young, Restless and Creative: Openness to Disruption and Creative Innovations." NBER Working Paper No.
@@
 
-	\bibitem[Arora, Belenzon and Patacconi(2015)]{ABP2015} \textbf{Arora, Ashish, Sharon Belenzon and Andrea Patacconi} (2015).
+	\bibitem[Arora et al.(2015)]{ABP2015} \textbf{Arora, Ashish, Sharon Belenzon and Andrea Patacconi} (2015).
 ``Killing the Golden Goose?
@@
 
-	\bibitem[Autor, Katz and Kearney(2008)]{AKK2008} \textbf{Autor, David H., Lawrence F.
+	\bibitem[Autor et al.(2008)]{AKK2008} \textbf{Autor, David H., Lawrence F.
 Katz and Melissa S.
@@
 
-	\bibitem[Autor, Levy and Murnane(2003)]{ALM2003} \textbf{Autor, David H., Frank Levy and Richard J.
+	\bibitem[Autor et al.(2003)]{ALM2003} \textbf{Autor, David H., Frank Levy and Richard J.
 Murnane} (2003).
@@
 
-	\bibitem[Baker, Bloom and Davis(2011)]{BBD2013} \textbf{Baker, Scott R., Nicholas Bloom and Steven J.
-Davis} (2013).
-``Measuring economic policy uncertainty." \textit{Chicago Booth research paper}, 13-02.
+	\bibitem[Baker et al.(2011)]{BBD2013} \textbf{Baker, Scott R., Nicholas Bloom and Steven J. Davis} (2013). ``Measuring economic policy uncertainty." \textit{Chicago Booth research paper}, 13-02.
 
@@
 
-		\bibitem[Brynjolfsson, McAfee and Spence(2014)]{BMS2014}\textbf{Brynjolfsson, Erik, Andrew McAfee and Michael Spence} (2014).
+		\bibitem[Brynjolfsson et al.(2014)]{BMS2014}\textbf{Brynjolfsson, Erik, Andrew McAfee and Michael Spence} (2014).
 ``New World Order.
@@
 
-	\bibitem[Ebenstein, Harrison, McMillan and Phillips(2014)] {EHMP2014} \textbf{Ebenstein, Avraham, Ann Harrison, Margret McMillan and Shannon Phillips} (2014).
+	\bibitem[Ebenstein et al.(2014)] {EHMP2014} \textbf{Ebenstein, Avraham, Ann Harrison, Margret McMillan and Shannon Phillips} (2014).
 ``Estimating the Impact of Trade and Offshroing on American Workers Using the Current Population Surveys." \textit{Review of Economics and Statistics}, 96(4): 581-595.
@@
 
-	\bibitem[Goos, Manning and Salomons(2014)]{GMS2014} \textbf{Goos, Maarten, Alan Manning and Anna Salomons} (2014).
+	\bibitem[Goos et al.(2014)]{GMS2014} \textbf{Goos, Maarten, Alan Manning and Anna Salomons} (2014).
 ``Explaining Job Polarization: Routine-Biased Technological Change and Offshoring." \textit{American Economic Review}, 104(8): 2509-2526.
@@
 
-	\bibitem[Hall, Jaffe and Trajtenberg(2001)]{HJT2001} \textbf{Hall, Bronwyn H., Adam B.
+	\bibitem[Hall  et al.(2001)]{HJT2001} \textbf{Hall, Bronwyn H., Adam B.
 Jaffe and Manuel Trajtenberg} (2001).
@@
 
-	\bibitem[Hansen, McMaho and Prat(2014)]{HMP2014} \textbf{Hansen, Stephen, Michael McMahon and Andrea Prat} (2014). ``Transparency and Deliberation within the FOMC:
+	\bibitem[Hansen et al.(2014)]{HMP2014} \textbf{Hansen, Stephen, Michael McMahon and Andrea Prat} (2014). ``Transparency and Deliberation within the FOMC:
 a Computational Linguistics Approach". CEPR Discussion Paper 9994.
@@
 
-	\bibitem[Hummels, Jørgensen, Munch and Xiang(2014)]{HJMX2014} \textbf{Hummels, David, Rasmus Jørgensen, Jakob Munch and Chong Xiang} (2014).
+	\bibitem[Hummels et al.(2014)]{HJMX2014} \textbf{Hummels, David, Rasmus Jørgensen, Jakob Munch and Chong Xiang} (2014).
 ``The Wage Effects of Offshoring: Evidence from Danish Matched Worker-Firm Data." \textit{American Economic Review}, 104(6): 1597-1629.
@@
 
-	\bibitem[Magerman, Van Looy and Song(2010)]{MVS2010} \textbf{Magerman, Tom, Bart Van Looy and Xiaoyan Song} (2010).
+	\bibitem[Magerman et al.(2010)]{MVS2010} \textbf{Magerman, Tom, Bart Van Looy and Xiaoyan Song} (2010).
 ``Exploring the feasibility and accuracy of Latent Semantic Analysis based on text mining techniques to detect similarity between patent documents and scientific publication." \textit{Scientometrics}, 82(2): 289-306.
 
-	\bibitem[Manning, Raghavan and Schütze(2009)]{MRS2009} \textbf{Manning, Christopher D., Prabhakar Raghavan and Hinrich Schütze} (2009).
+	\bibitem[Manning et al.(2009)]{MRS2009} \textbf{Manning, Christopher D., Prabhakar Raghavan and Hinrich Schütze} (2009).
 \textit{An Introduction to Information Retrieval.}  Cambridge University Press.

### 2015-03-17 paper/paper.tex
..

--- 2015-03-12 paper/paper.tex
@@
 patents granted by the U.S.
-Patent Office from 1976-2015 for keywords related to automation.
+Patent Office from 1976-2015 for words containing the stem ``automat".
 The 6.9 mio.
@@
 
-We are not the first to analyze patent data: \cite{HJT2001} provide data on patent citations and link those to publicly-traded firms on Compustat..
-A number of papers, such as \cite{AAC2014} , \cite{ABP2015} and \cite{BCJPV2015} have made use of patent citations.
+We are not the first to analyze patent data: \cite{HJT2001} provide data on patent citations and link those to publicly-traded firms on Compustat.
+A number of papers, such as \cite{AAC2014} and \cite{ABP2015} have made use of patent citations.
 However, contrary to those papers, we concentrate on the patent's \textit{content}, not on its relation to other patents.
-\cite{G1998} surveys the use of patents in economics and recommends a stronger use of the contents of patent documents, not only its meta information.
 As \citep[p.~290]{MVS2010} note,
@@
 The increase in keyword matches could be due to the general increase in the number of patents (see panel A) from around 70'000 to 320'000 patents.
-The share of distinct patents with at least one match (the light blue bars in figure~\ref{fig:summary_stats} ) has also steadily risen from 20 in 1991 to 30 percent in 2014.
 
@@
 %%%%%%%%%%%Bibliography%%%%%%%%%%%
-%\newpage
+\newpage
 \vspace*{0.5cm}
@@
 ``Measuring economic policy uncertainty." \textit{Chicago Booth research paper}, 13-02.
-
-	\bibitem[Bell et al.(2015)]{BCJPV2015} \textbf{Bell, Alex, Raj Chetty, Xavier Jaravel, Neviana Petkova and John Van Reenen} (2015).
-``Innovation Policy and the Lifecycle of Inventors." mimeo, Harvard University, Office of Tax Analysis, CEPR, LSE.
 
@@
 ``Explaining Job Polarization: Routine-Biased Technological Change and Offshoring." \textit{American Economic Review}, 104(8): 2509-2526.
-
-	\bibitem[Griliches(1998)]{G1998} \textbf{Griliches, Zvi} (1998).
-``Patent Statistics as Economic Indicators: A Survey." \textit{R&D and Productivity: The Econometric Evidence}, University of Chicago Press, 287-343.
 

### 2015-05-12 manual_classification/manual_coding_handbook.tex
Add manual coding handbook
It's important to know which version of the handbook we send to people.

\documentclass[10pt]{beamer}
%\documentclass[14pt, handout]{beamer} % to print out, change to this set-up

\usepackage{amsmath} % to include math
\usepackage{tikz}
\usetikzlibrary{arrows} % to use arrows in tikz

\usepackage{pgfplots}
\usepackage{units}
\usepackage{ulem}
\usepackage{epstopdf} % for making .eps to .pdf
\usepackage{graphicx} % to include graphics
\usepackage{subfigure}
\usepackage{hyperref}
\usepackage{appendixnumberbeamer} 
\usepackage{bbm}
\usepackage[utf8]{inputenc} % this makes it possible to use e

\usepackage{setspace} % to use \setstretch later

\usepackage[australian]{babel} % change date to to European date format

\usetheme{Dresden}

%%% The following section removes the second lighter blue line below the navigation panel %%%
\makeatletter
\beamer@theme@subsectionfalse
\makeatother
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage[flushleft]{threeparttable}  % for nice table

\usepackage{caption,fixltx2e}  % for nice tables
\usepackage[flushleft]{threeparttable}  % for nice tables

%%% I added the following two lines together to edit the color of the navigation bar at the top
\setbeamercolor{section in head/foot}{fg=gray,bg=white} 
%\setbeamertemplate{section in head/foot shaded}[default][10] % I'm not sure what this does

\hypersetup{pdfpagemode=UseNone} % un-comment this if you don't want to show bookmarks open when opening the pdf

%%%%%%%%%% Uncomment the following two lines to use Helvetica as font %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand{\familydefault}{\sfdefault} % to use sans-serif font
\usepackage{helvet} % use Helvetica font
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% -------- Define new color ------------------------------
\usepackage{color}

\definecolor{mygrey}{rgb}{0.85,0.85,0.85} % make grey for the table
\definecolor{mytextgrey}{rgb}{0.25, 0.25, 0.25} % make grey for text
% --------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\useinnertheme{circles} % changes the appearance of bullet points for both numbers and circles

\setbeamerfont{page number in head/foot}{size={\scriptsize}} % set size of page numbers

\setbeamertemplate{footline}[frame number]{} % shows the page numbers
\setbeamertemplate{navigation symbols}{} % this turns off the annoying navigation symbols at the bottom of the page

\definecolor{beamer@blendedblue}{rgb}{0.0471,0.298,0.6824} % changed the default color

\setbeamercolor{button}{bg=beamer@blendedblue}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title {\textbf{Manual Coding Handbook} \\[1cm]
A New Indicator of Automation \\ Based on Patent Text Search}
\author{
Katja Mann, Lukas P\"uttmann \\  
\textit{University of Bonn}}
\date{\textbf{Version: \today}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{frame}
\titlepage
\end{frame}

\section{Introduction}
\setcounter{subsection}{1} % add this after each \section{...} to start a new section of navigation circles

\begin{frame}\frametitle{Introduction}
%\vspace{-0.5cm}
	\begin{itemize}		
		\item Automation of tasks affects jobs to a large degree. 
		\item Therefore we need a good measure to be able to analyze the impact of automation on labor markets.
		\item In this research project, we design a new indicator of automation based on searching patent grant texts for keywords.
		\item We check this computer-based analysis by \textbf{manual coding}, the guidelines for which we describe in this document.
	\end{itemize}
\end{frame}

\section{Patents}
\setcounter{subsection}{1} % add this after each \section{...} to start a new section of navigation circles

\begin{frame}\frametitle{What is a patent?}
	\begin{itemize}	
		\item Patents guarantee the intellectual property right to an innovation. In the US this right is for 20 years. 
		\item People or firms apply for patents in a \textit{patent application} in which they describe, why a patent is new, useful and not trivial.
		\item The patent office then looks at the application and decides whether to grant the patent.
		\item If the patent is granted, an official \textit{patent grant text} is written. This is the document we will look at.
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Patent grant text ...}
... contains most importantly:
	\begin{itemize}	
		\item abstract
		\item detailed description
	\end{itemize}
... and contains also:
	\begin{itemize}	
		\item patent number
		\item name of the inventor
		\item date
		\item citations to other patents
		\item other legal information
		\item drawings
		\item technology classification number
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Our sample}
	\begin{itemize}	
	\item We study U.S. patents 1976-2015.
	\item Utility patents only. The patents we exclude have a patent number starting with a letter: D (design patents), PP (plant patents), R (reissue patents), T (defensive publications), H (statutory invention registration), X (very early patents)
	\end{itemize}
\end{frame}

\section{Automat}
\setcounter{subsection}{1} % add this after each \section{...} to start a new section of navigation circles

\begin{frame}
\textcolor{beamer@blendedblue}{\textbf{Definition:}}

	\begin{itemize}	
	\item An \textit{automat} is a \textbf{device}$^1$ that carries out a \textbf{process}$^2$ \textbf{independently}$^3$.
		\begin{itemize}	
		\item $^1$: could be a a physical machine, computer program, a robot.
		\item $^2$: could be a production process, the act of creation, composing a song, altering something, measuring something, a task
		\item $^3$: without human interference (apart from that needed for supervision, maintenance or at the start)
		\end{itemize}
		\item What we are not looking for: 
			\begin{itemize}
			\item tools, labor efficiency enhancing tools
			\item business or production methods and techniques
			\item new chemicals or medical drugs
			\end{itemize}			
	\end{itemize}
\vspace{0.6cm}
\textcolor{beamer@blendedblue}{\textbf{Our question to you:}}
	\begin{itemize}	
	\item Does the patent we will show you, \textit{even just in a loose sense}, describe an automat?
	\end{itemize}
\end{frame}

\section{Coding}
\setcounter{subsection}{1} % add this after each \section{...} to start a new section of navigation circles

\begin{frame}\frametitle{Practical issues}
	\begin{itemize}	
	\item We will give you an Excel document containing a list of patent numbers such as: 7091471 or 7124853 or 9027105.
	\item Please go to one of the following websites: \\[0.1cm]
 \href{https://www.google.com/patents}{\texttt{https://www.google.com/patents}}\\[0.1cm]
\href{http://patft.uspto.gov/netahtml/PTO/search-bool.html}{\texttt{http://patft.uspto.gov/netahtml/PTO/search-bool.html}}\\[0.1cm]
	and enter the patent number
	\item We recommend using Google Patents first, as it has usually the nicer interface. If you cannot find it (this happens rarely), please try at the USPTO website.
	\item The right patent might not be the first one in the list. In Google Patents, you might find patents from other countries. You identify the right patent as the one starting with ``US". In the USPTO search interface, the right patent is often the last one in the list (don't ask us why...).
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Practical issues}
	\begin{itemize}	
	\item There are some warning signs, that you might have clicked on the wrong patent: if the main language is not in English (but for example in German or Chinese), then it's probably not an US patent.
	\item If the date of the patent grant text (also called publication date) is before 1976, then something might be wrong. We are only looking at patents that were granted in 1976 and the years after. The application dates can be earlier, though (sometimes a long time before 1976). 
	\item If there is a problem and you cannot figure it out, please indicate that in the comment box.
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Manual coding}
	\begin{itemize}	
	\item After you have found the patent text, please read through the patent grant text, with a particular emphasis on the abstract and the description and decide: is this an automation patent?
		\begin{itemize}
		\item If yes please also decide:
			\begin{itemize}
			\item Is this is a cognitive automation patent?
			\item Is this is a manual automation patent?
			\item Or both?
			\item Or neither?
			\end{itemize}
		\end{itemize}
	\item Please use 1 to encode a Yes and 0 to encode a No.
	\item There is also a comment field. Please try to avoid using this, but you can enter here if you encountered technical problems, if something seemed wrong to you or if you encountered some other problem.
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Excel table after filling it in}
\vspace{-1cm}
\begin{table}
\begin{small}
  \begin{threeparttable}
     \begin{tabular}{ccccl}
        \textbf{Patent number} & \textbf{Classification} & \textbf{Cognitive} & \textbf{Manual} & \textbf{Comment}  \tabularnewline
        \hline
        8851703	& 0  &  &  &	\tabularnewline
        7725116 & 0	 &  &  &	Technical problem\tabularnewline
        8975301 & 0	 &  &  &	\tabularnewline
        4716621 & 1	 & 1 &  &	Not sure\tabularnewline
        4789151 & 0	 &  &  & 	\tabularnewline
        4116621 & 1	 & 1 & 1 &	\tabularnewline
        6785151 & 0	 &  &  & 	\tabularnewline
        \hline
     \end{tabular}
  \end{threeparttable}
\end{small}
\end{table}
\vspace{0.5cm}
{\small \textcolor{mytextgrey}{Please note that these patents and numbers have not been checked so don't use them as an orientation for your coding. Also the proportion of patents classified as automation patents is probably not representative.} }

\end{frame}

\begin{frame}\frametitle{When you're done}
	\begin{itemize}	
		\item Please make sure your file is formatted the following way:\\[0.1cm]
\texttt{manual\textunderscore classif\textunderscore <FirstnameLastname>\textunderscore <year>-<month>-<day>.xlsx}\\[0.3cm]
		for example, for Lukas on the 11\textsuperscript{th} of May 2015 that would be:\\[0.1cm]
\texttt{manual\textunderscore classif\textunderscore LukasPuettmann\textunderscore 2015-05-11.xlsx}\\[0.3cm]
		\item and then send it back to us in an email to\\[0.1cm] \hspace{1cm}\href{mailto:lukas.puettmann@uni-bonn.de}{\texttt{lukas.puettmann@uni-bonn.de}}\\[0.1cm]
	\end{itemize}
\end{frame}

\section{Examples}
\setcounter{subsection}{1} % add this after each \section{...} to start a new section of navigation circles

\begin{frame}\frametitle{An automation patent}
	\begin{itemize}	
	\item Hello
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Not an automation patent}
	\begin{itemize}	
	\item 6905407, Gaming device having display with interacting multiple rotating members and indicator
	\item 5552597, Hand-held scanner having adjustable light path 
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Not an automation patent (close call)}
	\begin{itemize}	
	\item 8457498, Methods and apparatus for target identification
	\end{itemize}
\end{frame}

\section{FAQs}
\setcounter{subsection}{1} % add this after each \section{...} to start a new section of navigation circles

\begin{frame}\frametitle{FAQs}
	\begin{itemize}	
	\item \textit{What am I looking for?}\\[0.1cm]
	We ask you to classify patents as to whether they are about automation or not. If they are about automation, we also ask you whether they are cognitive or manual.
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{FAQs}
	\begin{itemize}	
	\item \textit{What should I write to say Yes?}\\[0.1cm]
	Please write 1.
	\item \textit{What should I write to say No?}\\[0.1cm]
	Please write 0.
	\item \textit{Can I also leave the field blank if it's a No?}\\[0.1cm]
	We ask you to please fill out the classification with either a 0 or a 1. If that's somehow not possible, please write this into the comment box. The fields cognitive and manual you can leave empty to signal a No.
		\end{itemize}
\end{frame}

\begin{frame}\frametitle{FAQs}
	\begin{itemize}	
	\item \textit{What if I don't find the patent text?}\\[0.1cm]
	Have you tried both search masks? If you cannot find it on either one, please write this in the comment box.
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{FAQs}
	\begin{itemize}	
	\item \textit{Should I read the whole patent?}\\[0.1cm]
	No, that is likely not necessary (if the text is not very short). We recommend to concentrate on: the title, the abstract (which is a short overview), the beginning of the description and the beginning of the background. It also helps to look at the images. It can also help to see which patents were cited (they are likely similar to the one you're looking at) and who applied for it (you might know the firm and infer something from that).
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{FAQs}
	\begin{itemize}	
	\item \textit{Should I enter whether a patent is cognitive or manual even if I don't think the patent is an automation patent?}\\[0.1cm]
	No, that is not necessary, you can just leave this field empty.
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{FAQs}
	\begin{itemize}	
	\item \textit{Do I need any technical knowledge to judge a patent?}\\[0.1cm]
	Patent texts are written in a technical language and they can be very complex. We only ask you to classify the patent as an automation patent if you are \textit{reasonably sure} that the patent is an automation patent. 
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{FAQs}
	\begin{itemize}	
	\item \textit{How often do you expect me to use the comment box?}\\[0.1cm]
	We would like you to use that box as little as possible. Please only use that box to mark if you encounter any problems or if you are absolutely not sure how to classify the patent.
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{FAQs}
	\begin{itemize}	
	\item \textit{What if I don't understand what the patent is about?}\\[0.1cm]
	No problem, just judge if you think this patent might have something to contribute to automation. If you cannot find that out, it's probably a no. If you're not sure, please indicate this in the comment box.
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{FAQs}
	\begin{itemize}	
	\item \textit{How long should I take for a patent?}\\[0.1cm]
	We are not quite sure about that yet. If it's less 30 seconds per patent, it's probably too fast. If it's more than 5 minutes per patent, it's probably too slow. But the speed will likely differ between people. It's often much faster to see that a patent has \textit{nothing} to do with automation, rather than deciding it is an automation patent. It's ok (and indeed recommendable) to take more time for that.
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{FAQs}
	\begin{itemize}	
	\item \textit{Am I doing you a favor if I classify more patents as Yes?}\\[0.1cm]
	Unfortunately not. We might use your classifications to help us classify other patents. This will not work, if patents are wrongly classified. Also, it makes our work more credible if our manual classifications have a high quality.
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{FAQs}
	\begin{itemize}	
	\item \textit{Should I hurry and try to classify as many patents as possible?}\\[0.1cm]
	No, please take your time. It's much more important for us for your coding to accurate than to code more patents. Don't worry if things are going slow, it's ok to classify only few patents. If you're tired and you think you might be making mistakes, then please take a break or stop.
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{FAQs}
	\begin{itemize}	
	\item \textit{What if cannot find the patent?}\\[0.1cm]
Sometimes patent don't show up in \href{https://www.google.com/patents}{\texttt{Google Patents}}, but they do appear in the \href{http://patft.uspto.gov/netahtml/PTO/search-bool.html}{\texttt{USPTO}} search interace. In Google Patents you might get several hits and you should search for the patent number starting with US and then the number we give you. On the USPTO website, the patent you're looking for usually shows up as the last hit (don't ask us why). If after some searching you cannot find it, please just write something like ``Cannot find" in the comment box.
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{FAQs}
	\begin{itemize}	
	\item \textit{Question?}\\[0.1cm]
	Answer.
	\item \textit{Question?}\\[0.1cm]
	Answer.
	\end{itemize}
\end{frame}

\section{Thank you.}
\setcounter{subsection}{1} % add this after each \section{...} to start a new section of navigation circles
\begin{frame}
	Last and most importantly: \textbf{Thank you for your help}. We appreciate it very much.
\end{frame}

\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-05-12 manual_classification/manual_coding_handbook.tex
Analyze manual classifications and compare with automatical classifications

@@
 \textit{University of Bonn}}
-\date{\textbf{Version: \today}}
+\date{\today}
 
@@
 \begin{frame}\frametitle{Introduction}
-%\vspace{-0.5cm}
 	\begin{itemize}	
-		\item Automation of tasks affects jobs to a large degree. 
-		\item Therefore we need a good measure to be able to analyze the impact of automation on labor markets.
-		\item In this research project, we design a new indicator of automation based on searching patent grant texts for keywords.
-		\item We check this computer-based analysis by \textbf{manual coding}, the guidelines for which we describe in this document.
+		\item This document lays out the guidelines for the manual coding of patent texts.
+		\item This is used as both a reference and to train and guide human auditors.
 	\end{itemize}
@@
 	\begin{itemize}	
-	\item We study U.S. patents 1976-2015.
-	\item Utility patents only.
-The patents we exclude have a patent number starting with a letter: D (design patents), PP (plant patents), R (reissue patents), T (defensive publications), H (statutory invention registration), X (very early patents)
+	\item We study all U.S. utility patents 1976-2015.
+	\item We randomly pick an equal number of patents from all years.
+	\item We assign each auditor patents. 50\% of patents are assigned to multiple auditors.
+	\item The articles are passed in random order (so not in chronological order).
 	\end{itemize}
@@
 	and enter the patent number
-	\item We recommend using Google Patents first, as it has usually the nicer interface. If you cannot find it (this happens rarely), please try at the USPTO website.
+	\item We recommend using Google Patents first, as it has the nicer interface. If you cannot find it (this happens rarely), please try at the USPTO search interface.
 	\item The right patent might not be the first one in the list.
@@
 	\item After you have found the patent text, please read through the patent grant text, with a particular emphasis on the abstract and the description and decide: is this an automation patent?
-		\begin{itemize}
-		\item If yes please also decide:
-			\begin{itemize}
-			\item Is this is a cognitive automation patent?
-			\item Is this is a manual automation patent?
-			\item Or both?
-			\item Or neither?
-			\end{itemize}
-		\end{itemize}
 	\item Please use 1 to encode a Yes and 0 to encode a No.
@@
 	\end{itemize}
+\end{frame}
+
+\begin{frame}\frametitle{Sub-classification}
+If Yes (the patent is an automation patent) please also decide:
+	\begin{itemize}
+	\item Is this is a analytical (automation) patent? We mean by that if it does something cognitive and non-physical.
+	\item Is this is a manual (automation) patent? So is it a physical machine?
+	\end{itemize}
+It can also be both. If you think it's neither, that's ok, but please indicate why in the comment box (we haven't encountered that case yet).
 \end{frame}
@@
         8851703	& 0  &  &  &	\tabularnewline
-        7725116 & 0	 &  &  &	Technical problem\tabularnewline
+        7725116 & 	 &  &  &	Technical problem\tabularnewline
         8975301 & 0	 &  &  &	\tabularnewline
-        4716621 & 1	 & 1 &  &	Not sure\tabularnewline
-        4789151 & 0	 &  &  & 	\tabularnewline
+        4716621 & 1	 & 1 &  &	\tabularnewline
+        4789151 & 0	 &  &  & 	Not sure\tabularnewline
         4116621 & 1	 & 1 & 1 &	\tabularnewline
@@
 		\item Please make sure your file is formatted the following way:\\[0.1cm]
-\texttt{manual\textunderscore classif\textunderscore <FirstnameLastname>\textunderscore <year>-<month>-<day>.xlsx}\\[0.3cm]
+\texttt{manclass\textunderscore <FirstnameLastname>\textunderscore <year>-<month>-<day>.xlsx}\\[0.3cm]
 		for example, for Lukas on the 11\textsuperscript{th} of May 2015 that would be:\\[0.1cm]
-\texttt{manual\textunderscore classif\textunderscore LukasPuettmann\textunderscore 2015-05-11.xlsx}\\[0.3cm]
+\texttt{manclass\textunderscore LukasPuettmann\textunderscore 2015-05-11.xlsx}\\[0.3cm]
 		\item and then send it back to us in an email to\\[0.1cm] \hspace{1cm}\href{mailto:lukas.puettmann@uni-bonn.de}{\texttt{lukas.puettmann@uni-bonn.de}}\\[0.1cm]
@@
 
-\begin{frame}\frametitle{An automation patent}
+\begin{frame}\frametitle{Example: automation patent (a clear case)}
+\href{https://www.google.de/patents/US5531156?dq=5531156&hl=en&sa=X&ei=KPtRVd3vHYOssgGe2YGQDg&ved=0CCAQ6AEwAA}{\texttt{5531156: Automatic taco machine}}
 	\begin{itemize}	
-	\item Hello
+	\item We classify this as an automation patent as it automates the process of cooking tacos, keeping them fresh and filling them with minimal human input or interaction. 
+	\item We classify this as not a cognitive, but as a manual automation patent.
 	\end{itemize}
@@
 
-\begin{frame}\frametitle{Not an automation patent}
+\begin{frame}\frametitle{Example: automation patent (a clear case)}
+\href{https://www.google.de/patents/US6362849?dq=6362849&hl=en&sa=X&ei=k-9RVZjJHMmcsgHbvYCIDA&ved=0CCAQ6AEwAA}{\texttt{6362849: Color measuring method and device }}
 	\begin{itemize}	
-	\item 6905407, Gaming device having display with interacting multiple rotating members and indicator
-	\item 5552597, Hand-held scanner having adjustable light path 
+	\item This patent contains a video camera, a processor and the program to measure color.
+We classify this as an automation patent as it works independently of carrying out the process of recognizing colors.
+	\item We classify this as both a cognitive and a manual automation patent.
 	\end{itemize}
@@
 
-\begin{frame}\frametitle{Not an automation patent (close call)}
+\begin{frame}\frametitle{Example: automation patent (a borderline case)}
+\href{https://www.google.de/patents/US8497785?dq=8497785&hl=en&sa=X&ei=2O5RVYD3L4GWsAGt0oCgCA&ved=0CCEQ6AEwAA}{\texttt{8497785: Handheld electronic device and method for disambiguation of text input providing suppression of low probability artificial variants}}
+	\begin{itemize}	
+	\item We classify as an automation patent, as it automates the process of recognizing complete words that are likely to occur from only a few letters that are entered.
+	\item What makes this a boarderline case is that it is close to being a tool that is used interactively by people.
+	\item As the patent contains both a small machine and the software to it with we classify this as both a cognitive and a manual automation patent
+	\end{itemize}
+\end{frame}
+
+\begin{frame}\frametitle{Example: automation patent (a borderline case)}
+\href{https://www.google.de/patents/US6905407?dq=6905407&hl=en&sa=X&ei=XfJRVYDIAYmosAGKx4CwCw&ved=0CCEQ6AEwAA}{\texttt{6905407: Gaming device having display with interacting multiple rotating members and indicator}}
+	\begin{itemize}	
+	\item This is an automation patent as it automates the process of dealing hands for ``including but not limited to the games of slot, poker, keno, blackjack, bunco and checkers".
+What makes this a borderline case is the high degree of human interaction with the machine.
+Nevertheless, once the machine has been installed, it operates independently and with a high degree of sophistication.
+	\item It contains both the physical machine (which also has moving parts) and the software (like programs to play games with) to run on it, so we classify it as both cognitive and manual.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}\frametitle{Example: \textbf{not} automation patent (a borderline case)}
 	\begin{itemize}	
 	\item 8457498, Methods and apparatus for target identification
+	\end{itemize}
+\end{frame}
+
+\begin{frame}\frametitle{Example: \textbf{not} automation patent (a borderline case)}
+\href{https://www.google.de/patents/US5505821?dq=5505821&hl=en&sa=X&ei=DvRRVbmqEomrsAHtxIE4&ved=0CCEQ6AEwAA}{\texttt{5505821: Turbulence insert of a papermaking machine}}
+	\begin{itemize}	
+	\item This is part of a machine which automates the process of paper making. However, it is only a small part of it related to the flow of materials.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}\frametitle{Example: \textbf{not} automation patent (a clear case)}
+\href{https://www.google.de/patents/US5552597?dq=5552597&hl=en&sa=X&ei=mvtRVYXNNomjsAHFi4GYBw&ved=0CCEQ6AEwAA}{\texttt{5552597: Hand-held scanner having adjustable light path }}
+	\begin{itemize}	
+	\item This is a small hand-held version of a larger desktop scanner which delivers an electronic version of printed text. 
+	\end{itemize}
+\end{frame}
+
+\begin{frame}\frametitle{Example: \textbf{not} automation patent (a clear case)}
+\href{https://www.google.de/patents/US7878521?dq=7878521&hl=en&sa=X&ei=VfZRVe_QMsGzswHZtYHwDA&ved=0CCEQ6AEwAA}{\texttt{7878521: Bicycle frame with device cavity }}
+	\begin{itemize}	
+	\item This is a bicycle frame that has a cavity for sensors. It does not automate anything.
 	\end{itemize}
@@
 	We ask you to please fill out the classification with either a 0 or a 1.
-If that's somehow not possible, please write this into the comment box.
+The 0 is important for us to see that you made a conscious decision about it.
+If that's somehow not possible, leave it empty and please write this into the comment box.
 The fields cognitive and manual you can leave empty to signal a No.
@@
 	\begin{itemize}	
-	\item \textit{What if I don't find the patent text?}\\[0.1cm]
-	Have you tried both search masks? If you cannot find it on either one, please write this in the comment box.
+	\item \textit{What if cannot find the patent?}\\[0.1cm]
+Sometimes patent don't show up in \href{https://www.google.com/patents}{\texttt{Google Patents}}, but they do appear in the \href{http://patft.uspto.gov/netahtml/PTO/search-bool.html}{\texttt{USPTO}} search interace.
+In Google Patents you might get several hits and you should search for the patent number starting with US and then the number we give you.
+On the USPTO website, the patent you're looking for usually shows up as the last hit.
+If after some searching you cannot find it, please just write something like ``Cannot find" in the comment box.
 	\end{itemize}
@@
 	No, that is likely not necessary (if the text is not very short).
-We recommend to concentrate on: the title, the abstract (which is a short overview), the beginning of the description and the beginning of the background.
+We recommend to concentrate on: the title, the abstract (which is a short overview) and the description.
+The beginning of the description is often most interesting and there is sometimes a section called ``background" which is informative.
 It also helps to look at the images.
 It can also help to see which patents were cited (they are likely similar to the one you're looking at) and who applied for it (you might know the firm and infer something from that).
+You can also use outside knowledge (like Googling a term) if you think that helps.
 	\end{itemize}
@@
 	\item \textit{Should I enter whether a patent is cognitive or manual even if I don't think the patent is an automation patent?}\\[0.1cm]
-	No, that is not necessary, you can just leave this field empty.
+	No, that is not necessary, you can just leave the field empty if the patent is not an automation patent.
 	\end{itemize}
@@
 We only ask you to classify the patent as an automation patent if you are \textit{reasonably sure} that the patent is an automation patent.
+If you absolutely cannot figure it out, then consider writing that in the comment box.
 	\end{itemize}
@@
 	\item \textit{How often do you expect me to use the comment box?}\\[0.1cm]
-	We would like you to use that box as little as possible. Please only use that box to mark if you encounter any problems or if you are absolutely not sure how to classify the patent.
+	Please only use that box to mark if you encounter any problems or if you are absolutely not sure how to classify the patent.
 	\end{itemize}
@@
 	No problem, just judge if you think this patent might have something to contribute to automation.
-If you cannot find that out, it's probably a no.
-If you're not sure, please indicate this in the comment box.
+If you're not sure \textit{beyond reasonable doubt} (to use such a legal term), please indicate this in the comment box.
 	\end{itemize}
@@
 	We are not quite sure about that yet.
-If it's less 30 seconds per patent, it's probably too fast.
+If it's less 30 seconds on average per patent, it's probably too fast.
 If it's more than 5 minutes per patent, it's probably too slow.
@@
 It's often much faster to see that a patent has \textit{nothing} to do with automation, rather than deciding it is an automation patent.
-It's ok (and indeed recommendable) to take more time for that.
+It's ok (and indeed recommended by us) to take more time for those patents that you think might be automation patents.
 	\end{itemize}
@@
 	Unfortunately not.
-We might use your classifications to help us classify other patents.
-This will not work, if patents are wrongly classified.
-Also, it makes our work more credible if our manual classifications have a high quality.
+We might use your classifications to classify more patents.
+This will not work if patents are wrongly classified.
+Also, it makes our work more credible if the manual classifications have a high quality.
 	\end{itemize}
@@
 
-\begin{frame}\frametitle{FAQs}
-	\begin{itemize}	
-	\item \textit{What if cannot find the patent?}\\[0.1cm]
-Sometimes patent don't show up in \href{https://www.google.com/patents}{\texttt{Google Patents}}, but they do appear in the \href{http://patft.uspto.gov/netahtml/PTO/search-bool.html}{\texttt{USPTO}} search interace.
-In Google Patents you might get several hits and you should search for the patent number starting with US and then the number we give you.
-On the USPTO website, the patent you're looking for usually shows up as the last hit (don't ask us why).
-If after some searching you cannot find it, please just write something like ``Cannot find" in the comment box.
-	\end{itemize}
-\end{frame}
-
-\begin{frame}\frametitle{FAQs}
-	\begin{itemize}	
-	\item \textit{Question?}\\[0.1cm]
-	Answer.
-	\item \textit{Question?}\\[0.1cm]
-	Answer.
-	\end{itemize}
-\end{frame}
-
 \section{Thank you.}
@@
 \begin{frame}
-	Last and most importantly: \textbf{Thank you for your help}. We appreciate it very much.
+	Last and most importantly: \\[0.2cm]
+	\textbf{Thank you for your help}. We appreciate it very much.
 \end{frame}

### 2015-05-12 manual_classification/analyze_manclass.m

@@ -1,0 +1,75 @@
+close all
+clear all
+clc
+
+
+
+% Load excel file
+[manclass_data, txt, ~] = xlsread('manclass_FULL.xlsx');
+
+
+% Figure out how many patents have been classified yet
+indic_automat = manclass_data(:, 3);
+
+last_codpt = find(isnan(indic_automat), 1) - 1;
+indic_automat = indic_automat(1:last_codpt);
+
+% Truncate until last coded patent
+manclass_data = manclass_data(1:last_codpt, :);
+
+
+% Check if there any NaN's left in the vector of classifications
+if any(isnan(indic_automat))
+    fprintf('Some patents not classified (NaN): %d.\n', ...
+        find(isnan(indic_automat)))
+end
+
+
+nr_codpt = length(indic_automat);
+sum_automat = sum(indic_automat);
+share_automat = sum_automat / nr_codpt;
+
+fprintf('Number patents manually coded: %d, of those %d (%3.2f) automation patents.\n', ...
+    nr_codpt, sum_automat, share_automat)
+
+
+% Compare manual classification with automated keyword search
+nr_keyword_find = manclass_data(:, 7); % extract number of keyword matches
+% Find patents with at least 1 match
+pat_1match = (nr_keyword_find > 0); % the plus converts logical to double 
+
+pos_manclass_automat = find(indic_automat);
+pos_pat_1match = find(pat_1match);
+
+complete_class = union(pos_pat_1match, pos_manclass_automat);
+overlap_class = intersect(pos_pat_1match, pos_manclass_automat);
+differ_class = setdiff(complete_class, ...
+    overlap_class);
+
+fprintf('___________________________________________________________\n');
+fprintf('<strong>Comparison of manual and automatical patent classification</strong>\n');
+fprintf('  \n')
+fprintf('Same classifications: %d (%3.2f).\n', length(overlap_class), ...
+    length(overlap_class) / length(complete_class))
+fprintf('Differing classifications: %d (%3.2f).\n', length(differ_class), ...
+    length(differ_class) / length(complete_class))
+
+
+
+% Analyze those patents that were manually classified as automation patents
+matches_manclasspt = nr_keyword_find(pos_manclass_automat)
+
+matches_rest = nr_keyword_find(not(indic_automat))
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2015-05-18 manual_classification/manual_coding_handbook.tex
Work on manual classification

@@
 	\item We assign each auditor patents. 50\% of patents are assigned to multiple auditors.
-	\item The articles are passed in random order (so not in chronological order).
+	\item The list of patents is given to the auditor in random (not chronological) order.
 	\end{itemize}
@@
 		\begin{itemize}	
-		\item $^1$: could be a a physical machine, computer program, a robot.
+		\item $^1$: could be a physical machine, computer program, a robot.
 		\item $^2$: could be a production process, the act of creation, composing a song, altering something, measuring something, a task
@@
 			\begin{itemize}
-			\item tools, labor efficiency enhancing tools
+			\item tools, labor efficiency-enhancing machines
 			\item business or production methods and techniques
@@
 	\item Please use 1 to encode a Yes and 0 to encode a No.
-	\item There is also a comment field.
-Please try to avoid using this, but you can enter here if you encountered technical problems, if something seemed wrong to you or if you encountered some other problem.
+	\item There is also a comment field. Please try to avoid using this, but you can enter here if you had technical problems, if something seemed wrong to you or if you encountered some other problem.
 	\end{itemize}
@@
 	\begin{itemize}
-	\item Is this is a analytical (automation) patent? We mean by that if it does something cognitive and non-physical.
+	\item Is this is an analytical (automation) patent? We mean by that if it does something cognitive and non-physical.
 	\item Is this is a manual (automation) patent? So is it a physical machine?
@@
 {\small \textcolor{mytextgrey}{Please note that these patents and numbers have not been checked so don't use them as an orientation for your coding.
-Also the proportion of patents classified as automation patents is probably not representative.} }
+Also the proportion of patents classified as automation patents might not be representative.} }
 
@@
 \begin{frame}\frametitle{Example:  \textbf{not} automation patent (a borderline case)}
+\href{https://www.google.de/patents/US8457498?dq=8457498&hl=en&sa=X&ei=BgRSVYnsIMmdsgG_tYHQDQ&ved=0CCAQ6AEwAA}{\texttt{8457498: Methods and apparatus for target identification}}
 	\begin{itemize}	
-	\item 8457498, Methods and apparatus for target identification
+	\item This patent is a system to differentiate enemy and friendly troops through a system of back and forth communication. 
+	\item We classify this as not an automation patent, but it's a close call.
+The process automates the identification of enemy targets.
+However, it does so in a large scale back and forth communication manner that more resembles a business operation process.
+This is not what we understand as an automat.
 	\end{itemize}
@@
 	\begin{itemize}	
-	\item \textit{What if cannot find the patent?}\\[0.1cm]
-Sometimes patent don't show up in \href{https://www.google.com/patents}{\texttt{Google Patents}}, but they do appear in the \href{http://patft.uspto.gov/netahtml/PTO/search-bool.html}{\texttt{USPTO}} search interace.
+	\item \textit{What if I cannot find the patent?}\\[0.1cm]
+Sometimes patents don't show up in \href{https://www.google.com/patents}{\texttt{Google Patents}}, but they do appear in the \href{http://patft.uspto.gov/netahtml/PTO/search-bool.html}{\texttt{USPTO}} search interace.
 In Google Patents you might get several hits and you should search for the patent number starting with US and then the number we give you.
@@
 	\item \textit{How long should I take for a patent?}\\[0.1cm]
-	We are not quite sure about that yet.
+	There is no clear number here.
 If it's less 30 seconds on average per patent, it's probably too fast.
@@
 
-\section{Thank you.}
-\setcounter{subsection}{1} % add this after each \section{...} to start a new section of navigation circles
-\begin{frame}
-	Last and most importantly: \\[0.2cm]
-	\textbf{Thank you for your help}. We appreciate it very much.
-\end{frame}
-
 \end{document}

### 2015-05-18 manual_classification/analyze_manclass.m

@@ -6,16 +6,30 @@ clc
 
 % Load excel file
 [manclass_data, txt, ~] = xlsread('manclass_FULL.xlsx');
+% [manclass_data, txt, ~] = xlsread('new_manclass_FULL.xlsx');
+
+
+
 
 
 % Figure out how many patents have been classified yet
 indic_automat = manclass_data(:, 3);
 
-last_codpt = find(isnan(indic_automat), 1) - 1;
-indic_automat = indic_automat(1:last_codpt);
+% if any((indic_automat ~= 0) | (indic_automat ~= 1) | (indic_automat ~= 1))
+%     warning('There should be only 0 and 1 and NaN here.')
+%     
+%     disp('Replace 99 with 0.')
+%     pos99 = find(indic_automat == 99);
+%     indic_automat(pos99) = 0;
+% end
 
-% Truncate until last coded patent
-manclass_data = manclass_data(1:last_codpt, :);
+last_codpt = find(isnan(indic_automat), 1) - 1;
+
+if not(isempty(last_codpt))
+    % Truncate until last coded patent
+    indic_automat = indic_automat(1:last_codpt);
+    manclass_data = manclass_data(1:last_codpt, :);
+end
 
 
 % Check if there any NaN's left in the vector of classifications
@@ -41,6 +55,9 @@ pat_1match = (nr_keyword_find > 0); % the plus converts logical to double
 pos_manclass_automat = find(indic_automat);
 pos_pat_1match = find(pat_1match);
 
+% Calculate the overall agreement rate
+agree_rate = sum(indic_automat == pat_1match) / nr_codpt;
+
 complete_class = union(pos_pat_1match, pos_manclass_automat);
 overlap_class = intersect(pos_pat_1match, pos_manclass_automat);
 differ_class = setdiff(complete_class, ...
@@ -49,17 +66,21 @@ differ_class = setdiff(complete_class, ...
 fprintf('___________________________________________________________\n');
 fprintf('<strong>Comparison of manual and automatical patent classification</strong>\n');
 fprintf('  \n')
-fprintf('Same classifications: %d (%3.2f).\n', length(overlap_class), ...
-    length(overlap_class) / length(complete_class))
-fprintf('Differing classifications: %d (%3.2f).\n', length(differ_class), ...
-    length(differ_class) / length(complete_class))
+
+fprintf('Overall agreement: %d/%d (%3.2f).\n', ...
+    sum(indic_automat == pat_1match), nr_codpt, agree_rate)
[…]

### 2015-05-19 manual_classification/analyze_manclass.m
Work on manual coding

@@ -5,23 +5,17 @@ clc
 
 
 % Load excel file
-[manclass_data, txt, ~] = xlsread('manclass_FULL.xlsx');
-% [manclass_data, txt, ~] = xlsread('new_manclass_FULL.xlsx');
-
-
-
+[manclass_data, txt, ~] = xlsread('manclass_consolidated.xlsx');
 
 
 % Figure out how many patents have been classified yet
 indic_automat = manclass_data(:, 3);
 
-% if any((indic_automat ~= 0) | (indic_automat ~= 1) | (indic_automat ~= 1))
-%     warning('There should be only 0 and 1 and NaN here.')
-%     
-%     disp('Replace 99 with 0.')
-%     pos99 = find(indic_automat == 99);
-%     indic_automat(pos99) = 0;
-% end
+
+if any(not((indic_automat == 1) | (indic_automat == 0)))
+    warning('There should be only 0 and 1 here.')
+end
+
 
 last_codpt = find(isnan(indic_automat), 1) - 1;
 
@@ -43,9 +37,6 @@ nr_codpt = length(indic_automat);
 sum_automat = sum(indic_automat);
 share_automat = sum_automat / nr_codpt;
 
-fprintf('Number patents manually coded: %d, of those %d (%3.2f) automation patents.\n', ...
-    nr_codpt, sum_automat, share_automat)
-
 
 % Compare manual classification with automated keyword search
 nr_keyword_find = manclass_data(:, 7); % extract number of keyword matches
@@ -60,17 +51,31 @@ agree_rate = sum(indic_automat == pat_1match) / nr_codpt;
 
 complete_class = union(pos_pat_1match, pos_manclass_automat);
 overlap_class = intersect(pos_pat_1match, pos_manclass_automat);
-differ_class = setdiff(complete_class, ...
-    overlap_class);
+differ_class = setdiff(complete_class, overlap_class);
+
+manual1_automatic0 = setdiff(pos_manclass_automat, pos_pat_1match);
+automatic1_manual0 = setdiff(pos_pat_1match, pos_manclass_automat);
+
 
 fprintf('___________________________________________________________\n');
 fprintf('<strong>Comparison of manual and automatical patent classification</strong>\n');
 fprintf('  \n')
 
+fprintf('Number patents manually coded: %d.\n', ...
+    nr_codpt)
+fprintf('Of those manually classified as automation patents: %d (%3.2f) .\n', ...
+   sum_automat, share_automat)
[…]

### 2015-05-19 manual_classification/manual_coding_handbook.tex
Work on manual coding
Add version number when drawing patents for manual classification and include new example (Van Halen Guitar Patent)

@@
 \definecolor{mygrey}{rgb}{0.85,0.85,0.85} % make grey for the table
+\definecolor{myred}{rgb}{0.85,0.1,0.1} % make grey for the table
 \definecolor{mytextgrey}{rgb}{0.25, 0.25, 0.25} % make grey for text
@@
 			\item new chemicals or medical drugs
+			\item parts of computers or of sofware that does not directly contribute to automation
 			\end{itemize}			
@@
 \begin{frame}\frametitle{Example: automation patent (a clear case)}
-\href{https://www.google.de/patents/US5531156?dq=5531156&hl=en&sa=X&ei=KPtRVd3vHYOssgGe2YGQDg&ved=0CCAQ6AEwAA}{\texttt{5531156: Automatic taco machine}}
+\href{https://www.google.de/patents/US5531156}{\texttt{5531156: Automatic taco machine}}
 	\begin{itemize}	
@@
 \begin{frame}\frametitle{Example: automation patent (a clear case)}
-\href{https://www.google.de/patents/US6362849?dq=6362849&hl=en&sa=X&ei=k-9RVZjJHMmcsgHbvYCIDA&ved=0CCAQ6AEwAA}{\texttt{6362849: Color measuring method and device }}
+\href{https://www.google.de/patents/US6362849}{\texttt{6362849: Color measuring method and device }}
 	\begin{itemize}	
-	\item This patent contains a video camera, a processor and the program to measure color.
-We classify this as an automation patent as it works independently of carrying out the process of recognizing colors.
+	\item This patent contains a video camera, a processor and the program to measure color. We classify this as an automation patent as it independently recognizes colors.
 	\item We classify this as both a cognitive and a manual automation patent.
@@
 \begin{frame}\frametitle{Example: automation patent (a borderline case)}
-\href{https://www.google.de/patents/US8497785?dq=8497785&hl=en&sa=X&ei=2O5RVYD3L4GWsAGt0oCgCA&ved=0CCEQ6AEwAA}{\texttt{8497785: Handheld electronic device and method for disambiguation of text input providing suppression of low probability artificial variants}}
+\href{https://www.google.de/patents/US8497785}{\texttt{8497785: Handheld electronic device and method for disambiguation of text input providing suppression of low probability artificial variants}}
 	\begin{itemize}	
@@
 \begin{frame}\frametitle{Example: automation patent (a borderline case)}
-\href{https://www.google.de/patents/US6905407?dq=6905407&hl=en&sa=X&ei=XfJRVYDIAYmosAGKx4CwCw&ved=0CCEQ6AEwAA}{\texttt{6905407: Gaming device having display with interacting multiple rotating members and indicator}}
+\href{https://www.google.de/patents/US6905407}{\texttt{6905407: Gaming device having display with interacting multiple rotating members and indicator}}
 	\begin{itemize}	
@@
 
-\begin{frame}\frametitle{Example:  \textbf{not} automation patent (a borderline case)}
-\href{https://www.google.de/patents/US8457498?dq=8457498&hl=en&sa=X&ei=BgRSVYnsIMmdsgG_tYHQDQ&ved=0CCAQ6AEwAA}{\texttt{8457498: Methods and apparatus for target identification}}
+\begin{frame}\frametitle{Example:  \textcolor{myred}{\textbf{not}} automation patent (a borderline case)}
+\href{https://www.google.de/patents/US8457498}{\texttt{8457498: Methods and apparatus for target identification}}
 	\begin{itemize}	
@@
 
-\begin{frame}\frametitle{Example: \textbf{not} automation patent (a borderline case)}
-\href{https://www.google.de/patents/US5505821?dq=5505821&hl=en&sa=X&ei=DvRRVbmqEomrsAHtxIE4&ved=0CCEQ6AEwAA}{\texttt{5505821: Turbulence insert of a papermaking machine}}
+\begin{frame}\frametitle{Example: \textcolor{myred}{\textbf{not}} automation patent (a borderline case)}
+\href{https://www.google.de/patents/US5505821}{\texttt{5505821: Turbulence insert of a papermaking machine}}
 	\begin{itemize}	
@@
 
-\begin{frame}\frametitle{Example: \textbf{not} automation patent (a clear case)}
-\href{https://www.google.de/patents/US5552597?dq=5552597&hl=en&sa=X&ei=mvtRVYXNNomjsAHFi4GYBw&ved=0CCEQ6AEwAA}{\texttt{5552597: Hand-held scanner having adjustable light path }}
+\begin{frame}\frametitle{Example: \textcolor{myred}{\textbf{not}} automation patent (a clear case)}
+\href{https://www.google.de/patents/US5552597}{\texttt{5552597: Hand-held scanner having adjustable light path }}
 	\begin{itemize}	
@@
 
-\begin{frame}\frametitle{Example: \textbf{not} automation patent (a clear case)}
-\href{https://www.google.de/patents/US7878521?dq=7878521&hl=en&sa=X&ei=VfZRVe_QMsGzswHZtYHwDA&ved=0CCEQ6AEwAA}{\texttt{7878521: Bicycle frame with device cavity }}
+\begin{frame}\frametitle{Example: \textcolor{myred}{\textbf{not}} automation patent (a clear case)}
+\href{https://www.google.de/patents/US7878521}{\texttt{7878521: Bicycle frame with device cavity }}
 	\begin{itemize}	
 	\item This is a bicycle frame that has a cavity for sensors. It does not automate anything.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}\frametitle{Example: \textcolor{myred}{\textbf{not}} automation patent (a clear case)}
+\href{http://www.google.com/patents/US4656917}{\texttt{4656917: Musical instrument support }}
+	\begin{itemize}	
+	\item This patent by the guitarist Van Halen describes a device that allows for more creative guitar handling and playing.
+It does not automate anything, but rather enables a person to do something she could not previously do.
 	\end{itemize}
@@
 If after some searching you cannot find it, please just write something like ``Cannot find" in the comment box.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}\frametitle{FAQs}
+	\begin{itemize}	
+	\item \textit{Can I enter something else like 1? if I'm not quite sure?}\\[0.1cm]
+	No, please write your remarks in the comment box if you're not sure. 
 	\end{itemize}

### 2015-05-19 manual_classification/draw_patents4manclass.m

@@ -58,6 +58,9 @@ end
 % Rearrange elements randomly
 rand_pat = rand_pat(randperm(length(rand_pat)), :);
 
+% Assign a version number
+vnum = 4;
+
 % Create an Excel document which gives the patent number of the drawn
 % patent
 col_header = {'Patent number', 'Year', ...
@@ -66,7 +69,7 @@ col_header = {'Patent number', 'Year', ...
 data4exc = [rand_pat(:, 1:2), nan(length(rand_pat), ...
     length(col_header) - 3), rand_pat(:, 3)];
 output_matrix = [col_header; num2cell(data4exc)];
-save_name = 'manclass_FULL.xlsx';
+save_name = horzcat('manclass_FULL_v', num2str(vnum), '.xlsx');
 xlswrite(save_name, output_matrix);
 fprintf('Saved: %s.\n', save_name)
 
@@ -77,7 +80,7 @@ col_header = {'Patent number', 'Year', ...
 data4exc = [rand_pat(:, 1:2), nan(length(rand_pat), ...
     length(col_header) - 2)];
 output_matrix = [col_header; num2cell(data4exc)];
-save_name = 'manclass.xlsx';
+save_name = horzcat('manclass_v', num2str(vnum), '.xlsx');
 xlswrite(save_name, output_matrix);
 fprintf('Saved: %s.\n', save_name)
 

### 2015-05-19 manual_classification/manual_coding_handbook.tex
Automatically download files from Google Patents

@@
 
-\begin{frame}
-\textcolor{beamer@blendedblue}{\textbf{Definition:}}
-
+\begin{frame}\frametitle{Definition}
 	\begin{itemize}	
@@
 		\begin{itemize}	
-		\item $^1$: could be a physical machine, computer program, a robot.
+		\item $^1$: could be a physical machine, computer program, an algorithm, a robot.
 		\item $^2$: could be a production process, the act of creation, composing a song, altering something, measuring something, a task
-		\item $^3$: without human interference (apart from that needed for supervision, maintenance or at the start)
+		\item $^3$: without human interference (apart from that needed for supervision, maintenance or at the start) and with a reasonable amount of completeness (so it should not be a minor part of a computer or machine even if that was what we think of as an automat).
 		\end{itemize}
@@
 			\item new chemicals or medical drugs
+			\item parts of machines (e.g. a tube) that does not automate or that is not a part of an automat
 			\item parts of computers or of sofware that does not directly contribute to automation
+			\item highly abstract algorithms (a potential application in automation should be recognizable)
 			\end{itemize}			
 	\end{itemize}
+\end{frame}
+
+\begin{frame}\frametitle{Our question to you}
 \vspace{0.6cm}
-\textcolor{beamer@blendedblue}{\textbf{Our question to you:}}
 	\begin{itemize}	
@@
 	and enter the patent number
-	\item We recommend using Google Patents first, as it has the nicer interface. If you cannot find it (this happens rarely), please try at the USPTO search interface.
+	\item We recommend using Google Patents first, as it has the nicer interface.
+If you cannot find it (this happens rarely) or if the patent grant text looks incomplete (also rare), please try at the USPTO search interface.
 	\item The right patent might not be the first one in the list.
@@
 
+\begin{frame}\frametitle{Example: automation patent (a clear case)}
+\href{https://www.google.de/patents/US8857476}{\texttt{8857476 : Coinfusion apparatus }}
+	\begin{itemize}	
+	\item This machine independently ``mix[es] and adjust[s] medical agent such as anticancer drug".
+This avoids the need for humans exposing themselves to dangerous materials.
+This means that  ``a part or the entirety of the coinfusion processing can be performed automatically by [the invention]".
+	\item We classify this as a manual machine.
+	\end{itemize}
+\end{frame}
+
 \begin{frame}\frametitle{Example: automation patent (a borderline case)}
@@
 	\item This is a bicycle frame that has a cavity for sensors. It does not automate anything.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}\frametitle{Example: \textcolor{myred}{\textbf{not}} automation patent (a clear case)}
+\href{https://www.google.de/patents/US4323683}{\texttt{4323683: Process for making pyridinethione salts }}
+	\begin{itemize}	
+	\item This is a manufacturing method to make salts used against dandruff.
+It is for various reasons not an automation patent: it is not a device (but a production method), it is not clear if a machine or a human will produce it
 	\end{itemize}
@@
 	No problem, just judge if you think this patent might have something to contribute to automation.
-If you're not sure \textit{beyond reasonable doubt} (to use such a legal term), please indicate this in the comment box.
+If you're not sure \textit{beyond reasonable doubt} (to borrow such a legal term), please indicate this in the comment box.
 	\end{itemize}

### 2015-05-19 download_patent_data/download_patent_data.py

@@ -1,0 +1,18 @@
+# http://yizeng.me/2014/05/23/download-pdf-files-automatically-in-firefox-using-selenium-webdriver/
+
+from selenium import webdriver 
+from selenium.webdriver.firefox.firefox_profile import FirefoxProfile
+
+profile = FirefoxProfile ()
+profile.set_preference("browser.download.panel.shown", False) 
+
+profile.set_preference("browser.download.folderList", 2) # 2 means specify custom location
+profile.set_preference("browser.download.manager.showWhenStarting", False)
+profile.set_preference("browser.download.dir", 'D:\\') # choose folder to download to
+profile.set_preference("browser.helperApps.neverAsk.saveToDisk",'application/octet-stream')
+
+driver = webdriver.Firefox(firefox_profile=profile)
+driver.get('https://www.google.com/googlebooks/uspto-patents-grants-text.html#2015')
+
+filename = driver.find_element_by_xpath('//a[contains(text(),"ipg150106.zip")]') # use loop to list all zip files
+filename.click()

### 2015-05-21 manual_classification/analyze_manclass.m
Make automatic contingency table of classifications

@@ -86,6 +86,35 @@ matches_manclasspt = nr_keyword_find(pos_manclass_automat);
 matches_rest = nr_keyword_find(not(indic_automat));
 
 
+%% Save contingency table to .tex
+
+% Print to .txt file in Latex format
+printname = 'table_contingency_classfc.tex';
+
+FID = fopen(printname, 'w');
+
+fprintf(FID,'\\begin{table}\n');
+fprintf(FID,'\\begin{small}\n');
+fprintf(FID,'\\begin{threeparttable}\n');
+fprintf(FID,'\\caption{{\\normalsize Manual vs. automated classification}}\n');
+fprintf(FID,'\\begin{tabular}{ll|ll|l}\n');
+
+fprintf(FID, '& \\multicolumn{4}{c}{Automated} \\tabularnewline[0.1cm]\n');
+fprintf(FID, '& & No & Yes &   \\tabularnewline\n');
+fprintf(FID, '\\cline{2-5}\n');
+fprintf(FID, '\\parbox[t]{2mm}{\\multirow{2}{*}{\\rotatebox[origin=c]{90}{Manual}}} & No & 148 & 30 & 178 \\tabularnewline\n');
+fprintf(FID, '& Yes & 31 & 30 & 61 \\tabularnewline\n');
+fprintf(FID, '\\cline{2-5}\n');
+fprintf(FID, '&  & 209 & 60 & 239 \\tabularnewline\n');
+
+
+fprintf(FID,'\\end{tabular}\n');
+fprintf(FID,'\\end{threeparttable}\n');
+fprintf(FID,'\\end{small}\n');
+fprintf(FID,'\\end{table}\n');
+fclose(FID); 
+
+fprintf('Saved: %s.\n', printname)
 
 
 

### 2015-05-21 manual_classification/draw_patents4manclass.m

@@ -16,7 +16,7 @@ year_start = 1976;
 year_end = 2015;
 nr_years = length(year_start:year_end);
 week_start = 1;
-nr_draw_pat_yr = 10; % how many patents to draw from every year
+nr_draw_pat_yr = 1; % how many patents to draw from every year
 
 
 
@@ -59,7 +59,7 @@ end
 rand_pat = rand_pat(randperm(length(rand_pat)), :);
 
 % Assign a version number
-vnum = 4;
+vnum = 5;
 
 % Create an Excel document which gives the patent number of the drawn
 % patent

### 2015-05-27 RUN_SEVERAL_LOCALLY.m
Track 2 more files:
- a script to tie everything together (if used without waf)
- a script to look-up data on specific patents (in this case keyword matches)

@@ -1,0 +1,111 @@
+clear all
+close all
+clc
+
+
+addpath('functions')
+
+
+% Close all previously openned files
+check_open_files
+disp('Close all files.')
+fclose('all');
+
+
+
+%% Define email parameters
+sender = 'lukas.puettmann@gmail.com';
+password = 'egGiegGG';
+recipient = 'lukas.puettmann@gmx.de';
+
+
+%% Set email connection settings
+setpref('Internet', 'E_mail', sender);
+setpref('Internet', 'SMTP_Server', 'smtp.gmail.com');
+setpref('Internet', 'SMTP_Username', sender);
+setpref('Internet', 'SMTP_Password', password);
+
+props = java.lang.System.getProperties;
+props.setProperty('mail.smtp.auth', 'true');
+props.setProperty('mail.smtp.socketFactory.class', ...
+                  'javax.net.ssl.SSLSocketFactory');
+props.setProperty('mail.smtp.socketFactory.port', '465');
+
+
+
+%% Delete previous log file
+if exist('CommandLineTextLog.txt', 'file') == 2
+    delete('CommandLineTextLog.txt')
+    disp('Delete previous log file.')
+else
+    disp('Make new file CommandLineTextLog.txt.')
+end
+
+
+%% Run the analysis for the first part (1976-2001)
+tic
+
+% Save command line input/output to text file
+diary('CommandLineTextLog.txt'); 
+
+% Run analysis
+find_patents_part1
+
+part_run_time = toc;
+fprintf('Part 1 finished, time: %d seconds (%d minutes).\n', ...
+    round(part_run_time), round(part_run_time/60))
+
+diary('off'); % stop saving command line text
+
+% Send email stating that first part has finished. Also send the command
+% line text (input and output) in the body of the message.
+subject = 'Matlab status report: part 1 (1976-2001) finished.';
+message_text_log = textread('CommandLineTextLog.txt', '%s', 'delimiter', '\n');
+sendmail(recipient, subject, message_text_log);
+
+
+
+
+%% Run the analysis for the second part (2002-2004)
+tic
+
+% Save command line input/output to text file
+diary('CommandLineTextLog.txt'); 
+
+% Run analysis
+find_patents_part2
+
+part_run_time = toc;
+fprintf('Part 2 finished, time: %d seconds (%d minutes).\n', ...
+    round(part_run_time), round(part_run_time/60))
+
+diary('off'); % stop saving command line text
+
+% Send email stating that first part has finished. Also send the command
[…]

### 2015-05-27 manual_classification/analyze_manclass.m

@@ -23,6 +23,8 @@ if not(isempty(last_codpt))
     % Truncate until last coded patent
     indic_automat = indic_automat(1:last_codpt);
     manclass_data = manclass_data(1:last_codpt, :);
+    
+    warning('TRUNCATING SAMPLE.')
 end
 
 
@@ -96,10 +98,10 @@ FID = fopen(printname, 'w');
 fprintf(FID,'\\begin{table}\n');
 fprintf(FID,'\\begin{small}\n');
 fprintf(FID,'\\begin{threeparttable}\n');
-fprintf(FID,'\\caption{{\\normalsize Manual vs. automated classification}}\n');
+fprintf(FID,'\\caption{{\\normalsize Manual vs. computerized classification}}\n');
 fprintf(FID,'\\begin{tabular}{ll|ll|l}\n');
 
-fprintf(FID, '& \\multicolumn{4}{c}{Automated} \\tabularnewline[0.1cm]\n');
+fprintf(FID, '& \\multicolumn{4}{c}{Computerized} \\tabularnewline[0.1cm]\n');
 fprintf(FID, '& & No & Yes &   \\tabularnewline\n');
 fprintf(FID, '\\cline{2-5}\n');
 fprintf(FID, '\\parbox[t]{2mm}{\\multirow{2}{*}{\\rotatebox[origin=c]{90}{Manual}}} & No & %d & %d & %d \\tabularnewline\n', nr_codpt - sum_automat - length(automatic1_manual0), length(automatic1_manual0), nr_codpt - sum_automat);
@@ -114,9 +116,118 @@ fprintf(FID,'\\end{small}\n');
 fprintf(FID,'\\end{table}\n');
 fclose(FID); 
 
+fprintf('___________________________________________________________\n');
 fprintf('Saved: %s.\n', printname)
 
 
+
+%% Errors over time
+year_start = 1976;
+year_end = 2015;
+
+
+% Extract
+for ix_year=year_start:year_end
+    t = ix_year - year_start + 1;
+    
+    yr_pos = find(ix_year == manclass_data(:, 2));
+    
+    yr_indic_automat = manclass_data(yr_pos, 3);
+    yr_pat_1match = manclass_data(yr_pos, end)>0;
+    
+    classifstat.number(t) = length(yr_pos);
+    classifstat.summanclass(t) = sum(yr_indic_automat);
+    classifstat.sumpat1match(t) = sum(yr_pat_1match);
[…]

### 2015-05-27 manual_classification/correct4missing_matches_in_manclass.m

@@ -1,0 +1,76 @@
+
+close all
+clear all
+clc
+
+addpath('../cleaned_matches');
+
+
+% Load excel file
+[manclass_data, txt, ~] = xlsread('manclass_FULL_v1.xlsx');
+
+
+[~, ix_sort] = sort(manclass_data(:,2));
+
+
+manclass_data = manclass_data(ix_sort, :);
+
+patent_data = manclass_data(:,1:2);
+
+year_start = 1976;
+year_end = 2015;
+nr_years = length(year_start:year_end);
+
+all_matches = [];
+
+ix_extract_start = 1;
+
+
+for ix_year=year_start:year_end
+    
+    % Load matches
+    % -------------------------------------------------------------
+    load_file_name = horzcat('patsearch_results_', num2str(ix_year));
+    load(load_file_name)
+    
+    patentyr_numbers = patsearch_results(:, 1);
+    patentyr_matches = patsearch_results(:, 2);
+    
+    nr_yearlength = length(find(manclass_data(:, 2) == ix_year));
+    
+    ix_extract_stop = ix_extract_start + nr_yearlength - 1;
+    
+    extract_patyrnr = patent_data(ix_extract_start:ix_extract_stop, 1);
+    
+    if length(extract_patyrnr) ~= nr_yearlength
+        warning('Check right length.')
+    end
+    
+    j_matches = zeros(nr_yearlength,1);
+    
+    for j=1:length(extract_patyrnr)
+        extract_me = extract_patyrnr(j,:);
+        extract_me = num2str(extract_me);
+        ix_pos_ex = find(strcmp(patentyr_numbers, extract_me));
+        j_matches(j) = patentyr_matches{ix_pos_ex};
+    end
+    all_matches = [all_matches; j_matches];
+    
+    ix_extract_start = ix_extract_stop + 1;
+    
+    fprintf('Year finished: %d.\n', ix_year)
+end
+
+
+%%
+if not(size(manclass_data,1) == size(all_matches, 1))
+    warning('Should be same size.')
+end
+
+manclass_data = [manclass_data, all_matches];
+
+xlswrite('new_manclass_FULL.xlsx', manclass_data)
+
+
+
+

### 2015-05-27 manual_classification/analyze_manclass.m
Try excluding some tech classes, move preparation
of manual classification data to separate script.

@@ -4,43 +4,46 @@ clc
 
 addpath('../functions')
 
-% Load excel file
-[manclass_data, txt, ~] = xlsread('manclass_consolidated.xlsx');
+%% Load previously extracted data
+load('manclass_data.mat')
 
+
+%% Delete those patents with technology numbers some industries
+delete_technr = [430, 431, 514, 600, 800];
+technr = manclass_data(:, 8);
+delete_pat_pos = find(ismember(technr, delete_technr));
+
+del_pat = manclass_data(delete_pat_pos, :);
+del_pat_manual1 = find(del_pat(:, 3));
+del_pat_automatic1 = find(del_pat(:, 7)>0);
+del_pat_manual1_automatic1 = intersect(del_pat_manual1, del_pat_automatic1);
+del_pat_manual1_automatic0 = setdiff(del_pat_manual1, del_pat_automatic1);
+del_pat_automatic1_manual0 = setdiff(del_pat_automatic1, del_pat_manual1);
+
+fprintf('___________________________________________________________\n');
+fprintf('<strong>Discarded technologies</strong>\n');
+fprintf(' \n')
+fprintf('Delete %d patents.\n', length(delete_pat_pos))
+fprintf('Of those: \n')
+fprintf('\t %d = manual: 1, automatic: 1.\n', length(del_pat_manual1_automatic1))
+fprintf('\t %d = manual: 1, automatic: 0.\n', length(del_pat_manual1_automatic0))
+fprintf('\t %d = automatic: 1, manual: 0.\n', length(del_pat_automatic1_manual0))
+fprintf(' ')
+
+manclass_data(delete_pat_pos, :) = [];
+
+
+%% Transform variables
 
 % Figure out how many patents have been classified yet
 indic_automat = manclass_data(:, 3);
-
-
-if any(not((indic_automat == 1) | (indic_automat == 0)))
-    warning('There should be only 0 and 1 here.')
-end
-
-
-last_codpt = find(isnan(indic_automat), 1) - 1;
-
-if not(isempty(last_codpt))
-    % Truncate until last coded patent
-    indic_automat = indic_automat(1:last_codpt);
-    manclass_data = manclass_data(1:last_codpt, :);
-    
-    warning('TRUNCATING SAMPLE.')
-end
-
-
-% Check if there any NaN's left in the vector of classifications
-if any(isnan(indic_automat))
-    fprintf('Some patents not classified (NaN): %d.\n', ...
[…]

### 2015-05-27 manual_classification/prepare_manclass.m

@@ -1,0 +1,107 @@
+close all
+clear all
+clc
+
+addpath('../functions')
+
+% Load excel file
+[manclass_data, ~, ~] = xlsread('manclass_consolidated.xlsx');
+
+% Figure out how many patents have been classified yet
+indic_automat = manclass_data(:, 3);
+
+
+%% Make some checks
+if any(not((indic_automat == 1) | (indic_automat == 0)))
+    warning('There should be only 0 and 1 here.')
+end
+
+last_codpt = find(isnan(indic_automat), 1) - 1;
+
+if not(isempty(last_codpt))
+    % Truncate until last coded patent
+    warning('TRUNCATING SAMPLE.')
+    indic_automat = indic_automat(1:last_codpt);
+    manclass_data = manclass_data(1:last_codpt, :);
+end
+
+% Check if there any NaN's left in the vector of classifications
+if any(isnan(indic_automat))
+    fprintf('Some patents not classified (NaN): %d.\n', ...
+        find(isnan(indic_automat)))
+end
+
+
+%% Sort data by years. IMPORTANT: We'll later loop through them.
+[~, ix_sort] = sort(manclass_data(:,2));
+manclass_data = manclass_data(ix_sort, :);
+
+patent_numbers = manclass_data(:, 1);
+patent_years = manclass_data(:, 2);
+
+year_start = 1976;
+year_end = 2015;
+nr_years = length(year_start:year_end);
+
+all_technr = [];
+
+ix_extract_start = 1;
+
+
+%% Extract the technology numbers for patents
+for ix_year=year_start:year_end
+    
+    % Load matches
+    % -------------------------------------------------------------
+    load_file_name = horzcat('patsearch_results_', num2str(ix_year));
+    load(load_file_name)
+    
+    patentyr_numbers = patsearch_results(:, 1);
+    patentyr_technr = patsearch_results(:, 3);
+    
+    nr_yearlength = length(find(patent_years == ix_year));
+    
+    ix_extract_stop = ix_extract_start + nr_yearlength - 1;
+    
+    extract_patyrnr = patent_numbers(ix_extract_start:ix_extract_stop);
+    
+    if length(extract_patyrnr) ~= nr_yearlength
+        warning('Check if length is right.')
+    end
+    
+    j_technr = zeros(nr_yearlength,1);
+    
+    for j=1:length(extract_patyrnr)
+        extract_me = extract_patyrnr(j,:);
+        extract_me = num2str(extract_me);
[…]

### 2015-05-27 manual_classification/analyze_manclass.m
Fix bug (duplicates in manual codings)

@@ -9,7 +9,8 @@ load('manclass_data.mat')
 
 
 %% Delete those patents with technology numbers some industries
-delete_technr = [430, 431, 514, 600, 800];
+% delete_technr = [430, 431, 435, 514, 600, 800];
+delete_technr = [430, 431, 435, 514, 800];
 technr = manclass_data(:, 8);
 delete_pat_pos = find(ismember(technr, delete_technr));
 
@@ -23,7 +24,8 @@ del_pat_automatic1_manual0 = setdiff(del_pat_automatic1, del_pat_manual1);
 fprintf('___________________________________________________________\n');
 fprintf('<strong>Discarded technologies</strong>\n');
 fprintf(' \n')
-fprintf('Delete %d patents.\n', length(delete_pat_pos))
+fprintf('Delete %d/%d (%3.2f) patents.\n', length(delete_pat_pos), ...
+    size(manclass_data, 1), length(delete_pat_pos)/size(manclass_data, 1))
 fprintf('Of those: \n')
 fprintf('\t %d = manual: 1, automatic: 1.\n', length(del_pat_manual1_automatic1))
 fprintf('\t %d = manual: 1, automatic: 0.\n', length(del_pat_manual1_automatic0))

### 2015-05-27 manual_classification/prepare_manclass.m

@@ -3,6 +3,7 @@ clear all
 clc
 
 addpath('../functions')
+addpath('../cleaned_matches')
 
 % Load excel file
 [manclass_data, ~, ~] = xlsread('manclass_consolidated.xlsx');
@@ -12,6 +13,14 @@ indic_automat = manclass_data(:, 3);
 
 
 %% Make some checks
+if length(unique(manclass_data(:, 1))) ~= length(manclass_data(:, 1))
+    warning('There are duplicate patents.')
+end
+
+if any(not((indic_automat == 1) | (indic_automat == 0)))
+    warning('There should be only 0 and 1 here.')
+end
+
 if any(not((indic_automat == 1) | (indic_automat == 0)))
     warning('There should be only 0 and 1 here.')
 end

### 2015-05-28 manual_classification/analyze_manclass.m
Now have full 300 manually coded patents

@@ -9,6 +9,7 @@ load('manclass_data.mat')
 
 
 %% Delete those patents with technology numbers some industries
+
 delete_technr = [430, % Radiation Imagery Chemistry
                  431, % Combustion
                  435, % Chemistry: Molecular Biology and Microbiology
@@ -17,6 +18,7 @@ delete_technr = [430, % Radiation Imagery Chemistry
                 % 600, % Surgery
                 % 606, % Surgery
                  800]; % Multicellar Living Organisms
+             
 technr = manclass_data(:, 8);
 delete_pat_pos = find(ismember(technr, delete_technr));
 
@@ -149,7 +151,6 @@ fprintf('Saved: %s.\n', printname)
 % -------------------------------------------------------------------
 year_start = 1976;
 year_end = 2015;
-
 
 % Extract
 for ix_year=year_start:year_end

### 2015-06-09 manual_classification/manual_coding_handbook.tex
Make automatic contingency table of classifications
..

@@
 
-\definecolor{mygrey}{rgb}{0.85,0.85,0.85} % make grey for the table
-\definecolor{myred}{rgb}{0.85,0.1,0.1} % make grey for the table
-\definecolor{mytextgrey}{rgb}{0.25, 0.25, 0.25} % make grey for text
+\definecolor{mygrey}{rgb}{0.85,0.85,0.85}
+\definecolor{myred}{rgb}{0.85,0.1,0.1}
+\definecolor{mytextgrey}{rgb}{0.25, 0.25, 0.25}
+\definecolor{mytextyellow}{rgb}{1, 1, 0.9}
 % --------------------------------------------------------
@@
 
+\begin{frame}\frametitle{Tradeoffs}
+\vspace{0.6cm}
+	\begin{itemize}	
+	\item Tool vs. automat
+	\item Part of larger process vs. independent device
+	\item Highly abstract vs. an application to automation is apparent
+	\end{itemize}
+\end{frame}
+
 \section{Coding}
@@
 	\item Please go to one of the following websites: \\[0.1cm]
- \href{https://www.google.com/patents}{\texttt{https://www.google.com/patents}}\\[0.1cm]
-\href{http://patft.uspto.gov/netahtml/PTO/search-bool.html}{\texttt{http://patft.uspto.gov/netahtml/PTO/search-bool.html}}\\[0.1cm]
+ \href{https://www.google.com/patents}{\texttt{\textcolor{myred}{https://www.google.com/patents}}}\\[0.1cm]
+\href{http://patft.uspto.gov/netahtml/PTO/search-bool.html}{\texttt{\textcolor{myred}{http://patft.uspto.gov/netahtml/PTO/search-bool.html}}}\\[0.1cm]
 	and enter the patent number

### 2015-06-19 manual_classification/analyze_manclass.m
Compare algorithms in contingency table

@@ -4,146 +4,173 @@ clc
 
 addpath('../functions')
 
-%% Parameters
+% Parameters
 year_start = 1976;
 year_end = 2015;
 
 
-%% Load previously extracted data
+% Load previously extracted data
 load('manclass_data.mat')
 
 
-%% Delete those patents with technology numbers some industries
+% Iterate through classification algorithm set-ups
+% ========================================================================
 
-delete_technr = [430, % Radiation Imagery Chemistry
-                 431, % Combustion
-                 435, % Chemistry: Molecular Biology and Microbiology
-                 514, % Drug, Bio-affecting and Body Treating Compositions
-                 530, % Chemistry: Natural Resins or Derivatives; Peptides or Proteins; ...
-                % 600, % Surgery
-                % 606, % Surgery
-                 800]; % Multicellar Living Organisms
-             
-technr = manclass_data(:, 8);
-delete_pat_pos = find(ismember(technr, delete_technr));
+nr_alg = 2;
 
-del_pat = manclass_data(delete_pat_pos, :);
-del_pat_manual1 = find(del_pat(:, 3));
-del_pat_automatic1 = find(del_pat(:, 7)>0);
-del_pat_manual1_automatic1 = intersect(del_pat_manual1, del_pat_automatic1);
-del_pat_manual1_automatic0 = setdiff(del_pat_manual1, del_pat_automatic1);
-del_pat_automatic1_manual0 = setdiff(del_pat_automatic1, del_pat_manual1);
+for i=1:nr_alg
 
-fprintf('___________________________________________________________\n');
-fprintf('<strong>Discarded technologies</strong>\n');
-fprintf(' \n')
-fprintf('Delete %d/%d (%3.2f) patents.\n', length(delete_pat_pos), ...
-    size(manclass_data, 1), length(delete_pat_pos)/size(manclass_data, 1))
-fprintf('Of those: \n')
-fprintf('\t %d = manual: 1, automatic: 1.\n', length(del_pat_manual1_automatic1))
-fprintf('\t %d = manual: 1, automatic: 0.\n', length(del_pat_manual1_automatic0))
-fprintf('\t %d = automatic: 1, manual: 0.\n', length(del_pat_automatic1_manual0))
-fprintf(' ')
+    if i==2
+        % Delete those patents with technology numbers some industries
+        delete_technr = [430, % Radiation Imagery Chemistry
+                         431, % Combustion
+                         435, % Chemistry: Molecular Biology and Microbiology
[…]

### 2015-06-19 manual_classification/make_manclass_contingency_table.m
Contingency table

@@ -17,42 +17,37 @@ FID = fopen(printname, 'w');
 fprintf(FID,'\\begin{table}\n');
 fprintf(FID,'\\begin{small}\n');
 fprintf(FID,'\\begin{threeparttable}\n');
-fprintf(FID,'\\caption{{\\normalsize Contingency table}}\n');
+fprintf(FID,'\\caption{{\\normalsize Comparison of classification algorithms}}\n');
 fprintf(FID,'\\label{table:contingency_classifications}\n');
-fprintf(FID,'\\begin{tabular}{ll|ll|ll|ll|ll}\n');
-
+fprintf(FID,'\\begin{tabular}{llllllllll}\n');
+fprintf(FID, '\\multicolumn{9}{c}{\\textit{Contingency table}} \\tabularnewline\n');
+fprintf(FID, '\\midrule');
+fprintf(FID, '&  &  & &  & &  &  &  \\tabularnewline[-0.3cm]\n');
 fprintf(FID, '& & \\multicolumn{7}{c}{Computerized} \\tabularnewline[0.1cm]\n');
+fprintf(FID, '\\cline{3-9}\n');
 fprintf(FID, '& & \\multicolumn{3}{c}{$A_1$} & & \\multicolumn{3}{c}{$A_2$} \\tabularnewline[0.1cm]\n');
-fprintf(FID, '& & No & Yes & & & No & Yes &  \\tabularnewline\n');
+fprintf(FID, '& & \\multicolumn{1}{|l}{No}  & \\multicolumn{1}{l|}{Yes} & & & \\multicolumn{1}{|l}{No} & \\multicolumn{1}{l|}{Yes} &  \\tabularnewline\n');
 fprintf(FID, '\\cline{2-5} \\cline{7-9}\n');
-fprintf(FID, '\\parbox[t]{2mm}{\\multirow{2}{*}{\\rotatebox[origin=c]{90}{Manual}}} & No & %d & %d & %d & & %d & %d & %d \\tabularnewline\n', conttab.val(1,:,1), conttab.val(1,:,2));
-fprintf(FID, '& Yes & %d & %d & %d & & %d & %d & %d \\tabularnewline\n', conttab.val(2,:,1), conttab.val(2,:,2));
[…]

### 2015-06-19 manual_classification/make_manclass_contingency_table.m
Table is nice

@@ -32,14 +32,14 @@ fprintf(FID, '\\parbox[t]{2mm}{\\multirow{2}{*}{\\rotatebox[origin=c]{90}{Manual
 fprintf(FID, '& Yes & \\multicolumn{1}{|l}{%d} & \\multicolumn{1}{l|}{%d} & %d & & \\multicolumn{1}{|l}{%d} & \\multicolumn{1}{l|}{%d} & %d \\tabularnewline\n', conttab.val(2,:,1), conttab.val(2,:,2));
 fprintf(FID, '\\cline{2-5} \\cline{7-9}\n');
 fprintf(FID, '&  & \\multicolumn{1}{|l}{%d} & \\multicolumn{1}{l|}{%d} & %d & & \\multicolumn{1}{|l}{%d} & \\multicolumn{1}{l|}{%d} & %d \\tabularnewline\n', conttab.val(3,:,1), conttab.val(3,:,2));
-fprintf(FID, '&  &  & &  & &  &  &  \\tabularnewline[0.3cm]\n');
+fprintf(FID, '&  &  & &  & &  &  &  \\tabularnewline[-0.1cm]\n');
 fprintf(FID, '\\cline{3-5} \\cline{7-9}\n');
-fprintf(FID, '& Accuracy & \\multicolumn{3}{r}{$\\frac{%d + %d}{%d} = %3.2f$} & & \\multicolumn{3}{r}{$\\frac{%d + %d}{%d} = %3.2f$}  \\tabularnewline\n', conttab.stats{1,:,1}, conttab.stats{1,:,2});
-fprintf(FID, '& Precision & \\multicolumn{3}{r}{$\\frac{%d}{%d} = %3.2f$} & & \\multicolumn{3}{r}{$\\frac{%d}{%d} = %3.2f$} \\tabularnewline\n', conttab.stats{2,:,1}, conttab.stats{2,:,2});
-fprintf(FID, '& Recall & \\multicolumn{3}{r}{$\\frac{%d}{%d} = %3.2f$} & & \\multicolumn{3}{r}{$\\frac{%d}{%d} = %3.2f$} \\tabularnewline\n', conttab.stats{3,:,1}, conttab.stats{3,:,2});
[…]

### 2015-06-19 manual_classification/make_manclass_contingency_table.m
Work on contingency table

@@ -19,29 +19,37 @@ fprintf(FID,'\\begin{small}\n');
 fprintf(FID,'\\begin{threeparttable}\n');
 fprintf(FID,'\\caption{{\\normalsize Comparison of classification algorithms}}\n');
 fprintf(FID,'\\label{table:contingency_classifications}\n');
-fprintf(FID,'\\begin{tabular}{llllllllll}\n');
-fprintf(FID, '\\multicolumn{9}{c}{\\textit{Contingency table}} \\tabularnewline\n');
-fprintf(FID, '\\midrule');
-fprintf(FID, '&  &  & &  & &  &  &  \\tabularnewline[-0.3cm]\n');
-fprintf(FID, '& & \\multicolumn{7}{c}{Computerized} \\tabularnewline[0.1cm]\n');
-fprintf(FID, '\\cline{3-9}\n');
-fprintf(FID, '& & \\multicolumn{3}{c}{$A_1$} & & \\multicolumn{3}{c}{$A_2$} \\tabularnewline[0.1cm]\n');
-fprintf(FID, '& & \\multicolumn{1}{|l}{No}  & \\multicolumn{1}{l|}{Yes} & & & \\multicolumn{1}{|l}{No} & \\multicolumn{1}{l|}{Yes} &  \\tabularnewline\n');
-fprintf(FID, '\\cline{2-5} \\cline{7-9}\n');
-fprintf(FID, '\\parbox[t]{2mm}{\\multirow{2}{*}{\\rotatebox[origin=c]{90}{Manual}}} & No & \\multicolumn{1}{|l}{%d} & \\multicolumn{1}{l|}{%d} & %d & & \\multicolumn{1}{|l}{%d} & \\multicolumn{1}{l|}{%d} & %d \\tabularnewline\n', conttab.val(1,:,1), conttab.val(1,:,2));
-fprintf(FID, '& Yes & \\multicolumn{1}{|l}{%d} & \\multicolumn{1}{l|}{%d} & %d & & \\multicolumn{1}{|l}{%d} & \\multicolumn{1}{l|}{%d} & %d \\tabularnewline\n', conttab.val(2,:,1), conttab.val(2,:,2));
-fprintf(FID, '\\cline{2-5} \\cline{7-9}\n');
[…]

### 2015-06-19 find_patents_part0.m
cont table

@@ -38,9 +38,10 @@ iter = ix_year - year_start + 1;
 
 choose_file_open = filenames{iter};
 
-% Load the patent text
+
 unique_file_identifier = fopen(choose_file_open, 'r');  
 
+%% Load the patent text
 tic
 open_file_aux = textscan(unique_file_identifier, '%s', ...
     'delimiter', '\n');
@@ -51,19 +52,24 @@ file_str = open_file_aux{1,1};
 
 
 %% Inspect files
+
+%% Print first lines of document
 clc
+disp('-------------------------------------------------------------------')
+pick_line2startshow = 1;
+nr_lines2show = 500;
+disp( file_str(pick_line2startshow:pick_line2startshow+nr_lines2show, :) );
+disp('-------------------------------------------------------------------')
 
-% Print first lines of document
-% disp( file_str(1:50, :) );
 
-
+%%
 nr_lines = size(file_str, 1);
 fprintf('Number of lines in document: %d (%3.1f million).\n', nr_lines, ...
     nr_lines / 1000000)
 
 
 % As a test, extract some lines from the document
-explore_lines = round(nr_lines * 1);
+explore_lines = round(nr_lines * 0.1);
 search_corpus = file_str(1:explore_lines, :);
 
 % 60.6 seconds for 28. mio lines, 55817 occurences. 

### 2015-06-19 manual_classification/make_manclass_contingency_table.m

@@ -17,7 +17,7 @@ FID = fopen(printname, 'w');
 fprintf(FID,'\\begin{table}\n');
 fprintf(FID,'\\begin{small}\n');
 fprintf(FID,'\\begin{threeparttable}\n');
-fprintf(FID,'\\caption{{\\normalsize Comparison of classification algorithms}}\n');
+fprintf(FID,'\\caption{{\\normalsize Comparison of classification algorithms with manual codingm}}\n');
 fprintf(FID,'\\label{table:contingency_classifications}\n');
 fprintf(FID,'\\begin{tabular}{lrllllllllllll}\n');
 fprintf(FID, '\\toprule');
@@ -37,17 +37,19 @@ fprintf(FID, '\\rule{0pt}{12pt}& Accuracy & \\multicolumn{3}{r}{$\\frac{%d + %d}
 fprintf(FID, '\\rule{0pt}{12pt}& Precision & \\multicolumn{3}{r}{$\\frac{%d}{%d} = %3.2f$} & & \\multicolumn{3}{r}{$\\frac{%d}{%d} = %3.2f$} & & \\multicolumn{3}{r}{$\\frac{%d}{%d} = %3.2f$} \\tabularnewline\n', conttab.stats{2,:,1}, conttab.stats{2,:,2}, conttab.stats{2,:,3});
 fprintf(FID, '\\rule{0pt}{12pt}& Recall & \\multicolumn{3}{r}{$\\frac{%d}{%d} = %3.2f$} & & \\multicolumn{3}{r}{$\\frac{%d}{%d} = %3.2f$}  & & \\multicolumn{3}{r}{$\\frac{%d}{%d} = %3.2f$} \\tabularnewline\n', conttab.stats{3,:,1}, conttab.stats{3,:,2}, conttab.stats{3,:,3});
 % Only print the beta once
-fprintf(FID, '\\rule{0pt}{12pt}& $F_{\\beta = %d}$ & \\multicolumn{3}{r}{%3.2f} & & \\multicolumn{3}{r}{%3.2f} & & \\multicolumn{3}{r}{%3.2f}\\tabularnewline\n', conttab.stats{4,:,1}(1), conttab.stats{4,:,1}(2), conttab.stats{4,:,2}(2), conttab.stats{4,:,3}(2));
[…]

### 2015-06-22 manual_classification/make_manclass_contingency_table.m
..

@@ -17,7 +17,7 @@ FID = fopen(printname, 'w');
 fprintf(FID,'\\begin{table}\n');
 fprintf(FID,'\\begin{small}\n');
 fprintf(FID,'\\begin{threeparttable}\n');
-fprintf(FID,'\\caption{{\\normalsize Comparison of classification algorithms with manual codingm}}\n');
+fprintf(FID,'\\caption{{\\normalsize Comparison of classification algorithms with manual coding}}\n');
 fprintf(FID,'\\label{table:contingency_classifications}\n');
 fprintf(FID,'\\begin{tabular}{lrllllllllllll}\n');
 fprintf(FID, '\\toprule');
@@ -60,4 +60,4 @@ fclose(FID);
 fprintf('Saved: %s.\n', printname)
 
 
-run '../copy_selected_files.m'
+%run '../copy_selected_files.m'

### 2015-06-24 functions/calculate_manclass_stats.m
Add tests for evaluation metrics

@@ -21,17 +21,13 @@ function classifstat = calculate_manclass_stats(correctClass, ...
 if (min(size(correctClass)) > 1) | (min(size(estimatClass)) > 1)
     error('Should be vector.')
 end
-    
 
-classifstat.computerClass = estimatClass;
 classifstat.nr_codpt = length(correctClass);
 classifstat.sum_automat = sum(correctClass);
 share_automat = classifstat.sum_automat / classifstat.nr_codpt;
 
-
 pos_manclass_automat = find(correctClass);
 pos_pat_1match = find(estimatClass);
-
 
 % Calculate area under (receiver operating) curve (AUROC)
 classifstat.auc = calculate_auc(correctClass, estimatClass);
@@ -52,7 +48,5 @@ classifstat.fmeasure = ((classifstat.evalbeta_squared + 1) * classifstat.precisi
     classifstat.recall) / (classifstat.evalbeta_squared * classifstat.precision + ...
     classifstat.recall);
 
-
 classifstat.manual1_automatic0 = setdiff(pos_manclass_automat, pos_pat_1match);
 classifstat.automatic1_manual0 = setdiff(pos_pat_1match, pos_manclass_automat);
-

### 2015-06-24 manual_classification/analyze_manclass.m

@@ -12,25 +12,25 @@ year_end = 2001;
 load('manclassData.mat')
 
 % Delete patents from some years 
-ixDelete = 252;
-
-% Delete entries for patents with those technologies
-manclassData.manAutomat(ixDelete:end) = [];
-manclassData.patentnr(ixDelete:end) = [];
-manclassData.classnr(ixDelete:end) = [];
-manclassData.year(ixDelete:end) = [];
-manclassData.coderID(ixDelete:end) = [];
-manclassData.coderDate(ixDelete:end) = [];
-manclassData.matches(ixDelete:end, :) = []; % this is a matrix
-manclassData.manCognitive(ixDelete:end) = [];
-manclassData.manManual(ixDelete:end) = [];
+% ixDelete = 252;
+% 
+% % Delete entries for patents with those technologies
+% manclassData.manAutomat(ixDelete:end) = [];
+% manclassData.patentnr(ixDelete:end) = [];
+% manclassData.classnr(ixDelete:end) = [];
+% manclassData.year(ixDelete:end) = [];
+% manclassData.coderID(ixDelete:end) = [];
+% manclassData.coderDate(ixDelete:end) = [];
+% manclassData.matches(ixDelete:end, :) = []; % this is a matrix
+% manclassData.manCognitive(ixDelete:end) = [];
+% manclassData.manManual(ixDelete:end) = [];
 
 
 
 % Iterate through classification algorithm set-ups
 % ========================================================================
 ix_keyword = 1;
-conttab.nr_alg = 1; % number of algorithms to compare
+conttab.nr_alg = 3; % number of algorithms to compare
 
 
 for i=1:conttab.nr_alg
@@ -98,7 +98,7 @@ for i=1:conttab.nr_alg
     % Calculate metrics that evaluate the precision of the classification
     % algorithm
     classifstat = calculate_manclass_stats(manclassData.manAutomat, ...
-        computerClass, 0.5)
+        computerClass, 0.5);
     
 
     % Errors over time
@@ -132,10 +132,10 @@ for i=1:conttab.nr_alg
     % -------------------------------------------------------------------
     conttab.val(:,:,i) = [classifstat.nr_codpt - classifstat.sum_automat - length(classifstat.automatic1_manual0), length(classifstat.automatic1_manual0), classifstat.nr_codpt - classifstat.sum_automat;
         length(classifstat.manual1_automatic0), classifstat.sum_automat - length(classifstat.manual1_automatic0), classifstat.sum_automat;
[…]

### 2015-06-24 manual_classification/make_manclass_contingency_table.m

@@ -56,3 +56,6 @@ fprintf(FID,'\\end{table}\n');
 fclose(FID); 
 
 fprintf('Saved: %s.\n', printname)
+
+
+run copy_selected_files.m

### 2015-06-24 test/test_calculate_manclass_stats.m

@@ -1,0 +1,49 @@
+function tests = test_calculate_manclass_stats
+    tests = functiontests(localfunctions);
+end
+
+function testnr_codpt(testCase)
+    correctClass = [0; 0; 1; 0; 1; 0; 0; 0; 1; 0; 1; 1; 0; 0];
+    estimatClass = [0; 0; 1; 0; 0; 0; 0; 1; 0; 0; 1; 1; 0; 0];
+       
+    alpha = 0.5;
+
+    classifstat = calculate_manclass_stats(correctClass, estimatClass, ...
+        alpha);
+    actSolution = classifstat.nr_codpt;
+
+    expSolution = 14;
+    
+    verifyEqual(testCase, actSolution, expSolution)
+end
+
+function testsum_automat(testCase)
+    correctClass = [0; 0; 1; 0; 1; 0; 0; 0; 1; 0; 1; 1; 0; 0];
+    estimatClass = [0; 0; 1; 0; 0; 0; 0; 1; 0; 0; 1; 1; 0; 0];
+       
+    alpha = 0.5;
+
+    classifstat = calculate_manclass_stats(correctClass, estimatClass, ...
+        alpha);
+    actSolution = classifstat.sum_automat;
+
+    expSolution = sum(correctClass);
+    
+    verifyEqual(testCase, actSolution, expSolution)
+end
+
+function testaccuracy(testCase)
+    correctClass = [0; 0; 1; 0; 1; 0; 0; 0; 1; 0; 1; 1; 0; 0];
+    estimatClass = [0; 0; 1; 0; 0; 0; 0; 1; 0; 0; 1; 1; 0; 0];
+       
+    alpha = 0.5;
+
+    classifstat = calculate_manclass_stats(correctClass, estimatClass, ...
+        alpha);
+    actSolution = classifstat.accuracy;
+
+    expSolution = sum((correctClass == estimatClass)) / ...
+        length(correctClass);
+    
+    verifyEqual(testCase, actSolution, expSolution)
+end

### 2015-06-24 testPatentAutomat.m

@@ -1,9 +1,8 @@
 function testPatentAutomat()
 
-
-
 run(test_count_nr_patents);
 run(test_count_elements_cell);
 run(test_delete_empty_cells);
 run(test_get_fullword_matches);
 run(test_auc);
+run(test_calculate_manclass_stats);

### 2015-07-23 RUN_SEVERAL_LOCALLY.m
Rewrite to work through all file type periods in one function

@@ -1,19 +1,0 @@
-clear all
-close all
-clc
-
-% Close all previously openned files
-fclose('all');
-
-% Set paths to all underlying directories
-setup_path
-
-% Make patent index for 2002-2004
-find_patents_part2
-
-disp('================================================================')
-
-% Search for keywords for 2002-2004
-analyze_patent_text_part2
-
-disp('================================================================')

### 2015-07-23 analyze_patent_text.m

@@ -1,0 +1,183 @@
+function patent_keyword_appear = analyze_patent_text(ix_year, ...
+    find_dictionary)
+
+% Save dictionary (to keep all information at one place)
+patent_keyword_appear.dictionary = find_dictionary;
+
+% Customize some settings for different file types
+if ix_year < 2002
+
+    
+elseif (ix_year >=2002) & (ix_year < 2005)
+
+    
+elseif ix_year >=2005
+    error('Not written yet for years 2005+.')
+end
+   
+% Initalize
+patent_metadata = []; 
+nr_keyword_appear = [];  
+save_line_keywordNAM = [];  
+
+tic
+
+week_start = 1;
+
+% Determine if there are 52 or 53 weeks in year
+week_end = set_weekend(ix_year); 
+
+% Build path to data
+build_data_path = set_data_path(ix_year);
+addpath(build_data_path);
+
+
+% Get names of files
+% -------------------------------------------------------------------
+liststruct = dir(build_data_path);
+filenames = {liststruct.name};
+filenames = filenames(3:end)'; % truncate first elements . and ..
+
+filenames = ifmac_truncate_more(filenames);
+
+check_filenames_format(filenames, ix_year, week_start, week_end)
+
+% Load patent_index for year
+% -------------------------------------------------------------------
+build_load_filename = horzcat('patent_index_', num2str(ix_year), ...
+    '.mat');
+load(build_load_filename)
+
+
+% Iterate through files of weekly patent grant text data
+% -------------------------------------------------------------------
+fprintf('Search through patent grant texts for year %d:\n', ix_year)
+
+for ix_week = week_start:week_end
+
+    % Get the index position of patent and the WKU number
+    % ----------------------------------------------------------------
+    patent_number = pat_ix{ix_week, 1};
+    ix_find = pat_ix{ix_week, 2};
+    show_row_NAM = pat_ix{ix_week, 3};
+    nr_patents = length(patent_number);   
+
+    % Load the patent text
+    choose_file_open = filenames{ix_week};
+    unique_file_identifier = fopen(choose_file_open, 'r');   
+
+    if unique_file_identifier == -1
+        warning('Matlab cannot open the file')
+    end
+
+    open_file_aux = textscan(unique_file_identifier, '%s', ...
+        'delimiter', '\n');
+    search_corpus = open_file_aux{1,1};
+
+
+    % Extract patent text
+    % ----------------------------------------------------------------
+    weekly_metadata = patent_number;
+
+    % Get empty cells next to the WKU patent numbers. 
[…]

### 2015-07-23 analyze_patent_text_part1.m

@@ -1,6 +1,5 @@
 close all
 clear all
-clc
 
 
 %% Define dictionary to search for
@@ -24,13 +23,13 @@ for ix_year = year_start:year_end
     nr_keyword_appear = []; 
     save_line_keywordNAM = [];  
     
-    tic
+
 
     week_start = 1;
 
     % Determine if there are 52 or 53 weeks in year 
     week_end = set_weekend(ix_year); 
-    week_end = 2
+
     % Build path to data
     build_data_path = set_data_path(ix_year);
     addpath(build_data_path);
@@ -76,11 +75,7 @@ for ix_year = year_start:year_end
 
         open_file_aux = textscan(unique_file_identifier, '%s', ...
             'delimiter', '\n');
-        file_str = open_file_aux{1,1};
-
-
-        % Define new search corpus as we might change some things about this
-        search_corpus = file_str; 
+        search_corpus = open_file_aux{1,1};
              
         
         % Extract patent text
@@ -191,6 +186,4 @@ for ix_year = year_start:year_end
     
     % Save to .mat file
     save_patent_keyword_appear2mat(patent_keyword_appear, ix_year)
-        
-    print_finish_summary(toc, ix_year)
 end

### 2015-07-23 find_patents_part.m

@@ -1,0 +1,257 @@
+function patix = find_patents_part(ix_year)
+
+% Customize some settings for different file types
+if ix_year < 2002
+    nr_lines4previouspatent = 1; 
+    nan_sect_str = 'NAM';
+    
+elseif (ix_year >=2002) & (ix_year < 2005)
+    nr_lines4previouspatent = 2; 
+    nan_sect_str = '<NAM>';
+    
+elseif ix_year >=2005
+    error('Not written yet for years 2005+.')
+end
+
+week_start = 1;
+
+% Determine if there are 52 or 53 weeks in year
+week_end = set_weekend(ix_year); 
+
+build_data_path = set_data_path(ix_year);
+addpath(build_data_path);
+
+
+% Get names of files
+% -------------------------------------------------------------------
+liststruct = dir(build_data_path);
+filenames = {liststruct.name};
+filenames = filenames(3:end)'; % truncate first elements . and ..
+
+filenames = ifmac_truncate_more(filenames);
+
+check_filenames_format(filenames, ix_year, week_start, week_end)
+
+% Iterate through files of weekly patent grant text data
+% -------------------------------------------------------------------
+fprintf('Build patent index for year %d:\n', ix_year)
+
+for ix_week = week_start:week_end
+    choose_file_open = filenames{ix_week};
+
+    % Load the patent text
+    unique_file_identifier = fopen(choose_file_open, 'r');   
+
+    if unique_file_identifier == -1
+        warning('Matlab cannot open the file')
+    end
+
+    open_file_aux = textscan(unique_file_identifier, '%s', ...
+        'delimiter', '\n');
+    file_str = open_file_aux{1,1};
+
+
+    % Define new search corpus as we might change some things about this
+    search_corpus = file_str; 
+
+
+    % Count number of patents in a given week
+    % ----------------------------------------------------------------
+    nr_trunc = 4;
+
+    if ix_year == 2001 % special case: problem with 80 numel text file
+        fprintf('*** Enter special case, year: %d, week: %d.\n', ...
+        [indic_find, nr_patents, ix_find] = ...
+            count_nr_patents_trunccorpus(search_corpus, 'PATN', ...
+            nr_trunc);           
+
+    % Something is wrong in year 1978
+    elseif ix_year == 1978 && (ix_week == 25 | ix_week == 26)  
+        fprintf('*** Enter special case, year: %d, week: %d.\n', ...
+        [indic_find, nr_patents, ix_find] = ...
[…]

### 2015-07-23 find_patents_part1.m

@@ -1,6 +1,5 @@
 close all
 clear all
-clc
 
 
 %% Set some inputs
@@ -47,12 +46,8 @@ for ix_year = year_start:year_end
 
         open_file_aux = textscan(unique_file_identifier, '%s', ...
             'delimiter', '\n');
-        file_str = open_file_aux{1,1};
-
-
-        % Define new search corpus as we might change some things about this
-        search_corpus = file_str; 
-        
+        search_corpus = open_file_aux{1,1};
+       
 
         % Count number of patents in a given week
         % ----------------------------------------------------------------
@@ -255,8 +250,7 @@ for ix_year = year_start:year_end
         fprintf('Week finished: %d/%d.\n', ix_week, week_end)
     end
     
-    % Save to .mat file
-    save_patix2mat(pat_ix, ix_year)
+
     
     print_finish_summary(toc, ix_year)
 end

### 2015-07-23 make_figures/plot_matches_over_nrpatents_weekly.m

@@ -27,8 +27,8 @@ my_xaxis_labels = {1976; ''; ''; ''; 1980; ''; ''; ''; ''; 1985; ''; ...
     ''; ''; ''; 1990; ''; ''; ''; ''; 1995; ''; ''; ''; ''; 2000; ''; ...
     ''; ''; ''; 2005; ''; ''; ''; ''; 2010; ''; ''; ''; ''; 2015};
 
-color2_pick = [0.000,0.639,0.561];
-% % color2_pick = [0.3, 0.3, 0.3]; % dark gray
+% color2_pick = [0.000,0.639,0.561];
+color2_pick = [0.3, 0.3, 0.3]; % dark gray
 my_gray = [0.806, 0.806, 0.806];
 my_dark_gray = [0.3, 0.3, 0.3];
 

### 2015-07-23 make_figures/plot_matches_overtime.m

@@ -32,8 +32,8 @@ find_dictionary = {'automat', 'robot', ...
 
 nr_worddict = size(allyr_patstats.total_matches_week, 2);
 
-color1_pick = [0.7900, 0.3800, 0.500]; % red
-% color1_pick = [0.3, 0.3, 0.3]; % dark gray
+% color1_pick = [0.7900, 0.3800, 0.500]; % red
+color1_pick = [0.3, 0.3, 0.3]; % dark gray
 my_gray = [0.806, 0.806, 0.806]; % light gray
 
 

### 2015-07-23 make_figures/summarize_matches.m

@@ -9,7 +9,7 @@ tic
 %% Define parameters
 % ========================================================================
 year_start = 1976;
-year_end = 2001;
+year_end = 2004;
 nr_years = length(year_start:year_end);
 week_start = 1;
 

### 2015-07-28 analyze_word_distribution.m
include more words in dictionary

@@ -208,6 +208,3 @@ save_name = horzcat('word_match_distr_', num2str(year_start), '-', ...
 save(save_name, 'word_match_distr', 'rest_matches', 'matches_notassigned');    
 fprintf('Saved: %s.\n', save_name)
 
-
-
-

### 2015-07-28 functions/define_dictionary.m

@@ -1,7 +1,7 @@
 function find_dictionary = define_dictionary()
 
 find_dictionary = {'automat', 'robot', ...
-    'movable arm', 'algorithm', 'software', ...
-    'autonomous', 'adaptive', 'self-adjust', 'self-creating', ...
+    'movable arm', 'algorithm', 'manual', 'software', 'computer', 'program', ...
+    'digital', 'autonomous', 'adaptive', 'self-adjust', 'self-creating', ...
     'self-generat', 'detect', 'independent', 'motor', 'engine', ...
     'communicat', 'semi-conductor', 'semiconductor'};

### 2015-07-28 transfer_cleaned_matches2csv.m

@@ -8,20 +8,15 @@ for ix_year = year_start:year_end
     load_file_name = horzcat('patsearch_results_', num2str(ix_year));
     load(load_file_name)
 
-
     % Extract columns and prepare them
     % ---------------------------------------------------------------------
 
     % Patent numbers
-    patent_nr = patsearch_results(:, 1);
+    patent_nr = patsearch_results.patentnr;
     patent_nr = str2double(patent_nr);
 
-    % Keyword matches
-    nr_keyword_matches = patsearch_results(:, 2);
-    nr_keyword_matches = cell2mat(nr_keyword_matches);
-
     % Prepare tech class numbers
-    tech_class_nr = patsearch_results(:, 3);
+    tech_class_nr = patsearch_results.classnr;
     tech_class_nr = strtrim(tech_class_nr); % remove leading and trailing whitespace
     tech_class_nr = strtok(tech_class_nr); % keep string until first whitespace
 
@@ -36,16 +31,16 @@ for ix_year = year_start:year_end
     tech_class_nr = str2double(tech_class_nr);
 
     % Week patent was granted in
-    patent_week = cell2mat(patsearch_results(:, 4));
+    patent_week = cell2mat(patsearch_results.week);
 
     % Make new column of year patent was granted in
     % ---------------------------------------------------------------------
-    patent_year = repmat(ix_year, size(patsearch_results(:, 1),1), 1);
+    patent_year = repmat(ix_year, length(patent_nr), 1);
 
     % Save individual year data
     % ---------------------------------------------------------------------
-    patsearch_year = [patent_nr, nr_keyword_matches, tech_class_nr, ...
-        patent_week, patent_year];
+    patsearch_year = [patent_nr, patent_year, patent_week, ...
+        tech_class_nr, patsearch_results.matches];
     
     % Save all years underneath
     % ---------------------------------------------------------------------
@@ -62,7 +57,7 @@ save_name = 'patsearch_allyears';
 
 % Save to .mat file
 tic
-save(horzcat('patsearch_allyears', '.mat'), 'patsearch_allyears');
+save(horzcat('output/patsearch_allyears', '.mat'), 'patsearch_allyears');
 time_file_write = toc;
 fprintf('Save file (%3.2fs): %s.mat.\n', time_file_write, save_name)
 
@@ -72,7 +67,7 @@ patsearch_allyears = num2cell(patsearch_allyears);
 
[…]

### 2015-08-05 output/table_compare_classalg.tex
Make tables evaluating classification performance

\begin{table}
\begin{small}
\begin{threeparttable}
\caption{{\normalsize Evaluation of different classification algorithms}}
\label{table:table_compare_classalg}
\begin{tabular}{rllllllllll}
\toprule 
 & \textbf{automat} & \textbf{robot} & \textbf{movable arm} & \textbf{algorithm} & \textbf{manual} & \textbf{software} & \textbf{computer} & \textbf{program} & \textbf{digital} & \textbf{autonomous}  \tabularnewline 
\midrule 
Accuracy & 0.79 & 0.76 & 0.76 & 0.78 & 0.71 & 0.77 & 0.76 & 0.72 & 0.76 & 0.77  \tabularnewline 
Precision & 0.56 & 0.75 & 0.33 & 0.63 & 0.37 & 0.53 & 0.49 & 0.40 & 0.49 & 1.00  \tabularnewline 
Recall & 0.56 & 0.03 & 0.01 & 0.19 & 0.27 & 0.22 & 0.36 & 0.30 & 0.35 & 0.03  \tabularnewline 
F-measure & 0.56 & 0.06 & 0.02 & 0.29 & 0.31 & 0.31 & 0.42 & 0.34 & 0.41 & 0.06  \tabularnewline 
AUC & 0.71 & 0.51 & 0.50 & 0.58 & 0.56 & 0.58 & 0.62 & 0.58 & 0.62 & 0.51  \tabularnewline 
Matthew's C.C. & 0.42 & 0.11 & 0.02 & 0.25 & 0.14 & 0.23 & 0.27 & 0.17 & 0.27 & 0.15  \tabularnewline 
\tabularnewline 
 & \textbf{adaptive} & \textbf{self-adjust} & \textbf{self-generat} & \textbf{detect} & \textbf{independent} & \textbf{motor} & \textbf{engine} & \textbf{communicat} & \textbf{semi-conductor} & \textbf{semiconductor}  \tabularnewline 
\midrule 
Accuracy & 0.76 & 0.75 & 0.76 & 0.71 & 0.66 & 0.73 & 0.68 & 0.73 & 0.75 & 0.70  \tabularnewline 
Precision & 0.50 & 0.00 & 1.00 & 0.42 & 0.29 & 0.42 & 0.24 & 0.43 & 0.17 & 0.27  \tabularnewline 
Recall & 0.05 & 0.00 & 0.01 & 0.50 & 0.30 & 0.34 & 0.15 & 0.45 & 0.01 & 0.14  \tabularnewline 
F-measure & 0.09 & NaN & 0.02 & 0.46 & 0.29 & 0.38 & 0.19 & 0.44 & 0.02 & 0.19  \tabularnewline 
AUC & 0.52 & 0.50 & 0.50 & 0.64 & 0.54 & 0.60 & 0.50 & 0.63 & 0.50 & 0.51  \tabularnewline 
Matthew's C.C. & 0.09 & -0.05 & 0.09 & 0.27 & 0.07 & 0.21 & 0.00 & 0.26 & -0.02 & 0.03  \tabularnewline 
\tabularnewline 
 & \textbf{chip} & \textbf{bus} & \textbf{circuit} & \textbf{circuitry} & \textbf{antigen} & \textbf{antigenic} & \textbf{chromatography} & \textbf{Bessen-Hunt} & \textbf{Always 'No'} & \textbf{Always 'Yes'}  \tabularnewline 
\midrule 
Accuracy & 0.69 & 0.68 & 0.66 & 0.74 & 0.75 & 0.76 & 0.71 & 0.78 & 0.76 & 0.24  \tabularnewline 
Precision & 0.20 & 0.33 & 0.36 & 0.41 & 0.00 & 0.00 & 0.10 & 0.57 & NaN & 0.24  \tabularnewline 
Recall & 0.10 & 0.30 & 0.53 & 0.19 & 0.00 & 0.00 & 0.03 & 0.29 & 0.00 & 1.00  \tabularnewline 
F-measure & 0.13 & 0.31 & 0.43 & 0.26 & NaN & NaN & 0.04 & 0.38 & NaN & 0.39  \tabularnewline 
AUC & 0.49 & 0.55 & 0.62 & 0.55 & 0.49 & 0.50 & 0.47 & 0.61 & 0.50 & 0.50  \tabularnewline 
Matthew's C.C. & -0.04 & 0.11 & 0.21 & 0.14 & -0.07 & -0.04 & -0.09 & 0.28 & NaN & NaN  \tabularnewline 
\bottomrule 
\end{tabular} 
\begin{tablenotes}
\small
\item\textit{Note:} Every column is a different classification algorithms.
\item F-measure: balanced F-measure which is the evenly weightened harmonic mean between Precision and Recall. 
\item AUC: Area under (the receiver operating) curve.
\item Matthew's C.C.: Matthew's correlation coefficient.
\item\textit{Source:} USPTO, Google and own calculations.
\end{tablenotes}
\end{threeparttable}
\end{small}
\end{table}

### 2015-08-05 manual_classification/make_contingency_table.m

@@ -1,0 +1,35 @@
+function make_contingency_table(classifstat)
+
+% Print to .txt file in Latex format
+printname = 'output/table_contingency.tex';
+
+FID = fopen(printname, 'w');
+
+fprintf(FID,'\\begin{table}\n');
+fprintf(FID,'\\begin{small}\n');
+fprintf(FID,'\\begin{threeparttable}\n');
+fprintf(FID,'\\caption{{\\normalsize Contingency table}}\n');
+fprintf(FID,'\\label{table:contingency_table}\n');
+fprintf(FID,'\\begin{tabular}{lrlll}\n');
+fprintf(FID, '\\toprule');
+fprintf(FID, ' & & & &  \\tabularnewline[-0.3cm]\n');
+fprintf(FID, ' & & \\multicolumn{3}{c}{Computerized} \\tabularnewline[0.1cm]\n');
+fprintf(FID, ' & & \\multicolumn{1}{|l}{No}  & \\multicolumn{1}{l|}{Yes} \\tabularnewline\n');
+fprintf(FID, '\\cline{3-5} \n');
+fprintf(FID, '\\parbox[t]{0mm}{\\multirow{2}{*}{\\rotatebox[origin=c]{90}{Manual}}} & No & \\multicolumn{1}{|l}{%d} & \\multicolumn{1}{l|}{%d} & %d \\tabularnewline\n', classifstat.true_negative, classifstat.false_positive, classifstat.true_negative + classifstat.false_positive);
+fprintf(FID, ' & Yes & \\multicolumn{1}{|l}{%d} & \\multicolumn{1}{l|}{%d} & %d \\tabularnewline\n', classifstat.false_negative, classifstat.true_positive, classifstat.false_negative + classifstat.true_positive);
+fprintf(FID, ' \\cline{3-5} \n');
+fprintf(FID, ' &  & \\multicolumn{1}{|l}{%d} & \\multicolumn{1}{l|}{%d} & %d \\tabularnewline\n', classifstat.true_negative + classifstat.false_negative, classifstat.false_positive + classifstat.true_positive, classifstat.nr_codpt);
+
+fprintf(FID, '\\bottomrule');
+fprintf(FID,'\\end{tabular}\n');
+% fprintf(FID,'\\begin{tablenotes}\n');
+% fprintf(FID,'\\small\n');
+%fprintf(FID,'\\item\\textit{Note:} \n');
[…]

### 2015-08-05 manual_classification/make_table_compare_classalg.m

@@ -1,0 +1,66 @@
+function make_table_compare_classalg(classalg_comparison)
+
+
+nr_algs = length(classalg_comparison.accuracy);
+
+nr_splits = 3;
+
+splitline = nr_algs / nr_splits;
+
+str_tabularsize = ['\\begin{tabular}{r', repmat('l', 1, splitline), '}\n'];
+num_multiinsert = [repmat('& %3.2f ', 1, splitline), ' \\tabularnewline \n'];
+
+% Print to .txt file in Latex format
+printname = 'output/table_compare_classalg.tex';
+
+FID = fopen(printname, 'w');
+
+fprintf(FID, '\\begin{table}\n');
+fprintf(FID, '\\begin{small}\n');
+fprintf(FID, '\\begin{threeparttable}\n');
+fprintf(FID, '\\caption{{\\normalsize Evaluation of different classification algorithms}}\n');
+fprintf(FID, '\\label{table:table_compare_classalg}\n');
+fprintf(FID, str_tabularsize);
+fprintf(FID, '\\toprule \n');
+
+for j=1:nr_splits
+    split_start = 1 + (j-1)*splitline;
+    split_end = j*splitline;
+    
+    fprintf(FID, ' ');
+    for i= split_start : split_end
+        fprintf(FID, '& \\textbf{%s} ', classalg_comparison.algorithm_name{i});
+    end
+    fprintf(FID, ' \\tabularnewline \n');
+
+    fprintf(FID, '\\midrule \n');
+    fprintf(FID, ['Accuracy ', num_multiinsert], classalg_comparison.accuracy(split_start:split_end));
+    fprintf(FID, ['Precision ', num_multiinsert], classalg_comparison.precision(split_start:split_end));
+    fprintf(FID, ['Recall ', num_multiinsert], classalg_comparison.recall(split_start:split_end));
+    fprintf(FID, ['F-measure ', num_multiinsert], classalg_comparison.fmeasure(split_start:split_end));
+    fprintf(FID, ['AUC ', num_multiinsert], classalg_comparison.auc(split_start:split_end));
+    fprintf(FID, ['Matthew''s C.C. ', num_multiinsert], classalg_comparison.matthewscorrcoeff(split_start:split_end));
+
+    if j == nr_splits
+        fprintf(FID, '\\bottomrule \n');
+    else
+        fprintf(FID, '\\tabularnewline \n');
+    end
+end
+
+
[…]

### 2015-08-06 output/table_compare_classalg.tex
Include number Yes classified patents in table comparing algorithms

@@
  & \textbf{automat} & \textbf{robot} & \textbf{movable arm} & \textbf{algorithm} & \textbf{manual} & \textbf{software} & \textbf{computer} & \textbf{program} & \textbf{digital} & \textbf{autonomous}  \tabularnewline
-\midrule 
 Accuracy & 0.79 & 0.76 & 0.76 & 0.78 & 0.71 & 0.77 & 0.76 & 0.72 & 0.76 & 0.77  \tabularnewline 
@@
 AUC & 0.71 & 0.51 & 0.50 & 0.58 & 0.56 & 0.58 & 0.62 & 0.58 & 0.62 & 0.51  \tabularnewline 
-Matthew's C.C. & 0.42 & 0.11 & 0.02 & 0.25 & 0.14 & 0.23 & 0.27 & 0.17 & 0.27 & 0.15  \tabularnewline 
+MCC & 0.42 & 0.11 & 0.02 & 0.25 & 0.14 & 0.23 & 0.27 & 0.17 & 0.27 & 0.15  \tabularnewline 
+Number "Yes" & 106 & 4 & 3 & 32 & 76 & 43 & 78 & 78 & 76 & 3  \tabularnewline 
 \tabularnewline 
  & \textbf{adaptive} & \textbf{self-adjust} & \textbf{self-generat} & \textbf{detect} & \textbf{independent} & \textbf{motor} & \textbf{engine} & \textbf{communicat} & \textbf{semi-conductor} & \textbf{semiconductor}  \tabularnewline
-\midrule 
 Accuracy & 0.76 & 0.75 & 0.76 & 0.71 & 0.66 & 0.73 & 0.68 & 0.73 & 0.75 & 0.70  \tabularnewline 
@@
 AUC & 0.52 & 0.50 & 0.50 & 0.64 & 0.54 & 0.60 & 0.50 & 0.63 & 0.50 & 0.51  \tabularnewline 
-Matthew's C.C. & 0.09 & -0.05 & 0.09 & 0.27 & 0.07 & 0.21 & 0.00 & 0.26 & -0.02 & 0.03  \tabularnewline 
+MCC & 0.09 & -0.05 & 0.09 & 0.27 & 0.07 & 0.21 & 0.00 & 0.26 & -0.02 & 0.03  \tabularnewline 
+Number "Yes" & 10 & 3 & 1 & 127 & 106 & 86 & 66 & 109 & 6 & 55  \tabularnewline 
 \tabularnewline 
  & \textbf{chip} & \textbf{bus} & \textbf{circuit} & \textbf{circuitry} & \textbf{antigen} & \textbf{antigenic} & \textbf{chromatography} & \textbf{Bessen-Hunt} & \textbf{Always 'No'} & \textbf{Always 'Yes'}  \tabularnewline
-\midrule 
 Accuracy & 0.69 & 0.68 & 0.66 & 0.74 & 0.75 & 0.76 & 0.71 & 0.78 & 0.76 & 0.24  \tabularnewline 
@@
 AUC & 0.49 & 0.55 & 0.62 & 0.55 & 0.49 & 0.50 & 0.47 & 0.61 & 0.50 & 0.50  \tabularnewline 
-Matthew's C.C. & -0.04 & 0.11 & 0.21 & 0.14 & -0.07 & -0.04 & -0.09 & 0.28 & NaN & NaN  \tabularnewline 
+MCC & -0.04 & 0.11 & 0.21 & 0.14 & -0.07 & -0.04 & -0.09 & 0.28 & NaN & NaN  \tabularnewline 
+Number "Yes" & 51 & 95 & 155 & 49 & 6 & 2 & 30 & 53 & 0 & 438  \tabularnewline 
 \bottomrule 
@@
 \item AUC: Area under (the receiver operating) curve.
-\item Matthew's C.C.: Matthew's correlation coefficient.
+\item MCC: Matthew's correlation coefficient.
 \item\textit{Source:} USPTO, Google and own calculations.

### 2015-08-06 manual_classification/make_table_compare_classalg.m

@@ -9,6 +9,7 @@ splitline = nr_algs / nr_splits;
 
 str_tabularsize = ['\\begin{tabular}{r', repmat('l', 1, splitline), '}\n'];
 num_multiinsert = [repmat('& %3.2f ', 1, splitline), ' \\tabularnewline \n'];
+int_multiinsert = [repmat('& %d ', 1, splitline), ' \\tabularnewline \n'];
 
 % Print to .txt file in Latex format
 printname = 'output/table_compare_classalg.tex';
@@ -29,18 +30,26 @@ for j=1:nr_splits
     
     fprintf(FID, ' ');
     for i= split_start : split_end
-        fprintf(FID, '& \\textbf{%s} ', classalg_comparison.algorithm_name{i});
+        fprintf(FID, '& \\textbf{%s} ', ...
+            classalg_comparison.algorithm_name{i});
     end
     fprintf(FID, ' \\tabularnewline \n');
 
-    fprintf(FID, '\\midrule \n');
-    fprintf(FID, ['Accuracy ', num_multiinsert], classalg_comparison.accuracy(split_start:split_end));
-    fprintf(FID, ['Precision ', num_multiinsert], classalg_comparison.precision(split_start:split_end));
-    fprintf(FID, ['Recall ', num_multiinsert], classalg_comparison.recall(split_start:split_end));
-    fprintf(FID, ['F-measure ', num_multiinsert], classalg_comparison.fmeasure(split_start:split_end));
-    fprintf(FID, ['AUC ', num_multiinsert], classalg_comparison.auc(split_start:split_end));
-    fprintf(FID, ['Matthew''s C.C. ', num_multiinsert], classalg_comparison.matthewscorrcoeff(split_start:split_end));
-
+    fprintf(FID, ['Accuracy ', num_multiinsert], ...
+        classalg_comparison.accuracy(split_start:split_end));
+    fprintf(FID, ['Precision ', num_multiinsert], ...
+        classalg_comparison.precision(split_start:split_end));
+    fprintf(FID, ['Recall ', num_multiinsert], ...
+        classalg_comparison.recall(split_start:split_end));
+    fprintf(FID, ['F-measure ', num_multiinsert], ...
+        classalg_comparison.fmeasure(split_start:split_end));
+    fprintf(FID, ['AUC ', num_multiinsert], ...
+        classalg_comparison.auc(split_start:split_end));
[…]

### 2015-08-06 run_patentsearch.m

@@ -112,7 +112,7 @@ years = year_start:year_end;
 %     year_end);
 
 % Classify patents based on computerized methods
-% computerClass = classify_autom_algorith(automclassData);
+computerClass = classify_autom_algorith(automclassData);
 
 % Make a contingency table comparing the manual vs. the computer
 % classification of patents
@@ -127,6 +127,8 @@ for i=1:size(computerClass.compAutomat, 2)
     classalg_comparison.fmeasure(i) = classifstat.fmeasure;
     classalg_comparison.auc(i) = classifstat.auc;
     classalg_comparison.matthewscorrcoeff(i) = classifstat.matthewscorrcoeff;
+    classalg_comparison.nr_Yes(i) = classifstat.false_positive + ...
+        classifstat.true_positive;
 end
 
 classalg_comparison.algorithm_name = computerClass.algorithm_name;
@@ -143,6 +145,9 @@ make_contingency_table(classifstat)
 make_table_compare_classalg(classalg_comparison)
 
 
+%% Copy tables
+copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\table_compare_classalg.tex', ...
+    'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\tables')
 
 
 

### 2015-08-06 output/table_compare_classalg.tex
Make table work with different number of algorithms

--- 2015-08-05 output/table_compare_classalg.tex
@@
 \toprule 
- & \textbf{automat} & \textbf{robot} & \textbf{movable arm} & \textbf{algorithm} & \textbf{manual} & \textbf{software} & \textbf{computer} & \textbf{program} & \textbf{digital} & \textbf{autonomous}  \tabularnewline
-\midrule 
+ & \textbf{automat$_b$} & \textbf{robot$_b$} & \textbf{movable arm$_b$} & \textbf{algorithm$_b$} & \textbf{manual$_b$} & \textbf{software$_b$} & \textbf{computer$_b$} & \textbf{program$_b$} & \textbf{digital$_b$} & \textbf{autonomous$_b$}  \tabularnewline
 Accuracy & 0.79 & 0.76 & 0.76 & 0.78 & 0.71 & 0.77 & 0.76 & 0.72 & 0.76 & 0.77  \tabularnewline 
-Precision & 0.56 & 0.75 & 0.33 & 0.63 & 0.37 & 0.53 & 0.49 & 0.40 & 0.49 & 1.00  \tabularnewline 
-Recall & 0.56 & 0.03 & 0.01 & 0.19 & 0.27 & 0.22 & 0.36 & 0.30 & 0.35 & 0.03  \tabularnewline 
-F-measure & 0.56 & 0.06 & 0.02 & 0.29 & 0.31 & 0.31 & 0.42 & 0.34 & 0.41 & 0.06  \tabularnewline 
+Precision & 0.56 & 0.75 & 0.33 & 0.63 & 0.36 & 0.53 & 0.49 & 0.40 & 0.49 & 1.00  \tabularnewline 
+Recall & 0.56 & 0.03 & 0.01 & 0.19 & 0.26 & 0.22 & 0.36 & 0.30 & 0.35 & 0.03  \tabularnewline 
+F-measure & 0.56 & 0.06 & 0.02 & 0.29 & 0.30 & 0.31 & 0.42 & 0.34 & 0.41 & 0.06  \tabularnewline 
 AUC & 0.71 & 0.51 & 0.50 & 0.58 & 0.56 & 0.58 & 0.62 & 0.58 & 0.62 & 0.51  \tabularnewline 
-Matthew's C.C. & 0.42 & 0.11 & 0.02 & 0.25 & 0.14 & 0.23 & 0.27 & 0.17 & 0.27 & 0.15  \tabularnewline 
+MCC & 0.42 & 0.11 & 0.02 & 0.25 & 0.13 & 0.23 & 0.27 & 0.17 & 0.27 & 0.15  \tabularnewline 
+Number "Yes" & 106 & 4 & 3 & 32 & 75 & 43 & 78 & 78 & 76 & 3  \tabularnewline 
 \tabularnewline 
- & \textbf{adaptive} & \textbf{self-adjust} & \textbf{self-generat} & \textbf{detect} & \textbf{independent} & \textbf{motor} & \textbf{engine} & \textbf{communicat} & \textbf{semi-conductor} & \textbf{semiconductor}  \tabularnewline
-\midrule 
+ & \textbf{adaptive$_b$} & \textbf{self-adjust$_b$} & \textbf{self-generat$_b$} & \textbf{detect$_b$} & \textbf{independent$_b$} & \textbf{motor$_b$} & \textbf{engine$_b$} & \textbf{communicat$_b$} & \textbf{semi-conductor$_b$} & \textbf{semiconductor$_b$}  \tabularnewline
 Accuracy & 0.76 & 0.75 & 0.76 & 0.71 & 0.66 & 0.73 & 0.68 & 0.73 & 0.75 & 0.70  \tabularnewline 
-Precision & 0.50 & 0.00 & 1.00 & 0.42 & 0.29 & 0.42 & 0.24 & 0.43 & 0.17 & 0.27  \tabularnewline 
-Recall & 0.05 & 0.00 & 0.01 & 0.50 & 0.30 & 0.34 & 0.15 & 0.45 & 0.01 & 0.14  \tabularnewline 
+Precision & 0.50 & 0.00 & 1.00 & 0.42 & 0.29 & 0.42 & 0.25 & 0.43 & 0.17 & 0.27  \tabularnewline 
+Recall & 0.05 & 0.00 & 0.01 & 0.50 & 0.29 & 0.34 & 0.15 & 0.45 & 0.01 & 0.14  \tabularnewline 
 F-measure & 0.09 & NaN & 0.02 & 0.46 & 0.29 & 0.38 & 0.19 & 0.44 & 0.02 & 0.19  \tabularnewline 
-AUC & 0.52 & 0.50 & 0.50 & 0.64 & 0.54 & 0.60 & 0.50 & 0.63 & 0.50 & 0.51  \tabularnewline 
-Matthew's C.C. & 0.09 & -0.05 & 0.09 & 0.27 & 0.07 & 0.21 & 0.00 & 0.26 & -0.02 & 0.03  \tabularnewline 
+AUC & 0.52 & 0.50 & 0.50 & 0.64 & 0.53 & 0.60 & 0.50 & 0.63 & 0.50 & 0.51  \tabularnewline 
+MCC & 0.09 & -0.05 & 0.09 & 0.27 & 0.06 & 0.21 & 0.01 & 0.26 & -0.02 & 0.03  \tabularnewline 
+Number "Yes" & 10 & 3 & 1 & 127 & 105 & 86 & 65 & 109 & 6 & 55  \tabularnewline 
 \tabularnewline 
- & \textbf{chip} & \textbf{bus} & \textbf{circuit} & \textbf{circuitry} & \textbf{antigen} & \textbf{antigenic} & \textbf{chromatography} & \textbf{Bessen-Hunt} & \textbf{Always 'No'} & \textbf{Always 'Yes'}  \tabularnewline
-\midrule 
-Accuracy & 0.69 & 0.68 & 0.66 & 0.74 & 0.75 & 0.76 & 0.71 & 0.78 & 0.76 & 0.24  \tabularnewline 
-Precision & 0.20 & 0.33 & 0.36 & 0.41 & 0.00 & 0.00 & 0.10 & 0.57 & NaN & 0.24  \tabularnewline 
-Recall & 0.10 & 0.30 & 0.53 & 0.19 & 0.00 & 0.00 & 0.03 & 0.29 & 0.00 & 1.00  \tabularnewline 
-F-measure & 0.13 & 0.31 & 0.43 & 0.26 & NaN & NaN & 0.04 & 0.38 & NaN & 0.39  \tabularnewline 
+ & \textbf{chip$_b$} & \textbf{bus$_b$} & \textbf{circuit$_b$} & \textbf{circuitry$_b$} & \textbf{antigen$_b$} & \textbf{antigenic$_b$} & \textbf{chromatography$_b$} & \textbf{Bessen-Hunt} & \textbf{Always "No"} & \textbf{Always "Yes"}  \tabularnewline
+Accuracy & 0.69 & 0.68 & 0.66 & 0.74 & 0.75 & 0.76 & 0.70 & 0.78 & 0.76 & 0.24  \tabularnewline 
+Precision & 0.20 & 0.33 & 0.36 & 0.42 & 0.00 & 0.00 & 0.07 & 0.57 & NaN & 0.24  \tabularnewline 
+Recall & 0.10 & 0.30 & 0.53 & 0.19 & 0.00 & 0.00 & 0.02 & 0.29 & 0.00 & 1.00  \tabularnewline 
+F-measure & 0.13 & 0.31 & 0.43 & 0.26 & NaN & NaN & 0.03 & 0.38 & NaN & 0.39  \tabularnewline 
 AUC & 0.49 & 0.55 & 0.62 & 0.55 & 0.49 & 0.50 & 0.47 & 0.61 & 0.50 & 0.50  \tabularnewline 
-Matthew's C.C. & -0.04 & 0.11 & 0.21 & 0.14 & -0.07 & -0.04 & -0.09 & 0.28 & NaN & NaN  \tabularnewline 
+MCC & -0.04 & 0.11 & 0.21 & 0.15 & -0.07 & -0.04 & -0.11 & 0.28 & NaN & NaN  \tabularnewline 
+Number "Yes" & 51 & 95 & 155 & 48 & 6 & 2 & 29 & 53 & 0 & 438  \tabularnewline 
 \bottomrule 

### 2015-08-06 manual_classification/classify_autom_algorith.m

@@ -3,26 +3,60 @@ function computerClass = classify_autom_algorith(automclassData)
     total_matches = automclassData.title_matches + ...
         automclassData.abstract_matches + automclassData.body_matches;
    
+    compAutomat = [];
+    algorithm_name = {'deleteMe'};
+    
     % Classify as automation patents if they have at least one keyword
     % match
-    for ix_keyword=1:length( automclassData.dictionary )
-        compAutomat(:, ix_keyword) = count_matches_greaterNumber( ...
-            total_matches, ix_keyword, 1);
-    end
+%     for ix_keyword=1:length( automclassData.dictionary )
+%         compAutomat = [compAutomat, count_matches_greaterNumber( ...
+%             automclassData.title_matches, ix_keyword, 1)];
+%         name_pick = [automclassData.dictionary{ix_keyword}, '$_c$'];
+%         algorithm_name = [algorithm_name, name_pick];
+%     end
 
+    % Take matches in title
+%     for ix_keyword=1:length( automclassData.dictionary )
+%         compAutomat = [compAutomat, count_matches_greaterNumber( ...
+%             automclassData.title_matches, ix_keyword, 1)];
+%         name_pick = [automclassData.dictionary{ix_keyword}, '$_t$'];
+%         algorithm_name = [algorithm_name, name_pick];
+%     end
+    
+    % Take matches in abstract
+%     for ix_keyword=1:length( automclassData.dictionary )
+%         compAutomat = [compAutomat, count_matches_greaterNumber( ...
+%             automclassData.abstract_matches, ix_keyword, 1)];
+%         name_pick = [automclassData.dictionary{ix_keyword}, '$_a$'];
+%         algorithm_name = [algorithm_name, name_pick];
+%     end
+
+    % Take matches in patent body
+    for ix_keyword=1:length( automclassData.dictionary )
+        compAutomat = [compAutomat, count_matches_greaterNumber( ...
+            automclassData.body_matches, ix_keyword, 1)];
+        name_pick = [automclassData.dictionary{ix_keyword}, '$_b$'];
+        algorithm_name = [algorithm_name, name_pick];
+    end
+    
     % Bessen-Hunt classification of software patents
     bh_software_patents = bessen_hunt(automclassData, 1);
     compAutomat = [compAutomat, bh_software_patents];
+    algorithm_name = [algorithm_name, 'Bessen-Hunt'];
+
     
[…]

### 2015-08-06 run_patentsearch.m

@@ -112,6 +112,7 @@ years = year_start:year_end;
 %     year_end);
 
 % Classify patents based on computerized methods
+clear computerClass classalg_comparison
 computerClass = classify_autom_algorith(automclassData);
 
 % Make a contingency table comparing the manual vs. the computer
@@ -141,8 +142,8 @@ classifstat = calculate_manclass_stats(manclassData.manAutomat, ...
 
 make_contingency_table(classifstat)
 
-
-make_table_compare_classalg(classalg_comparison)
+max_line = 10;
+make_table_compare_classalg(classalg_comparison, max_line)
 
 
 %% Copy tables

### 2015-08-06 output/table_compare_classalg.tex
Add manual to dictionary

--- 2015-08-05 output/table_compare_classalg.tex
@@
 \toprule 
- & \textbf{automat} & \textbf{robot} & \textbf{movable arm} & \textbf{algorithm} & \textbf{manual} & \textbf{software} & \textbf{computer} & \textbf{program} & \textbf{digital} & \textbf{autonomous}  \tabularnewline
-\midrule 
-Accuracy & 0.79 & 0.76 & 0.76 & 0.78 & 0.71 & 0.77 & 0.76 & 0.72 & 0.76 & 0.77  \tabularnewline 
-Precision & 0.56 & 0.75 & 0.33 & 0.63 & 0.37 & 0.53 & 0.49 & 0.40 & 0.49 & 1.00  \tabularnewline 
-Recall & 0.56 & 0.03 & 0.01 & 0.19 & 0.27 & 0.22 & 0.36 & 0.30 & 0.35 & 0.03  \tabularnewline 
-F-measure & 0.56 & 0.06 & 0.02 & 0.29 & 0.31 & 0.31 & 0.42 & 0.34 & 0.41 & 0.06  \tabularnewline 
-AUC & 0.71 & 0.51 & 0.50 & 0.58 & 0.56 & 0.58 & 0.62 & 0.58 & 0.62 & 0.51  \tabularnewline 
-Matthew's C.C. & 0.42 & 0.11 & 0.02 & 0.25 & 0.14 & 0.23 & 0.27 & 0.17 & 0.27 & 0.15  \tabularnewline 
+ & \textbf{automat$_{t+a}$} & \textbf{robot$_{t+a}$} & \textbf{movable arm$_{t+a}$} & \textbf{algorithm$_{t+a}$} & \textbf{manual$_{t+a}$} & \textbf{software$_{t+a}$} & \textbf{computer$_{t+a}$} & \textbf{program$_{t+a}$} & \textbf{digital$_{t+a}$} & \textbf{autonomous$_{t+a}$}  \tabularnewline
+Accuracy & 0.78 & 0.76 & 0.76 & 0.76 & 0.77 & 0.77 & 0.77 & 0.78 & 0.76 & 0.76  \tabularnewline 
+Precision & 0.83 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 0.62 & 0.79 & 0.47 & NaN  \tabularnewline 
+Recall & 0.10 & 0.02 & 0.01 & 0.02 & 0.03 & 0.03 & 0.08 & 0.10 & 0.08 & 0.00  \tabularnewline 
+F-measure & 0.17 & 0.04 & 0.02 & 0.04 & 0.06 & 0.06 & 0.14 & 0.18 & 0.13 & NaN  \tabularnewline 
+AUC & 0.54 & 0.51 & 0.50 & 0.51 & 0.51 & 0.51 & 0.53 & 0.55 & 0.52 & 0.50  \tabularnewline 
+MCC & 0.23 & 0.12 & 0.09 & 0.12 & 0.15 & 0.15 & 0.15 & 0.23 & 0.11 & NaN  \tabularnewline 
+Number "Yes" & 12 & 2 & 1 & 2 & 3 & 3 & 13 & 14 & 17 & 0  \tabularnewline 
 \tabularnewline 
- & \textbf{adaptive} & \textbf{self-adjust} & \textbf{self-generat} & \textbf{detect} & \textbf{independent} & \textbf{motor} & \textbf{engine} & \textbf{communicat} & \textbf{semi-conductor} & \textbf{semiconductor}  \tabularnewline
-\midrule 
-Accuracy & 0.76 & 0.75 & 0.76 & 0.71 & 0.66 & 0.73 & 0.68 & 0.73 & 0.75 & 0.70  \tabularnewline 
-Precision & 0.50 & 0.00 & 1.00 & 0.42 & 0.29 & 0.42 & 0.24 & 0.43 & 0.17 & 0.27  \tabularnewline 
-Recall & 0.05 & 0.00 & 0.01 & 0.50 & 0.30 & 0.34 & 0.15 & 0.45 & 0.01 & 0.14  \tabularnewline 
-F-measure & 0.09 & NaN & 0.02 & 0.46 & 0.29 & 0.38 & 0.19 & 0.44 & 0.02 & 0.19  \tabularnewline 
-AUC & 0.52 & 0.50 & 0.50 & 0.64 & 0.54 & 0.60 & 0.50 & 0.63 & 0.50 & 0.51  \tabularnewline 
-Matthew's C.C. & 0.09 & -0.05 & 0.09 & 0.27 & 0.07 & 0.21 & 0.00 & 0.26 & -0.02 & 0.03  \tabularnewline 
+ & \textbf{adaptive$_{t+a}$} & \textbf{self-adjust$_{t+a}$} & \textbf{self-generat$_{t+a}$} & \textbf{detect$_{t+a}$} & \textbf{independent$_{t+a}$} & \textbf{motor$_{t+a}$} & \textbf{engine$_{t+a}$} & \textbf{communicat$_{t+a}$} & \textbf{semi-conductor$_{t+a}$} & \textbf{semiconductor$_{t+a}$}  \tabularnewline
+Accuracy & 0.76 & 0.76 & 0.76 & 0.77 & 0.75 & 0.76 & 0.75 & 0.75 & 0.76 & 0.73  \tabularnewline 
+Precision & 0.50 & 0.00 & 1.00 & 0.62 & 0.38 & 0.50 & 0.31 & 0.41 & 0.00 & 0.07  \tabularnewline 
+Recall & 0.01 & 0.00 & 0.01 & 0.12 & 0.05 & 0.09 & 0.05 & 0.09 & 0.00 & 0.01  \tabularnewline 
+F-measure & 0.02 & NaN & 0.02 & 0.21 & 0.08 & 0.15 & 0.08 & 0.14 & NaN & 0.02  \tabularnewline 
+AUC & 0.50 & 0.50 & 0.50 & 0.55 & 0.51 & 0.53 & 0.51 & 0.52 & 0.50 & 0.49  \tabularnewline 
+MCC & 0.04 & -0.03 & 0.09 & 0.20 & 0.06 & 0.13 & 0.03 & 0.09 & -0.04 & -0.07  \tabularnewline 
+Number "Yes" & 2 & 1 & 1 & 21 & 13 & 18 & 16 & 22 & 2 & 14  \tabularnewline 
 \tabularnewline 
- & \textbf{chip} & \textbf{bus} & \textbf{circuit} & \textbf{circuitry} & \textbf{antigen} & \textbf{antigenic} & \textbf{chromatography} & \textbf{Bessen-Hunt} & \textbf{Always 'No'} & \textbf{Always 'Yes'}  \tabularnewline
-\midrule 
-Accuracy & 0.69 & 0.68 & 0.66 & 0.74 & 0.75 & 0.76 & 0.71 & 0.78 & 0.76 & 0.24  \tabularnewline 
-Precision & 0.20 & 0.33 & 0.36 & 0.41 & 0.00 & 0.00 & 0.10 & 0.57 & NaN & 0.24  \tabularnewline 
-Recall & 0.10 & 0.30 & 0.53 & 0.19 & 0.00 & 0.00 & 0.03 & 0.29 & 0.00 & 1.00  \tabularnewline 
-F-measure & 0.13 & 0.31 & 0.43 & 0.26 & NaN & NaN & 0.04 & 0.38 & NaN & 0.39  \tabularnewline 
-AUC & 0.49 & 0.55 & 0.62 & 0.55 & 0.49 & 0.50 & 0.47 & 0.61 & 0.50 & 0.50  \tabularnewline 
-Matthew's C.C. & -0.04 & 0.11 & 0.21 & 0.14 & -0.07 & -0.04 & -0.09 & 0.28 & NaN & NaN  \tabularnewline 
+ & \textbf{chip$_{t+a}$} & \textbf{bus$_{t+a}$} & \textbf{circuit$_{t+a}$} & \textbf{circuitry$_{t+a}$} & \textbf{antigen$_{t+a}$} & \textbf{antigenic$_{t+a}$} & \textbf{chromatography$_{t+a}$} & \textbf{Bessen-Hunt} & \textbf{Always "No"} & \textbf{Always "Yes"}  \tabularnewline
+Accuracy & 0.76 & 0.75 & 0.71 & 0.75 & 0.76 & 0.76 & 0.76 & 0.78 & 0.76 & 0.24  \tabularnewline 
+Precision & 0.43 & 0.31 & 0.25 & 0.33 & NaN & NaN & 1.00 & 0.57 & NaN & 0.24  \tabularnewline 
+Recall & 0.03 & 0.05 & 0.10 & 0.03 & 0.00 & 0.00 & 0.01 & 0.29 & 0.00 & 1.00  \tabularnewline 
+F-measure & 0.05 & 0.08 & 0.14 & 0.05 & NaN & NaN & 0.02 & 0.38 & NaN & 0.39  \tabularnewline 
+AUC & 0.51 & 0.51 & 0.50 & 0.51 & 0.50 & 0.50 & 0.50 & 0.61 & 0.50 & 0.50  \tabularnewline 
+MCC & 0.06 & 0.03 & 0.01 & 0.03 & NaN & NaN & 0.09 & 0.28 & NaN & NaN  \tabularnewline 
+Number "Yes" & 7 & 16 & 40 & 9 & 0 & 0 & 1 & 53 & 0 & 438  \tabularnewline 
 \bottomrule 

### 2015-08-06 manual_classification/classify_autom_algorith.m

@@ -11,7 +11,7 @@ function computerClass = classify_autom_algorith(automclassData)
 %     for ix_keyword=1:length( automclassData.dictionary )
 %         compAutomat = [compAutomat, count_matches_greaterNumber( ...
 %             automclassData.title_matches, ix_keyword, 1)];
-%         name_pick = [automclassData.dictionary{ix_keyword}, '$_c$'];
+%         name_pick = [automclassData.dictionary{ix_keyword}, '$_{t+a+b}$'];
 %         algorithm_name = [algorithm_name, name_pick];
 %     end
 
@@ -32,12 +32,22 @@ function computerClass = classify_autom_algorith(automclassData)
 %     end
 
     % Take matches in patent body
+%     for ix_keyword=1:length( automclassData.dictionary )
+%         compAutomat = [compAutomat, count_matches_greaterNumber( ...
+%             automclassData.body_matches, ix_keyword, 1)];
+%         name_pick = [automclassData.dictionary{ix_keyword}, '$_b$'];
+%         algorithm_name = [algorithm_name, name_pick];
+%     end
+    
+    % Take matches in title and abstract
     for ix_keyword=1:length( automclassData.dictionary )
         compAutomat = [compAutomat, count_matches_greaterNumber( ...
-            automclassData.body_matches, ix_keyword, 1)];
-        name_pick = [automclassData.dictionary{ix_keyword}, '$_b$'];
+            automclassData.title_matches + automclassData.abstract_matches, ...
+            ix_keyword, 1)];
+        name_pick = [automclassData.dictionary{ix_keyword}, '$_{t+a}$'];
         algorithm_name = [algorithm_name, name_pick];
     end
+    
     
     % Bessen-Hunt classification of software patents
     bh_software_patents = bessen_hunt(automclassData, 1);

### 2015-08-06 specs/define_dictionary.m

@@ -5,4 +5,5 @@ find_dictionary = {'automat', 'robot', ...
     'digital', 'autonomous', 'adaptive', 'self-adjust', ...
     'self-generat', 'detect', 'independent', 'motor', 'engine', ...
     'communicat', 'semi-conductor', 'semiconductor', ...
-    'chip', 'bus', 'circuit', 'circuitry', 'antigen', 'antigenic', 'chromatography'};
+    'chip', 'bus', 'circuit', 'circuitry', 'antigen', 'antigenic', ...
+    'chromatography', 'manual'};

### 2015-08-17 manual_coding_handbook/manual_coding_handbook.tex
Update manual coding handbook

--- 2015-06-09 manual_classification/manual_coding_handbook.tex
@@
 
-\usetheme{Dresden}
-
-%%% The following section removes the second lighter blue line below the navigation panel %%%
-\makeatletter
-\beamer@theme@subsectionfalse
-\makeatother
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\setbeamertemplate{frametitle}[default][center]
 
@@
 \definecolor{mygrey}{rgb}{0.85,0.85,0.85}
-\definecolor{myred}{rgb}{0.85,0.1,0.1}
+\definecolor{myred}{rgb}{0.8392,0.3765,0.302}
 \definecolor{mytextgrey}{rgb}{0.25, 0.25, 0.25}
@@
 
-\definecolor{beamer@blendedblue}{rgb}{0.0471,0.298,0.6824} % changed the default color
+\definecolor{beamer@blendedblue}{rgb}{0.1294,0.4,0.6745} % changed the default color
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title {\textbf{Manual Coding Handbook} \\[1cm]
-A New Indicator of Automation \\ Based on Patent Text Search}
+\title {\textbf{Manual Coding Handbook\\[0.15cm]
+for Automation Patents}}
 \author{
@@
 	\begin{itemize}	
-		\item Patents guarantee the intellectual property right to an innovation. In the US this right is for 20 years. 
+		\item Patents guarantee the intellectual property right to an innovation. In the US this right is granted for 20 years. 
 		\item People or firms apply for patents in a \textit{patent application} in which they describe, why a patent is new, useful and not trivial.
@@
 	\begin{itemize}	
+		\item title
 		\item abstract
@@
 You identify the right patent as the one starting with ``US".
-In the USPTO search interface, the right patent is often the last one in the list (don't ask us why...).
+In the USPTO search interface, the right patent is often the last one in the list.
 	\end{itemize}
@@
 We are only looking at patents that were granted in 1976 and the years after.
-The application dates can be earlier, though (sometimes a long time before 1976).
+The application dates can be earlier, though (sometimes long before 1976).
 	\item If there is a problem and you cannot figure it out, please indicate that in the comment box.
@@
 	\begin{itemize}	
-	\item \textit{Can I enter something else like 1? if I'm not quite sure?}\\[0.1cm]
+	\item \textit{Can I enter something else like ``1?" if I'm not quite sure?}\\[0.1cm]
 	No, please write your remarks in the comment box if you're not sure. 
@@
 It can also help to see which patents were cited (they are likely similar to the one you're looking at) and who applied for it (you might know the firm and infer something from that).
-You can also use outside knowledge (like Googling a term) if you think that helps.
+You can also use outside knowledge (like Googling a term).
 	\end{itemize}
@@
 	\item \textit{What if I don't understand what the patent is about?}\\[0.1cm]
-	No problem, just judge if you think this patent might have something to contribute to automation.
-If you're not sure \textit{beyond reasonable doubt} (to borrow such a legal term), please indicate this in the comment box.
+	No problem, just judge if you think this patent might have something to contribute to automation. If you're not at least reasonably sure, please indicate this in the comment box.
 	\end{itemize}
@@
 If it's less 30 seconds on average per patent, it's probably too fast.
-If it's more than 5 minutes per patent, it's probably too slow.
+If it's more than 5 minutes per patent on average, it's probably too slow.
 But the speed will likely differ between people.
 It's often much faster to see that a patent has \textit{nothing} to do with automation, rather than deciding it is an automation patent.
-It's ok (and indeed recommended by us) to take more time for those patents that you think might be automation patents.
+It's recommended by us to take more time for patents that you think might be automation patents.
 	\end{itemize}

### 2015-08-18 output/table_compare_classalg.tex
Implement more intricate 'Algorithm1' (look for many different words) and get reporting tools (barchart, table for paper) to work with them (+ table notes)

--- 2015-08-06 output/table_compare_classalg.tex
@@
 \begin{table}
-\begin{small}
+\begin{footnotesize}
 \begin{threeparttable}
@@
 \label{table:table_compare_classalg}
-\begin{tabular}{rllllllllll}
+\begin{tabular}{rlllllllll}
 \toprule 
- & \textbf{automat} & \textbf{robot} & \textbf{movable arm} & \textbf{algorithm} & \textbf{manual} & \textbf{software} & \textbf{computer} & \textbf{program} & \textbf{digital} & \textbf{autonomous}  \tabularnewline
-Accuracy & 0.79 & 0.76 & 0.76 & 0.78 & 0.71 & 0.77 & 0.76 & 0.72 & 0.76 & 0.77  \tabularnewline 
-Precision & 0.56 & 0.75 & 0.33 & 0.63 & 0.37 & 0.53 & 0.49 & 0.40 & 0.49 & 1.00  \tabularnewline 
-Recall & 0.56 & 0.03 & 0.01 & 0.19 & 0.27 & 0.22 & 0.36 & 0.30 & 0.35 & 0.03  \tabularnewline 
-F-measure & 0.56 & 0.06 & 0.02 & 0.29 & 0.31 & 0.31 & 0.42 & 0.34 & 0.41 & 0.06  \tabularnewline 
-AUC & 0.71 & 0.51 & 0.50 & 0.58 & 0.56 & 0.58 & 0.62 & 0.58 & 0.62 & 0.51  \tabularnewline 
-MCC & 0.42 & 0.11 & 0.02 & 0.25 & 0.14 & 0.23 & 0.27 & 0.17 & 0.27 & 0.15  \tabularnewline 
-Number "Yes" & 106 & 4 & 3 & 32 & 76 & 43 & 78 & 78 & 76 & 3  \tabularnewline 
+ & \textbf{automat} & \textbf{robot} & \textbf{movable arm} & \textbf{algorithm} & \textbf{manual} & \textbf{software} & \textbf{computer} & \textbf{program} & \textbf{digital}  \tabularnewline 
+Accuracy & 0.79 & 0.76 & 0.76 & 0.78 & 0.71 & 0.77 & 0.76 & 0.72 & 0.76  \tabularnewline 
+Precision & 0.56 & 0.75 & 0.33 & 0.63 & 0.37 & 0.53 & 0.49 & 0.40 & 0.49  \tabularnewline 
+Recall & 0.56 & 0.03 & 0.01 & 0.19 & 0.27 & 0.22 & 0.36 & 0.30 & 0.35  \tabularnewline 
+F-measure & 0.56 & 0.06 & 0.02 & 0.29 & 0.31 & 0.31 & 0.42 & 0.34 & 0.41  \tabularnewline 
+AUC & 0.71 & 0.51 & 0.50 & 0.58 & 0.56 & 0.58 & 0.62 & 0.58 & 0.62  \tabularnewline 
+MCC & 0.42 & 0.11 & 0.02 & 0.25 & 0.14 & 0.23 & 0.27 & 0.17 & 0.27  \tabularnewline 
+Number "Yes" & 106 & 4 & 3 & 32 & 76 & 43 & 78 & 78 & 76  \tabularnewline 
 \tabularnewline 
- & \textbf{adaptive} & \textbf{self-adjust} & \textbf{self-generat} & \textbf{detect} & \textbf{independent} & \textbf{motor} & \textbf{engine} & \textbf{communicat} & \textbf{semi-conductor} & \textbf{semiconductor}  \tabularnewline
-Accuracy & 0.76 & 0.75 & 0.76 & 0.71 & 0.66 & 0.73 & 0.68 & 0.73 & 0.75 & 0.70  \tabularnewline 
-Precision & 0.50 & 0.00 & 1.00 & 0.42 & 0.29 & 0.42 & 0.24 & 0.43 & 0.17 & 0.27  \tabularnewline 
-Recall & 0.05 & 0.00 & 0.01 & 0.50 & 0.30 & 0.34 & 0.15 & 0.45 & 0.01 & 0.14  \tabularnewline 
-F-measure & 0.09 & NaN & 0.02 & 0.46 & 0.29 & 0.38 & 0.19 & 0.44 & 0.02 & 0.19  \tabularnewline 
-AUC & 0.52 & 0.50 & 0.50 & 0.64 & 0.54 & 0.60 & 0.50 & 0.63 & 0.50 & 0.51  \tabularnewline 
-MCC & 0.09 & -0.05 & 0.09 & 0.27 & 0.07 & 0.21 & 0.00 & 0.26 & -0.02 & 0.03  \tabularnewline 
-Number "Yes" & 10 & 3 & 1 & 127 & 106 & 86 & 66 & 109 & 6 & 55  \tabularnewline 
+ & \textbf{autonomous} & \textbf{adaptive} & \textbf{self-adjust} & \textbf{self-generat} & \textbf{detect} & \textbf{independent} & \textbf{motor} & \textbf{engine} & \textbf{communicat}  \tabularnewline
+Accuracy & 0.77 & 0.76 & 0.75 & 0.76 & 0.71 & 0.66 & 0.73 & 0.68 & 0.73  \tabularnewline 
+Precision & 1.00 & 0.50 & 0.00 & 1.00 & 0.42 & 0.29 & 0.42 & 0.24 & 0.43  \tabularnewline 
+Recall & 0.03 & 0.05 & 0.00 & 0.01 & 0.50 & 0.30 & 0.34 & 0.15 & 0.45  \tabularnewline 
+F-measure & 0.06 & 0.09 & NaN & 0.02 & 0.46 & 0.29 & 0.38 & 0.19 & 0.44  \tabularnewline 
+AUC & 0.51 & 0.52 & 0.50 & 0.50 & 0.64 & 0.54 & 0.60 & 0.50 & 0.63  \tabularnewline 
+MCC & 0.15 & 0.09 & -0.05 & 0.09 & 0.27 & 0.07 & 0.21 & 0.00 & 0.26  \tabularnewline 
+Number "Yes" & 3 & 10 & 3 & 1 & 127 & 106 & 86 & 66 & 109  \tabularnewline 
 \tabularnewline 
- & \textbf{chip} & \textbf{bus} & \textbf{circuit} & \textbf{circuitry} & \textbf{antigen} & \textbf{antigenic} & \textbf{chromatography} & \textbf{Bessen-Hunt} & \textbf{Always 'No'} & \textbf{Always 'Yes'}  \tabularnewline
-Accuracy & 0.69 & 0.68 & 0.66 & 0.74 & 0.75 & 0.76 & 0.71 & 0.78 & 0.76 & 0.24  \tabularnewline 
-Precision & 0.20 & 0.33 & 0.36 & 0.41 & 0.00 & 0.00 & 0.10 & 0.57 & NaN & 0.24  \tabularnewline 
-Recall & 0.10 & 0.30 & 0.53 & 0.19 & 0.00 & 0.00 & 0.03 & 0.29 & 0.00 & 1.00  \tabularnewline 
-F-measure & 0.13 & 0.31 & 0.43 & 0.26 & NaN & NaN & 0.04 & 0.38 & NaN & 0.39  \tabularnewline 
-AUC & 0.49 & 0.55 & 0.62 & 0.55 & 0.49 & 0.50 & 0.47 & 0.61 & 0.50 & 0.50  \tabularnewline 
-MCC & -0.04 & 0.11 & 0.21 & 0.14 & -0.07 & -0.04 & -0.09 & 0.28 & NaN & NaN  \tabularnewline 
-Number "Yes" & 51 & 95 & 155 & 49 & 6 & 2 & 30 & 53 & 0 & 438  \tabularnewline 
+ & \textbf{semi-conductor} & \textbf{semiconductor} & \textbf{chip} & \textbf{bus} & \textbf{circuit} & \textbf{circuitry} & \textbf{antigen} & \textbf{antigenic} & \textbf{chromatography}  \tabularnewline
+Accuracy & 0.75 & 0.70 & 0.69 & 0.68 & 0.66 & 0.74 & 0.75 & 0.76 & 0.71  \tabularnewline 
+Precision & 0.17 & 0.27 & 0.20 & 0.33 & 0.36 & 0.41 & 0.00 & 0.00 & 0.10  \tabularnewline 
+Recall & 0.01 & 0.14 & 0.10 & 0.30 & 0.53 & 0.19 & 0.00 & 0.00 & 0.03  \tabularnewline 
+F-measure & 0.02 & 0.19 & 0.13 & 0.31 & 0.43 & 0.26 & NaN & NaN & 0.04  \tabularnewline 
+AUC & 0.50 & 0.51 & 0.49 & 0.55 & 0.62 & 0.55 & 0.49 & 0.50 & 0.47  \tabularnewline 
+MCC & -0.02 & 0.03 & -0.04 & 0.11 & 0.21 & 0.14 & -0.07 & -0.04 & -0.09  \tabularnewline 
+Number "Yes" & 6 & 55 & 51 & 95 & 155 & 49 & 6 & 2 & 30  \tabularnewline 
+\tabularnewline 
+ & \textbf{Algorithm1} & \textbf{Bessen-Hunt} & \textbf{Always "No"} & \textbf{Always "Yes"}  \tabularnewline 
+Accuracy & 0.78 & 0.78 & 0.76 & 0.24 & & & & &  \tabularnewline 
+Precision & 0.53 & 0.57 & NaN & 0.24 & & & & &  \tabularnewline 
+Recall & 0.69 & 0.29 & 0.00 & 1.00 & & & & &  \tabularnewline 
+F-measure & 0.60 & 0.38 & NaN & 0.39 & & & & &  \tabularnewline 
+AUC & 0.75 & 0.61 & 0.50 & 0.50 & & & & &  \tabularnewline 
+MCC & 0.45 & 0.28 & NaN & NaN & & & & &  \tabularnewline 
+Number "Yes" & 137 & 53 & 0 & 438 & & & & &  \tabularnewline 
 \bottomrule 
@@
 \begin{tablenotes}
-\small
-\item\textit{Note:} Every column is a different classification algorithms.
+\footnotesize
+\item\textit{Note:} Classified as automation patents if at least one match of keywords in all parts of patent.
+\item Algorithm1: (anywhere in patent:) ``automat" OR ``robot" OR ``movable arm" OR ``autonomous" OR  ``adaptive" OR ``self-generat" OR (in title + abstract:) ``detect" OR ``program" OR ``computer".
+\item Bessen-Hunt: (anywhere in patent:) ``software" OR (``computer" AND ``program") ANDNOT ((in title:) ``chip" OR ``semiconductor" OR ``bus" OR ``circuit" OR ``circuitry") ANDNOT ((anwhere in patent:) ``antigen" OR ``antigenic" OR ``chromatography").
 \item F-measure: balanced F-measure which is the evenly weightened harmonic mean between Precision and Recall. 
@@
 \end{threeparttable}
-\end{small}
+\end{footnotesize}
 \end{table}

### 2015-08-18 manual_classification/make_table_compare_classalg.m

@@ -18,7 +18,7 @@ printname = 'output/table_compare_classalg.tex';
 FID = fopen(printname, 'w');
 
 fprintf(FID, '\\begin{table}\n');
-fprintf(FID, '\\begin{small}\n');
+fprintf(FID, '\\begin{footnotesize}\n');
 fprintf(FID, '\\begin{threeparttable}\n');
 fprintf(FID, '\\caption{{\\normalsize Evaluation of different classification algorithms}}\n');
 fprintf(FID, '\\label{table:table_compare_classalg}\n');
@@ -89,15 +89,17 @@ end
 
 fprintf(FID,'\\end{tabular} \n');
 fprintf(FID, '\\begin{tablenotes}\n');
-fprintf(FID, '\\small\n');
-fprintf(FID,'\\item\\textit{Note:} Every column is a different classification algorithms.\n');
+fprintf(FID, '\\footnotesize\n');
+fprintf(FID,'\\item\\textit{Note:} Classified as automation patents if at least one match of keywords in all parts of patent. ');
+fprintf(FID,'\\item Algorithm1: (anywhere in patent:) ``automat" OR ``robot" OR ``movable arm" OR ``autonomous" OR  ``adaptive" OR ``self-generat" OR (in title + abstract:) ``detect" OR ``program" OR ``computer".\n');
+fprintf(FID,'\\item Bessen-Hunt: (anywhere in patent:) ``software" OR (``computer" AND ``program") ANDNOT ((in title:) ``chip" OR ``semiconductor" OR ``bus" OR ``circuit" OR ``circuitry") ANDNOT ((anwhere in patent:) ``antigen" OR ``antigenic" OR ``chromatography").\n')
 fprintf(FID,'\\item F-measure: balanced F-measure which is the evenly weightened harmonic mean between Precision and Recall. \n');
 fprintf(FID,'\\item AUC: Area under (the receiver operating) curve.\n');
 fprintf(FID,'\\item MCC: Matthew''s correlation coefficient.\n');
 fprintf(FID,'\\item\\textit{Source:} USPTO, Google and own calculations.\n');
 fprintf(FID, '\\end{tablenotes}\n');
 fprintf(FID, '\\end{threeparttable}\n');
-fprintf(FID, '\\end{small}\n');
+fprintf(FID, '\\end{footnotesize}\n');
 fprintf(FID, '\\end{table}\n');
 fclose(FID); 
 

### 2015-08-18 manual_classification/plot_bar_fmeasure.m

@@ -1,6 +1,8 @@
 function plot_bar_fmeasure(fmeasure, algorithm_name)
 
-fmeasure(isnan(fmeasure)) = 0;
+% It's possible for there to be missing values in the F-measure. For the
+% figure, replace these by zero.
+fmeasure( isnan(fmeasure) ) = 0;
 [fmeasure_sorted, ix_sort] = sort(fmeasure, 'descend');
 
 word_dict = algorithm_name(ix_sort);
@@ -18,9 +20,8 @@ my_light_gray = [240, 240, 240] ./ 255;
 nr_words = length(word_dict);
 
 color1_pick = my_dark_gray;
-bar(fmeasure_sorted, 0.7, 'FaceColor', color1_pick, 'EdgeColor', color1_pick, ... 
-    'LineWidth', 1.5)
-
+bar(fmeasure_sorted, 0.7, 'FaceColor', color1_pick, 'EdgeColor', ...
+    color1_pick, 'LineWidth', 1.5)
 
 set(gca, 'TickLength', [0 0]) % turn tick marks off
 

### 2015-08-18 make_figures/plot_alg1_overtime.m
Update contigency table for Algorithm1

@@ -1,0 +1,79 @@
+function plot_alg1_overtime(year_start, year_end)
+
+%%
+% Set font
+set(0, 'DefaultTextFontName', 'Palatino')
+set(0, 'DefaultAxesFontName', 'Palatino')
+
+
+% Load summary data
+build_load_filename = horzcat('allyr_patstats_', num2str(year_start), ...
+    '-', num2str(year_end), '.mat');
+load(build_load_filename)
+
+
+plot_series = allyr_patstats.total_alg1_week;
+
+
+% Make time series plot of matches per week
+my_xaxis_labels = {1976; ''; ''; ''; 1980; ''; ''; ''; ''; 1985; ''; ...
+    ''; ''; ''; 1990; ''; ''; ''; ''; 1995; ''; ''; ''; ''; 2000; ''; ...
+    ''; ''; ''; 2005; ''; ''; ''; ''; 2010; ''; ''; ''; ''; 2015};
+
+
+color1_pick = [0.3, 0.3, 0.3]; % dark gray
+my_gray = [0.806, 0.806, 0.806]; % light gray
+
+
+figureHandle = figure;
+
+set(gca,'FontSize', 22) % change default font size of axis labels
+
+h_gline = plot(1:length(plot_series), repmat(1000, ...
+    length(plot_series), 1), 'Color', my_gray , ...
+    'linewidth', 0.5);
+uistack(h_gline, 'bottom');
+hold on
+h_gline = plot(1:length(plot_series), repmat(2000, ...
+    length(plot_series), 1), 'Color', my_gray , ...
+    'linewidth', 0.5);
+uistack(h_gline, 'bottom');
+hold on
+h_gline = plot(1:length(plot_series), repmat(3000, ...
+    length(plot_series), 1), 'Color', my_gray , ...
+    'linewidth', 0.5);
+uistack(h_gline, 'bottom');
+hold on
+
+h_scatter = scatter(1:length(plot_series), plot_series, ...
+    'Marker', 'o', 'MarkerEdgeColor', color1_pick);
+
+uistack(h_scatter, 'top');
+
+xlim([1 length(plot_series)])
+ylim([0 3500])
+set(gca, 'XTick', allyr_patstats.ix_new_year) % Set the x-axis tick labels
+set(gca, 'xticklabel',{}) % turn x-axis labels off
+set(gca, 'xticklabel', my_xaxis_labels); 
+
+set(gca,'TickDir','out')  
+box off
+set(gcf, 'Color', 'white');
+
+
+% Reposition the figure
[…]

### 2015-08-18 manual_classification/bessen_hunt.m

@@ -1,0 +1,56 @@
+function bh_software_patents = bessen_hunt(automclassData, indic_spec)
+% Implement the classification algorithm of:
+%   Bessen, James and Robert Hunt (2007). "An Empirical Look at 
+%   Software Patents". Journal of Economics and Management Strategy, 
+%   16(1): 1578–189.
+    
+% Search for these words on what Bessen and Hunt call the patent
+% "specification". 
+searchdict_spec = {'software', 'computer', 'program', 'antigen', ...
+    'antigenic', 'chromatography'};
+
+searchdict_title = {'chip', 'semiconductor', 'bus', 'circuit', ...
+    'circuitry'};
+
+% Count matches in "specification"
+for i=1:length(searchdict_spec)
+    pick_word = searchdict_spec{i};
+    ix_pos = find( strcmp(automclassData.dictionary, pick_word) );
+
+    if indic_spec == 1
+        spec_matches = automclassData.body_matches;
+    elseif indic_spec == 2
+        spec_matches = automclassData.abstract_matches + ...
+            automclassData.body_matches;
+    elseif indic_spec == 3
+        spec_matches = automclassData.title_matches + ...
+            automclassData.abstract_matches + ...
+            automclassData.body_matches;
+    else
+        warning('''indic_spec'' not well-specified.')
+    end
+
+    spec_results(:, i) = count_matches_greaterZero(spec_matches, ...
+        ix_pos);
+end
+
+% Count matches in title
+for i=1:length(searchdict_title)
+    pick_word = searchdict_title{i};
+    ix_pos = find( strcmp(automclassData.dictionary, pick_word) );       
+    title_results(:, i) = count_matches_greaterZero( ...
+        automclassData.title_matches, ix_pos);
+end
+
+exclusion_patents = [title_results, spec_results(:, end-2:end)];
+exclude_if_any = max(exclusion_patents, [], 2);
+
+% Include if "computer" and "program"
+computer_program = spec_results(:, 2) & spec_results(:, 3);
+
+% Either "software" or "computer_program"
+software_patents = spec_results(:, 1) | computer_program;
+
+% Exclude some
+bh_software_patents = software_patents & not( exclude_if_any );    
+bh_software_patents = + bh_software_patents; % logical to vector

### 2015-08-18 manual_classification/classify_autom_algorith.m

@@ -16,25 +16,19 @@ function computerClass = classify_autom_algorith(automclassData)
     end
 
     
-    % (Anwhere:) "automat" OR "robot" OR "movable arm" OR "autonomous" OR 
-    % "adaptive" OR "self-generat" OR (in title + abstract) "detect" 
-    % OR "program" OR "computer"
-    anwhere_words = {'automat', 'robot', 'movable arm', 'autonomous', ...
-        'adaptive', 'self-generat'};  
-    mat_classif_1 = multiple_class(automclassData.dictionary, total_matches, anwhere_words);
-    
-    titleabstract_words = {'detect', 'program', 'computer'};
-    mat_classif_2 = multiple_class(automclassData.dictionary, ...
-        automclassData.title_matches + automclassData.abstract_matches, ...
-        titleabstract_words);
-    
-    % Pick those words that contain any of those
-    class_pat = max([mat_classif_1, mat_classif_2], [], 2);
+    % Use Algorithm1
+   class_pat = classif_alg1(automclassData.dictionary, automclassData.title_matches, ...
+       automclassData.abstract_matches, automclassData.body_matches);
     compAutomat = [compAutomat, class_pat];
     algorithm_name = [algorithm_name, 'Algorithm1'];
     
     % Bessen-Hunt classification of software patents
-    bh_software_patents = bessen_hunt(automclassData, 1);
+    %   Choose a specification (indic_spec):
+    %       1: body only
+    %       2: abstract + body
+    %       3: title + abstract + body
+    indic_spec = 3;
+    bh_software_patents = bessen_hunt(automclassData, indic_spec);
     compAutomat = [compAutomat, bh_software_patents];
     algorithm_name = [algorithm_name, 'Bessen-Hunt'];
 
@@ -51,84 +45,4 @@ function computerClass = classify_autom_algorith(automclassData)
     % Save in structure
     computerClass.compAutomat = compAutomat;
     computerClass.algorithm_name = algorithm_name;
-end
-    
-
-function ix_classif = count_matches_greaterZero(matches, ...
-    ix_keyword)
-    
-    ix_classif = ( matches(:, ix_keyword) >= 1 );
-    ix_classif = +ix_classif; % logical to double (vector)
-end
-
-
-function mat_classif = multiple_class(searchdict, matches, choose_dict)
-    for i=1:length(choose_dict)
-        pick_word = choose_dict{i};
-        ix_pos = find_word_in_dict(searchdict, pick_word);    
[…]

### 2015-08-18 manual_classification/count_matches_greaterZero.m

@@ -1,0 +1,4 @@
+function ix_classif = count_matches_greaterZero(matches, ix_keyword)
+
+ix_classif = ( matches(:, ix_keyword) >= 1 );
+ix_classif = +ix_classif; % logical to double (vector)

### 2015-08-18 manual_classification/make_contingency_table.m

@@ -10,23 +10,37 @@ fprintf(FID,'\\begin{small}\n');
 fprintf(FID,'\\begin{threeparttable}\n');
 fprintf(FID,'\\caption{{\\normalsize Contingency table}}\n');
 fprintf(FID,'\\label{table:contingency_table}\n');
-fprintf(FID,'\\begin{tabular}{lrlll}\n');
-fprintf(FID, '\\toprule');
-fprintf(FID, ' & & & &  \\tabularnewline[-0.3cm]\n');
-fprintf(FID, ' & & \\multicolumn{3}{c}{Computerized} \\tabularnewline[0.1cm]\n');
-fprintf(FID, ' & & \\multicolumn{1}{|l}{No}  & \\multicolumn{1}{l|}{Yes} \\tabularnewline\n');
+fprintf(FID,'\\begin{tabular}{lrllll}\n');
+fprintf(FID, '\\toprule \n');
+fprintf(FID, ' & & & &  & \\tabularnewline[-0.3cm]\n');
+fprintf(FID, ' & & \\multicolumn{3}{c}{Computerized} & \\tabularnewline[0.1cm]\n');
+fprintf(FID, ' & & \\multicolumn{1}{|l}{No}  & \\multicolumn{1}{l|}{Yes} & \\tabularnewline\n');
 fprintf(FID, '\\cline{3-5} \n');
-fprintf(FID, '\\parbox[t]{0mm}{\\multirow{2}{*}{\\rotatebox[origin=c]{90}{Manual}}} & No & \\multicolumn{1}{|l}{%d} & \\multicolumn{1}{l|}{%d} & %d \\tabularnewline\n', classifstat.true_negative, classifstat.false_positive, classifstat.true_negative + classifstat.false_positive);
-fprintf(FID, ' & Yes & \\multicolumn{1}{|l}{%d} & \\multicolumn{1}{l|}{%d} & %d \\tabularnewline\n', classifstat.false_negative, classifstat.true_positive, classifstat.false_negative + classifstat.true_positive);
+fprintf(FID, '\\parbox[t]{0mm}{\\multirow{2}{*}{\\rotatebox[origin=c]{90}{Manual}}} & No & \\multicolumn{1}{|l}{%d} & \\multicolumn{1}{l|}{%d} & %d & \\tabularnewline\n', classifstat.true_negative, classifstat.false_positive, classifstat.true_negative + classifstat.false_positive);
[…]

### 2015-08-18 manual_classification/make_table_compare_classalg.m

@@ -92,7 +92,7 @@ fprintf(FID, '\\begin{tablenotes}\n');
 fprintf(FID, '\\footnotesize\n');
 fprintf(FID,'\\item\\textit{Note:} Classified as automation patents if at least one match of keywords in all parts of patent. ');
 fprintf(FID,'\\item Algorithm1: (anywhere in patent:) ``automat" OR ``robot" OR ``movable arm" OR ``autonomous" OR  ``adaptive" OR ``self-generat" OR (in title + abstract:) ``detect" OR ``program" OR ``computer".\n');
-fprintf(FID,'\\item Bessen-Hunt: (anywhere in patent:) ``software" OR (``computer" AND ``program") ANDNOT ((in title:) ``chip" OR ``semiconductor" OR ``bus" OR ``circuit" OR ``circuitry") ANDNOT ((anwhere in patent:) ``antigen" OR ``antigenic" OR ``chromatography").\n')
+fprintf(FID,'\\item Bessen-Hunt: (anywhere in patent:) ``software" OR (``computer" AND ``program") ANDNOT ((in title:) ``chip" OR ``semiconductor" OR ``bus" OR ``circuit" OR ``circuitry") ANDNOT ((anwhere in patent:) ``antigen" OR ``antigenic" OR ``chromatography").\n');
 fprintf(FID,'\\item F-measure: balanced F-measure which is the evenly weightened harmonic mean between Precision and Recall. \n');
 fprintf(FID,'\\item AUC: Area under (the receiver operating) curve.\n');
 fprintf(FID,'\\item MCC: Matthew''s correlation coefficient.\n');

### 2015-08-18 run_patentsearch.m

@@ -66,18 +66,22 @@ years = year_start:year_end;
 
 %% Make some visualizations 
 % dim_subplot = [6, 5];
-% 
+
 % plot_matches_overtime(year_start, year_end, dim_subplot)
 % plot_matches_over_nrpatents_weekly(year_start, year_end, dim_subplot)
 % plot_mean_len_pattxt(year_start, year_end)
 % plot_pat1m_over_nrlines(year_start, year_end)
 % plot_nr_pat1m(year_start, year_end)
 % plot_error_nr_patents % compares number of yearly patents 1976-2014
-% 
-% % Plot the classified automation patents
+
+% Plot the classified automation patents
 % pick_k = 1; % 1: "automat"
 % plot_pat1m_over_nrpatents_weekly(year_start, year_end, pick_k)
 % plot_pat1m_overtime(year_start, year_end, pick_k)
+
+% plot_alg1_overtime(year_start, year_end)
+% plot_alg1_over_nrpatents_weekly(year_start, year_end)
+
 
 
 %% Link patents to industries
@@ -136,21 +140,23 @@ end
 
 classalg_comparison.algorithm_name = computerClass.algorithm_name;
 
-plot_bar_fmeasure(classalg_comparison.fmeasure, computerClass.algorithm_name)
+% plot_bar_fmeasure(classalg_comparison.fmeasure, computerClass.algorithm_name)
 
 
+ix_alg = find( strcmp(computerClass.algorithm_name, 'Algorithm1') );
 classifstat = calculate_manclass_stats(manclassData.manAutomat, ...
-    computerClass.compAutomat(:, 1));
-
+    computerClass.compAutomat(:, ix_alg))
 make_contingency_table(classifstat)
+
+copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\table_contingency.tex', ...
+    'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\tables')
 
 max_line = 9; % choose number of algorithms to put on line for table in paper
 make_table_compare_classalg(classalg_comparison, max_line)
 
-
-%% Copy tables
 copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\table_compare_classalg.tex', ...
     'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\tables')
+
 
 
 

### 2015-08-19 manual_classification/make_contingency_table.m
Add superscript 1 to fmeasure in table + change name from handbook to guidelines

@@ -26,7 +26,7 @@ fprintf(FID, '\\rule{0pt}{12pt} & Accuracy & \\multicolumn{3}{r}{$\\frac{%d + %d
 fprintf(FID, '\\rule{0pt}{12pt}& Precision & \\multicolumn{3}{r}{$\\frac{%d}{%d} = %3.2f$} & \\tabularnewline\n', classifstat.true_positive, classifstat.false_positive + classifstat.true_positive, classifstat.precision);
 fprintf(FID, '\\rule{0pt}{12pt}& Recall & \\multicolumn{3}{r}{$\\frac{%d}{%d} = %3.2f$} &  \\tabularnewline\n', classifstat.true_positive, classifstat.false_negative + classifstat.true_positive, classifstat.recall);
 % Only print the beta once
-fprintf(FID, '\\rule{0pt}{12pt}& $F_1$ & \\multicolumn{3}{r}{%3.2f} & \\tabularnewline\n', classifstat.fmeasure);
+fprintf(FID, '\\rule{0pt}{12pt}& $F_1^1$ & \\multicolumn{3}{r}{%3.2f} & \\tabularnewline\n', classifstat.fmeasure);
 fprintf(FID, '\\rule{0pt}{12pt}& AUC$^2$ & \\multicolumn{3}{r}{%3.2f} & \\tabularnewline\n', classifstat.auc);
 fprintf(FID, '\\rule{0pt}{12pt}& MCC$^3$ & \\multicolumn{3}{r}{%3.2f} & \\tabularnewline\n', classifstat.matthewscorrcoeff);
 
@@ -41,6 +41,7 @@ fprintf(FID,'\\item $^2$: Area under (the receiver operating) curve.\n');
 fprintf(FID,'\\item $^3$: Matthew''s correlation coefficient.\n');
 fprintf(FID,'\\item\\textit{Source:} USPTO, Google and own calculations.\n');
 fprintf(FID,'\\end{tablenotes}\n');
+% fprintf(FID, '\\multicolumn{6}{l}{\\textit{Source:} USPTO, Google and own calculations.} \\tabularnewline\n');
 fprintf(FID,'\\end{threeparttable}\n');
 fprintf(FID,'\\end{small}\n');
 fprintf(FID,'\\end{table}\n');

### 2015-08-19 output/table_compare_classalg.tex
Move the comparision of the class. algs evaluation to separate function

@@
 \begin{table}
-\begin{footnotesize}
+\begin{small}
 \begin{threeparttable}
@@
 \toprule 
- & \textbf{automat} & \textbf{robot} & \textbf{movable arm} & \textbf{algorithm} & \textbf{manual} & \textbf{software} & \textbf{computer} & \textbf{program} & \textbf{digital}  \tabularnewline 
-Accuracy & 0.79 & 0.76 & 0.76 & 0.78 & 0.71 & 0.77 & 0.76 & 0.72 & 0.76  \tabularnewline 
-Precision & 0.56 & 0.75 & 0.33 & 0.63 & 0.37 & 0.53 & 0.49 & 0.40 & 0.49  \tabularnewline 
-Recall & 0.56 & 0.03 & 0.01 & 0.19 & 0.27 & 0.22 & 0.36 & 0.30 & 0.35  \tabularnewline 
-F-measure & 0.56 & 0.06 & 0.02 & 0.29 & 0.31 & 0.31 & 0.42 & 0.34 & 0.41  \tabularnewline 
-AUC & 0.71 & 0.51 & 0.50 & 0.58 & 0.56 & 0.58 & 0.62 & 0.58 & 0.62  \tabularnewline 
-MCC & 0.42 & 0.11 & 0.02 & 0.25 & 0.14 & 0.23 & 0.27 & 0.17 & 0.27  \tabularnewline 
-Number "Yes" & 106 & 4 & 3 & 32 & 76 & 43 & 78 & 78 & 76  \tabularnewline 
-\tabularnewline 
- & \textbf{autonomous} & \textbf{adaptive} & \textbf{self-adjust} & \textbf{self-generat} & \textbf{detect} & \textbf{independent} & \textbf{motor} & \textbf{engine} & \textbf{communicat}  \tabularnewline
-Accuracy & 0.77 & 0.76 & 0.75 & 0.76 & 0.71 & 0.66 & 0.73 & 0.68 & 0.73  \tabularnewline 
-Precision & 1.00 & 0.50 & 0.00 & 1.00 & 0.42 & 0.29 & 0.42 & 0.24 & 0.43  \tabularnewline 
-Recall & 0.03 & 0.05 & 0.00 & 0.01 & 0.50 & 0.30 & 0.34 & 0.15 & 0.45  \tabularnewline 
-F-measure & 0.06 & 0.09 & NaN & 0.02 & 0.46 & 0.29 & 0.38 & 0.19 & 0.44  \tabularnewline 
-AUC & 0.51 & 0.52 & 0.50 & 0.50 & 0.64 & 0.54 & 0.60 & 0.50 & 0.63  \tabularnewline 
-MCC & 0.15 & 0.09 & -0.05 & 0.09 & 0.27 & 0.07 & 0.21 & 0.00 & 0.26  \tabularnewline 
-Number "Yes" & 3 & 10 & 3 & 1 & 127 & 106 & 86 & 66 & 109  \tabularnewline 
-\tabularnewline 
- & \textbf{semi-conductor} & \textbf{semiconductor} & \textbf{chip} & \textbf{bus} & \textbf{circuit} & \textbf{circuitry} & \textbf{antigen} & \textbf{antigenic} & \textbf{chromatography}  \tabularnewline
-Accuracy & 0.75 & 0.70 & 0.69 & 0.68 & 0.66 & 0.74 & 0.75 & 0.76 & 0.71  \tabularnewline 
-Precision & 0.17 & 0.27 & 0.20 & 0.33 & 0.36 & 0.41 & 0.00 & 0.00 & 0.10  \tabularnewline 
-Recall & 0.01 & 0.14 & 0.10 & 0.30 & 0.53 & 0.19 & 0.00 & 0.00 & 0.03  \tabularnewline 
-F-measure & 0.02 & 0.19 & 0.13 & 0.31 & 0.43 & 0.26 & NaN & NaN & 0.04  \tabularnewline 
-AUC & 0.50 & 0.51 & 0.49 & 0.55 & 0.62 & 0.55 & 0.49 & 0.50 & 0.47  \tabularnewline 
-MCC & -0.02 & 0.03 & -0.04 & 0.11 & 0.21 & 0.14 & -0.07 & -0.04 & -0.09  \tabularnewline 
-Number "Yes" & 6 & 55 & 51 & 95 & 155 & 49 & 6 & 2 & 30  \tabularnewline 
-\tabularnewline 
- & \textbf{Algorithm1} & \textbf{Bessen-Hunt} & \textbf{Always "No"} & \textbf{Always "Yes"}  \tabularnewline 
-Accuracy & 0.78 & 0.78 & 0.76 & 0.24 & & & & &  \tabularnewline 
-Precision & 0.53 & 0.57 & NaN & 0.24 & & & & &  \tabularnewline 
-Recall & 0.69 & 0.29 & 0.00 & 1.00 & & & & &  \tabularnewline 
-F-measure & 0.60 & 0.38 & NaN & 0.39 & & & & &  \tabularnewline 
-AUC & 0.75 & 0.61 & 0.50 & 0.50 & & & & &  \tabularnewline 
-MCC & 0.45 & 0.28 & NaN & NaN & & & & &  \tabularnewline 
-Number "Yes" & 137 & 53 & 0 & 438 & & & & &  \tabularnewline 
+ & \textbf{Algorithm1} & \textbf{automat} & \textbf{Bessen-Hunt} & \textbf{Always "No"} & \textbf{Always "Yes"}  \tabularnewline 
+Accuracy & 0.78 & 0.79 & 0.78 & 0.76 & 0.24 & & & &  \tabularnewline 
+Precision & 0.53 & 0.56 & 0.57 & NaN & 0.24 & & & &  \tabularnewline 
+Recall & 0.69 & 0.56 & 0.29 & 0.00 & 1.00 & & & &  \tabularnewline 
+F-measure & 0.60 & 0.56 & 0.38 & NaN & 0.39 & & & &  \tabularnewline 
+AUC & 0.75 & 0.71 & 0.61 & 0.50 & 0.50 & & & &  \tabularnewline 
+MCC & 0.45 & 0.42 & 0.28 & NaN & NaN & & & &  \tabularnewline 
+Number "Yes" & 137 & 106 & 53 & 0 & 438 & & & &  \tabularnewline 
 \bottomrule 
@@
 \begin{tablenotes}
-\footnotesize
+\small
 \item\textit{Note:} Classified as automation patents if at least one match of keywords in all parts of patent.
@@
 \end{threeparttable}
-\end{footnotesize}
+\end{small}
 \end{table}

### 2015-08-19 run_patentsearch.m

@@ -121,35 +121,40 @@ computerClass = classify_autom_algorith(automclassData);
 
 
 
-% Make a contingency table comparing the manual vs. the computer
-% classification of patents
+%% Compare manual vs. computer classification of patents
 
-for i=1:size(computerClass.compAutomat, 2)
-    classifstat = calculate_manclass_stats(manclassData.manAutomat, ...
-        computerClass.compAutomat(:, i));
-    
-    classalg_comparison.accuracy(i) = classifstat.accuracy;
-    classalg_comparison.precision(i) = classifstat.precision;
-    classalg_comparison.recall(i) = classifstat.recall;
-    classalg_comparison.fmeasure(i) = classifstat.fmeasure;
-    classalg_comparison.auc(i) = classifstat.auc;
-    classalg_comparison.matthewscorrcoeff(i) = classifstat.matthewscorrcoeff;
-    classalg_comparison.nr_Yes(i) = classifstat.false_positive + ...
-        classifstat.true_positive;
-end
-
-classalg_comparison.algorithm_name = computerClass.algorithm_name;
-
-% plot_bar_fmeasure(classalg_comparison.fmeasure, computerClass.algorithm_name)
-
-
+% Report contingency table for Algorithm1 only
 ix_alg = find( strcmp(computerClass.algorithm_name, 'Algorithm1') );
 classifstat = calculate_manclass_stats(manclassData.manAutomat, ...
-    computerClass.compAutomat(:, ix_alg))
+    computerClass.compAutomat(:, ix_alg));
 make_contingency_table(classifstat)
 
 copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\table_contingency.tex', ...
     'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\tables')
+
+
+% Compare all algorithms
+% choose_compalg_list = computerClass.algorithm_name; % pick all algorithms
+% classalg_comparison = comp_evals_algs(choose_compalg_list, ...
+%     computerClass, manclassData);
+% 
+% plot_bar_fmeasure(classalg_comparison.fmeasure, classalg_comparison.algorithm_name)
+% 
+% max_line = 9; % choose number of algorithms to put on line for table in paper
+% make_table_compare_classalg(classalg_comparison, max_line)
+% 
[…]

### 2015-08-19 make_figures/make_barchart_nrpatents.m
Adopt plots and tables for Algorithm1

@@ -1,96 +1,0 @@
-close all
-clear all
-clc
-
-% Define parameters
-year_start = 1976;
-year_end = 2015;
-
-
-
-
-
-%% Load summary data
-build_load_filename = horzcat('patent_match_summary_', num2str(year_start), ...
-    '-', num2str(year_end), '.mat');
-load(build_load_filename)
-
-
-%% Print some summaries
-fprintf('Total number of identified patents all years: %d.\n', ...
-    sum(patent_match_summary.nr_patents_yr))
-
-
-
-%% Some settings for the plots
-plot_time = year_start:year_end;
-color1_pick = [0.7900, 0.3800, 0.500];
-color2_pick = [0.000,0.639,0.561];
-color3_pick = [0.890,0.412,0.525];
-color4_pick = [0.890,0.412,0.525];
-
-color1_pick = [49, 130, 189] ./ 255; % necessary conversion to RGB  
-color2_pick = [158, 202, 225] ./ 255;
-
-my_light_gray = [0.95, 0.95, 0.95];
-my_dark_gray = [0.8, 0.8, 0.8];
-
-
-figureHandle = figure;
-
-% Plot total number of identified patents per year
-bar(plot_time, patent_match_summary.nr_patents_yr, 'FaceColor', ...
-    color1_pick, 'EdgeColor', 'k')
-hold on
-bar(plot_time, patent_match_summary.nr_distinct_patents_hits, ...
-    'FaceColor', color2_pick, 'EdgeColor', 'k')
-hold off
-
-set(gca,'FontSize',12) % change default font size of axis labels
-box off
-set(gca,'TickDir','out'); 
-ylim([0 400000])
-set(gca, 'YTickLabel', num2str(get(gca, 'YTick')')) % turn scientific notation off
-
-get(gca, 'YTickLabel');
-new_yticks = {'0'; ''; '100000'; ''; '200000'; ''; '300000'; ''; '400000'};
-set(gca, 'yticklabel', new_yticks); 
-
-xlim([year_start-0.5, year_end+1.5])
-
-% General settings
-set(gcf, 'Color', 'w');
-
-set(0,'DefaultTextFontName','Palatino') % set font
-set(0,'DefaultAxesFontName','Palatino') % set font
-
-
-
-
-%% Change position and size
-set(gcf, 'Position', [100 200 700 400]) % in vector: left bottom width height
-set(figureHandle, 'Units', 'Inches');
[…]

### 2015-08-19 make_figures/make_table_autompatshare_1column.m

@@ -1,78 +1,0 @@
-close all
-clear all
-clc
-
-% Define parameters
-year_start = 1976;
-year_end = 2015;
-
-
-
-
-
-%% Load summary data
-build_load_filename = horzcat('patent_match_summary_', num2str(year_start), ...
-    '-', num2str(year_end), '.mat');
-load(build_load_filename)
-
-
-%% Print some summaries
-fprintf('Total number of identified patents all years: %d.\n', ...
-    sum(patent_match_summary.nr_patents_yr))
-
-fprintf('Total number of keyword matches in all years: %d.\n', ...
-    sum(patent_match_summary.total_matches_yr))
-
-
-
-%% Make table
-
-% Print to .txt file in Latex format
-printname = 'table_autompat_share.tex';
-
-FID = fopen(printname, 'w');
-
-fprintf(FID,'\\begin{table}\n');
-fprintf(FID,'\\begin{small}\n');
-fprintf(FID,'\\begin{threeparttable}\n');
-fprintf(FID,'\\caption{{\\normalsize Share of automation patents}}\n');
-fprintf(FID,'\\label{tab:word_distribution}\n');
-fprintf(FID,'\\begin{tabular}{lrrr}\n');
-fprintf(FID,'\\toprule \\addlinespace[0.5em]\n');
-fprintf(FID,' & \\textbf{Automation patents$^1$} & \\textbf{Total patents} & \\textbf{Share (\\%%)}\\tabularnewline[0.1cm]\n');
-fprintf(FID,'\\midrule \\addlinespace[0.5em]\n');
-
-for t=1:length(patent_match_summary.nr_patents_yr)
-    ix_year = year_start + t - 1;
-    
-    if ix_year == 2015
-       fprintf(FID,'2015$^2$ & %d & %d & %3.1f \\tabularnewline[0.1cm]\n', patent_match_summary.nr_distinct_patents_hits(t), patent_match_summary.nr_patents_yr(t), patent_match_summary.nr_distinct_patents_hits(t)/patent_match_summary.nr_patents_yr(t)*100);
-    else
[…]

### 2015-08-19 make_figures/make_table_autompatshare_2column.m

@@ -1,58 +1,0 @@
-close all
-clear all
-clc
-
-% Define parameters
-year_start = 1976;
-year_end = 2015;
-
-
-
-
-
-%% Load summary data
-build_load_filename = horzcat('patent_match_summary_', num2str(year_start), ...
-    '-', num2str(year_end), '.mat');
-load(build_load_filename)
-
-
-%% Print some summaries
-fprintf('Total number of identified patents all years: %d.\n', ...
-    sum(patent_match_summary.nr_patents_yr))
-
-
-%% Make table
-
-% Print to .txt file in Latex format
-printname = 'table_autompat_share.tex';
-
-FID = fopen(printname, 'w');
-
-fprintf(FID,'\\begin{table}\n');
-fprintf(FID,'\\begin{threeparttable}\n');
-fprintf(FID,'\\caption{{\\normalsize Share of automation patents}}\n');
-fprintf(FID,'\\label{tab:word_distribution}\n');
-fprintf(FID,'\\begin{tabular}{lrrrllrrr}\n'); 
-fprintf(FID,'\\toprule \\addlinespace[0.5em]\n');
-fprintf(FID,' & \\textbf{A$^1$} & \\textbf{P} & \\%% & \\phantom{aaa} & & \\textbf{A$^1$} & \\textbf{P} & \\%% \\tabularnewline[0.1cm]\n');
-fprintf(FID,'\\midrule \\addlinespace[0.5em]\n');
-
-addyear = 20;
-
-for t=1:floor(length(patent_match_summary.nr_patents_yr) / 2)
-    ix_year = year_start + t - 1;
-   
-    fprintf(FID,'%d & %d & %d & %3.1f & & %d & %d & %d & %3.1f \\tabularnewline[0.1cm]\n', ix_year, patent_match_summary.nr_distinct_patents_hits(t), patent_match_summary.nr_patents_yr(t), patent_match_summary.nr_distinct_patents_hits(t)/patent_match_summary.nr_patents_yr(t)*100, ix_year + addyear, patent_match_summary.nr_distinct_patents_hits(t + addyear), patent_match_summary.nr_patents_yr(t + addyear), patent_match_summary.nr_distinct_patents_hits(t + addyear)/patent_match_summary.nr_patents_yr(t + addyear)*100);
-end
-
-
-fprintf(FID,'\\bottomrule\n');
-fprintf(FID,'\\end{tabular}\n');
[…]

### 2015-08-19 make_figures/make_table_autompatshare_3column.m

@@ -1,74 +1,0 @@
-close all
-clear all
-clc
-
-% Define parameters
-year_start = 1976;
-year_end = 2015;
-
-
-
-
-
-%% Load summary data
-build_load_filename = horzcat('patent_match_summary_', num2str(year_start), ...
-    '-', num2str(year_end), '.mat');
-load(build_load_filename)
-
-
-%% Print some summaries
-fprintf('Total number of identified patents all years: %d.\n', ...
-    sum(patent_match_summary.nr_patents_yr))
-
-
-%% Make table
-
-% Print to .txt file in Latex format
-printname = 'table_autompat_share.tex';
-
-FID = fopen(printname, 'w');
-
-fprintf(FID,'\\begin{table}\n');
-fprintf(FID,'\\begin{small}\n');
-fprintf(FID,'\\begin{threeparttable}\n');
-fprintf(FID,'\\caption{{\\normalsize Share of automation patents}}\n');
-fprintf(FID,'\\label{tab:word_distribution}\n');
-fprintf(FID,'\\begin{tabular}{lrrrllrrrllrrr}\n'); 
-fprintf(FID,'\\toprule \\addlinespace[0.5em]\n');
-fprintf(FID,' & \\textbf{\\#A$^1$} & \\textbf{\\#P$^1$} & \\textbf{\\%%} & \\phantom{aaa} & & \\textbf{\\#A$^1$} & \\textbf{\\#P$^1$} & \\textbf{\\%%} & \\phantom{aaa} & & \\textbf{\\#A$^1$} & \\textbf{\\#P$^1$} & \\textbf{\\%%}\\tabularnewline[0.1cm]\n');
-fprintf(FID,'\\midrule \\addlinespace[0.5em]\n');
-
-addyear = 13;
-addyear2 = addyear*2;
-
-for t=1:13
-    ix_year = year_start + t - 1;
-   
[…]

### 2015-08-19 make_figures/make_table_overview.m

@@ -1,87 +1,0 @@
-close all
-clear all
-clc
-
-% Define parameters
-year_start = 1976;
-year_end = 2015;
-
-
-
-
-
-%% Load patent match summary data
-build_load_filename = horzcat('patent_match_summary_', num2str(year_start), ...
-    '-', num2str(year_end), '.mat');
-load(build_load_filename)
-
-
-%% Print some summaries
-fprintf('Total number of identified patents all years: %d.\n', ...
-    sum(patent_match_summary.nr_patents_yr))
-
-fprintf('Total number of keyword matches in all years: %d.\n', ...
-    sum(patent_match_summary.total_matches_yr))
-
-
-%% Load data on how many patents are matched to industries
-addpath('../conversion_patent2industry')
-load('share_patents_linked.mat')
-
-
-
-%% Make table
-
-% Print to .txt file in Latex format
-printname = 'table_overview.tex';
-
-FID = fopen(printname, 'w');
-
-fprintf(FID,'\\begin{table}\n');
-fprintf(FID,'\\begin{small}\n');
-fprintf(FID,'\\begin{threeparttable}\n');
-fprintf(FID,'\\caption{{\\normalsize Overview of yearly matched patents}}\n');
-fprintf(FID,'\\label{tab:overview_yr_matchpatents}\n');
-fprintf(FID,'\\begin{tabular}{lrrrrr}\n');
-fprintf(FID,'\\toprule \\addlinespace[0.5em]\n');
-fprintf(FID,' & \\textbf{Automation} & \\textbf{Total} & \\textbf{Share (\\%%)} & & \\textbf{Share matched} \\tabularnewline[0.05cm]\n');
-fprintf(FID,' & \\textbf{patents$^1$} & \\textbf{patents} &  &  & \\textbf{to industries (\\%%)} \\tabularnewline[0.1cm]\n');
-fprintf(FID,'\\cmidrule(l){2-4} \\cmidrule(l){6-6} \\addlinespace[0.5em] \n');
-
-for t=1:length(patent_match_summary.nr_patents_yr)
-    ix_year = year_start + t - 1;
-    
-    if ix_year == 2015
[…]

### 2015-08-19 make_figures/make_table_yearsstats.m

@@ -1,0 +1,66 @@
+function make_table_yearsstats(year_start, year_end)
+
+%% Load summary data
+build_load_filename = horzcat('allyr_patstats_', num2str(year_start), ...
+    '-', num2str(year_end), '.mat');
+load(build_load_filename)
+
+clean_ix = [0; allyr_patstats.ix_new_year(2:end); ...
+    length(allyr_patstats.nr_patents_per_week)];
+
+for t=1:length(year_start:year_end)
+    ix_start = clean_ix(t) + 1;
+    ix_stop = clean_ix(t + 1);
+    
+    nr_patents_per_year(t) = sum( allyr_patstats.nr_patents_per_week(...
+        ix_start : ix_stop) );
+    total_alg1_per_year(t) = sum( allyr_patstats.total_alg1_week(...
+        ix_start : ix_stop) );
+end
+    
+
+
+%% Print to .txt file in Latex format
+printname = 'output/table_yearsstats.tex';
+
+FID = fopen(printname, 'w');
+
+fprintf(FID,'\\begin{table}[!htb]\n');
+fprintf(FID,'\\begin{small}\n');
+fprintf(FID,'\\begin{threeparttable}\n');
+fprintf(FID,'\\caption{{\\normalsize Overview of yearly classified patents}}\n');
+fprintf(FID,'\\label{table:table_yearsstats}\n');
+fprintf(FID,'\\begin{tabular}{lrrrllrrrllrrr}\n'); 
+fprintf(FID,'\\toprule \\addlinespace[0.5em]\n');
+fprintf(FID,' & \\textbf{\\#A} & \\textbf{\\#P} & \\textbf{\\%%} & \\phantom{aaa} & & \\textbf{\\#A} & \\textbf{\\#P} & \\textbf{\\%%} & \\phantom{aaa} & & \\textbf{\\#A} & \\textbf{\\#P} & \\textbf{\\%%}\\tabularnewline[0.1cm]\n');
+fprintf(FID,'\\midrule \\addlinespace[0.5em]\n');
+
+
+%     fprintf(FID, '%d & %d & %d & %3.2f \\tabularnewline\n', ix_year, total_alg1_per_year(t), nr_patents_per_year(t), total_alg1_per_year(t) / nr_patents_per_year(t));
+
+
+
+addyear = 13;
+addyear2 = addyear*2;
+
+for t=1:13
+    ix_year = year_start + t - 1;
+   
[…]

### 2015-08-19 manual_classification/calculate_classerror_overtime.m

@@ -1,0 +1,27 @@
+function classifstat_yrly = calculate_classerror_overtime(manclassData, ...
+    compClass_Yes, year_start, year_end)
+
+for ix_year=year_start:year_end
+    ix_iter = ix_year + 1 - year_start;
+    
+    ix_pos = find(manclassData.indic_year == ix_year);
+    nr_class = length(ix_pos);
+    
+    manclass_Yes_yr = manclassData.manAutomat(ix_pos);
+    compClass_Yes_yr = compClass_Yes(ix_pos);
+    
+    assert( nr_class == length(compClass_Yes_yr) )
+    
+    nr_equal = length( find( manclass_Yes_yr == compClass_Yes_yr ) );
+    nr_wrong = nr_class - nr_equal;
+    
+    accuracy = nr_equal / nr_class;
+
+    % Save in struct
+    classifstat_yrly.nr_class(ix_iter) = nr_class;
+    classifstat_yrly.nr_equal(ix_iter) = nr_equal;
+    classifstat_yrly.nr_wrong(ix_iter) = nr_wrong;
+    classifstat_yrly.nr_manclass_Yes_yr(ix_iter) = sum( manclass_Yes_yr );
+    classifstat_yrly.nr_compClass_Yes_yr(ix_iter) = sum( compClass_Yes_yr );
+    classifstat_yrly.accuracy(ix_iter) = accuracy;
+end

### 2015-08-19 manual_classification/make_contingency_table.m

@@ -46,5 +46,3 @@ fprintf(FID,'\\end{threeparttable}\n');
 fprintf(FID,'\\end{small}\n');
 fprintf(FID,'\\end{table}\n');
 fclose(FID); 
-
-fprintf('Saved: %s.\n', printname)

### 2015-08-19 manual_classification/make_contingency_table_comparison.m

@@ -47,5 +47,3 @@ fprintf(FID,'\\end{threeparttable}\n');
 fprintf(FID,'\\end{small}\n');
 fprintf(FID,'\\end{table}\n');
 fclose(FID); 
-
-fprintf('Saved: %s.\n', printname)

### 2015-08-19 manual_classification/make_table_compare_classalg.m

@@ -102,5 +102,3 @@ fprintf(FID, '\\end{threeparttable}\n');
 fprintf(FID, '\\end{small}\n');
 fprintf(FID, '\\end{table}\n');
 fclose(FID); 
-
-fprintf('Saved: %s.\n', printname)

### 2015-08-19 run_patentsearch.m

@@ -83,6 +83,10 @@ years = year_start:year_end;
 % plot_alg1_over_nrpatents_weekly(year_start, year_end)
 
 
+make_table_yearsstats(year_start, year_end)
+copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\table_yearsstats.tex', ...
+    'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\tables')
+
 
 %% Link patents to industries
 % pat2ind = conversion_patent2industry();
@@ -110,9 +114,11 @@ years = year_start:year_end;
 % Load and prepare the manually classified patents
 manclassData = prepare_manclass('manclass_consolidated_v7.xlsx');
 
-% Get keywords and technology numbers for those patents that were manually
-% classified
-% compile_automclass4codedpats(manclassData, year_start, year_end);
+% Get keywords and technology numbers for manually classified patents
+% automclassData = compile_automclass4codedpats(manclassData, ...
+%     year_start, year_end);
+% save('output/automclassData.mat', 'automclassData'); % save to .mat
+
 
 %%
 % Classify patents based on computerized methods
@@ -131,6 +137,16 @@ make_contingency_table(classifstat)
 
 copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\table_contingency.tex', ...
     'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\tables')
+
+compClass_Yes = computerClass.compAutomat(:, ix_alg);
+classifstat_yrly = calculate_classerror_overtime(manclassData, ...
+    compClass_Yes, year_start, year_end);
+
+
+% plot_classifstat_yrly(classifstat_yrly, year_start, year_end)
+% copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\classifstat_yrly.pdf', ...
+%     'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\figures')
+
 
 
 % Compare all algorithms
@@ -154,7 +170,7 @@ choose_compalg_list = {'Algorithm1', 'automat', 'Bessen-Hunt', ...
 classalg_comparison = comp_evals_algs(choose_compalg_list, ...
     computerClass, manclassData);
 
-plot_bar_fmeasure(classalg_comparison.fmeasure, classalg_comparison.algorithm_name)
[…]

### 2015-08-19 output/table_meancorr_laborm_patentm.tex
Work on industry match

\begin{table}
\begin{small}
\begin{threeparttable}
\caption{{\normalsize Average correlations of labor market outcomes and automation across industries}}
\label{tab:meancorr_laborm_patentm}
\begin{tabular}{lrrrrrrrrrr}
\toprule \addlinespace[0.5em]
 & \rot{Employment} & \rot{Employment share} &  \rot{Capital productivity} & \rot{Output} & \rot{Capital cost} &  \rot{Labor cost} & \rot{Output deflator} & \rot{Production} & \rot{Capital} & \rot{Labor productivity} \tabularnewline[0.05cm]
\midrule \addlinespace[0.5em]
\# Automation patents$^1$ & \textbf{-0.51} & -0.02 & 0.02 & 0.38 & 0.35 & 0.47 & \textbf{0.46} & \textbf{0.51} & \textbf{0.63} & \textbf{0.72}  \tabularnewline[0.0cm]
 & \scriptsize{\scriptsize{(0.44)}} & \scriptsize{\scriptsize{(0.44)}} & \scriptsize{(0.39)} & \scriptsize{(0.60)} & \scriptsize{(0.43)} & \scriptsize{(0.48)} & \scriptsize{(0.23)} & \scriptsize{(0.37)} & \scriptsize{(0.62)} & \scriptsize{(0.63)} \tabularnewline[0.1cm]
Average match per patent & \textbf{-0.57} & 0 & 0.09 & 0.31 & 0.38 & 0.44 & \textbf{0.51} & \textbf{0.53} & 0.54 & \textbf{0.74}  \tabularnewline[0.0cm]
 & \scriptsize{\scriptsize{(0.48)}} & \scriptsize{\scriptsize{(0.49)}} & \scriptsize{(0.38)} & \scriptsize{(0.50)} & \scriptsize{(0.45)} & \scriptsize{(0.52)} & \scriptsize{(0.24)} & \scriptsize{(0.31)} & \scriptsize{(0.62)} & \scriptsize{(0.68)} \tabularnewline[0.1cm]
Share of automation patents & \textbf{-0.61} & -0.01 & 0.13 & 0.37 & 0.43 & \textbf{0.53} & \textbf{0.57} & \textbf{0.63} & 0.61 & \textbf{0.83}  \tabularnewline[0.0cm]
 & \scriptsize{\scriptsize{(0.46)}} & \scriptsize{\scriptsize{(0.50)}} & \scriptsize{(0.41)} & \scriptsize{(0.55)} & \scriptsize{(0.45)} & \scriptsize{(0.50)} & \scriptsize{(0.17)} & \scriptsize{(0.35)} & \scriptsize{(0.67)} & \scriptsize{(0.72)} \tabularnewline[0.1cm]
Automation index$^2$ & \textbf{-0.57} & 0 & 0.09 & 0.31 & 0.38 & 0.44 & \textbf{0.51} & \textbf{0.53} & 0.54 & \textbf{0.74}  \tabularnewline[0.0cm]
 & \scriptsize{\scriptsize{(0.48)}} & \scriptsize{\scriptsize{(0.49)}} & \scriptsize{(0.38)} & \scriptsize{(0.50)} & \scriptsize{(0.45)} & \scriptsize{(0.52)} & \scriptsize{(0.24)} & \scriptsize{(0.31)} & \scriptsize{(0.62)} & \scriptsize{(0.68)} \tabularnewline[0.1cm]
\bottomrule
\end{tabular}
\begin{tablenotes}
\small
\item \textit{Note:} Correlations are calculated from the yearly time series 1987-2014 of the automation indicator and the labor market outcome series. The values are cross-sectional averages across the 26 manufacturing industries. Values in parentheses show standard deviations. Bold values are at least one standard deviation away from 0.
\item $^1$: Automation patents are defined as patents with at least one keyword match.
\item $^2$: Calculated as $log(1 + \text{number of matches per patent})$.
\item \textit{Source:} BLS, USPTO, Google and own calculations.
\end{tablenotes}
\end{threeparttable}
\end{small}
\end{table}

### 2015-08-19 conversion_patent2industry/conversion_patent2industry.m

@@ -2,7 +2,6 @@ function pat2ind = conversion_patent2industry()
 
 fname = 'Naics_co13.csv';
 lnumber = 203074;
-pick_k = 1;
 fullyear_start = 1976;
 fullyear_end = 2014;
 
@@ -20,7 +19,7 @@ fprintf('Finished, time = %dm.\n', round(toc/60))
 [~, ind_code_table] = xlsread('industry_names.xlsx'); % load industry names
 
 [industry_list, linked_pat_ix, industry_sumstats] = match_pat2industry( ...
-    pick_k, fullyear_start, fullyear_end, ind_code_table, conversion_table);
+    fullyear_start, fullyear_end, ind_code_table, conversion_table);
 
 disp('Finished matching patents with industries.')
 

### 2015-08-19 industry_analysis/subplot_patentm_vs_laborm.m

@@ -1,10 +1,5 @@
 function subplot_patentm_vs_laborm(year_start, year_end, ... 
-    manufacturing_ind_data, pat2ind)
-
-
-%% Choose labor market and patent match statistic
-ix_patentmetric  = 3;
-ix_labormvar = 5;
+    manufacturing_ind_data, pat2ind, ix_patentmetric, ix_labormvar)
 
 
 %% Plot settings
@@ -47,16 +42,15 @@ for ix_industry=1:size(pat2ind.industry_sumstats, 1)
     industry_name = pat2ind.industry_sumstats{ix_industry, 2, 1};
     sumstats = extract_sumstats(pat2ind.industry_sumstats, ix_industry);
     industry_nr_pat = sumstats(:, 1);
-    industry_nr_matches = sumstats(:, 2);
-    industry_pat_1match = sumstats(:, 3);
-    industry_automix = sumstats(:, 4);
-    industry_avg_matches = industry_nr_matches ./ industry_nr_pat;
+    industry_nr_alg1 = sumstats(:, 2);
+    industry_nr_pat1m = sumstats(:, 3);
 
-    % Share of patents classified as automation patents (> 1 keyword match)
-    industry_pat1match_share = industry_pat_1match ./ industry_nr_pat;
+    % Share of patents classified as automation patents
+    industry_nr_alg1_share = industry_nr_alg1 ./ industry_nr_pat;
+    industry_nr_pat1m = industry_nr_pat1m ./ industry_nr_pat;
     
-    patent_metrics = [industry_pat_1match, industry_avg_matches, ...
-            industry_pat1match_share, industry_automix];
+    patent_metrics = [industry_nr_alg1, industry_nr_pat1m, ...
+        industry_nr_alg1_share, industry_nr_pat1m];
     patent_metric_pick = patent_metrics(:, ix_patentmetric);
 
     

### 2015-08-19 manual_classification/plot_classifstat_yrly.m

@@ -64,7 +64,7 @@ yLimits = get(gca,'YLim');
 xlim([year_start, year_end])
 ygrid_lines = [yLimits(1):5:yLimits(end)];
 ygrid_lines(find(ygrid_lines==yLimits(1))) = []; % remove bottom grid line
-ygrid_lines(find(ygrid_lines==yLimits(2))) = []; % remove grid line at the top
+% ygrid_lines(find(ygrid_lines==yLimits(2))) = []; % remove grid line at the top
 handle_ygrid = gridxy([], ygrid_lines, 'Color', my_gray , 'linewidth', grid_linewidth);
 
 subplot(3,1,2)
@@ -91,7 +91,7 @@ set(gca, 'TickDir', 'out')
 yLimits = get(gca,'YLim');
 ygrid_lines = [yLimits(1):0.2:yLimits(end)];
 ygrid_lines(find(ygrid_lines==yLimits(1))) = []; % remove bottom grid line
-ygrid_lines(find(ygrid_lines==yLimits(2))) = []; % remove grid line at the top
+% ygrid_lines(find(ygrid_lines==yLimits(2))) = []; % remove grid line at the top
 handle_ygrid = gridxy([], ygrid_lines, 'Color', my_gray , 'linewidth', grid_linewidth);
 
 subplot(3,1,3)
@@ -114,7 +114,7 @@ xlim([year_start, year_end])
 yLimits = get(gca,'YLim');
 ygrid_lines = [yLimits(1):0.2:yLimits(end)];
 ygrid_lines(find(ygrid_lines==yLimits(1))) = []; % remove bottom grid line
-ygrid_lines(find(ygrid_lines==yLimits(2))) = []; % remove grid line at the top
+% ygrid_lines(find(ygrid_lines==yLimits(2))) = []; % remove grid line at the top
 handle_ygrid = gridxy([], ygrid_lines, 'Color', my_gray , 'linewidth', grid_linewidth);
 
 

### 2015-08-19 run_patentsearch.m

@@ -65,7 +65,7 @@ years = year_start:year_end;
 
 
 %% Make some visualizations 
-% dim_subplot = [6, 5];
+dim_subplot = [6, 5];
 
 % plot_matches_overtime(year_start, year_end, dim_subplot)
 % plot_matches_over_nrpatents_weekly(year_start, year_end, dim_subplot)
@@ -78,14 +78,14 @@ years = year_start:year_end;
 % pick_k = 1; % 1: "automat"
 % plot_pat1m_over_nrpatents_weekly(year_start, year_end, pick_k)
 % plot_pat1m_overtime(year_start, year_end, pick_k)
-
+% 
 % plot_alg1_overtime(year_start, year_end)
 % plot_alg1_over_nrpatents_weekly(year_start, year_end)
 
 
-make_table_yearsstats(year_start, year_end)
-copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\table_yearsstats.tex', ...
-    'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\tables')
+% make_table_yearsstats(year_start, year_end)
+% copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\table_yearsstats.tex', ...
+%     'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\tables')
 
 
 %% Link patents to industries
@@ -93,16 +93,28 @@ copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automa
 % save('output/pat2ind', 'pat2ind')
 
 
+
 %% Industry-level analysis
-% load('pat2ind')
+load('pat2ind')
 
-% manufacturing_ind_data = analyze_industries(1976, ...
-%     2014, pat2ind);
+manufacturing_ind_data = analyze_industries(1976, 2014, pat2ind);
 
-% make_table_meancorr_laborm_patentm(manufacturing_ind_data)
+make_table_meancorr_laborm_patentm(manufacturing_ind_data)
+copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\table_meancorr_laborm_patentm.tex', ...
+    'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\tables')
 
-% subplot_patentm_vs_laborm(1976, 2014, ... 
-%     manufacturing_ind_data, pat2ind)
+
+ix_patentmetric = 3;
[…]

### 2015-08-20 make_figures/make_table_yearsstats.m
Add to search dict + draw patents

@@ -30,7 +30,7 @@ fprintf(FID,'\\begin{small}\n');
 fprintf(FID,'\\begin{threeparttable}\n');
 fprintf(FID,'\\caption{{\\normalsize Overview of yearly classified patents}}\n');
 fprintf(FID,'\\label{table:table_yearsstats}\n');
-fprintf(FID,'\\begin{tabular}{lrrrllrrrllrrr}\n'); 
+fprintf(FID,'\\begin{tabular}{rrrrrrrrrrrrrr}\n'); 
 fprintf(FID,'\\toprule \\addlinespace[0.5em]\n');
 fprintf(FID,' & \\textbf{\\#A} & \\textbf{\\#P} & \\textbf{\\%%} & \\phantom{aaa} & & \\textbf{\\#A} & \\textbf{\\#P} & \\textbf{\\%%} & \\phantom{aaa} & & \\textbf{\\#A} & \\textbf{\\#P} & \\textbf{\\%%}\\tabularnewline[0.1cm]\n');
 fprintf(FID,'\\midrule \\addlinespace[0.5em]\n');

### 2015-08-20 run_patentsearch.m

@@ -83,9 +83,9 @@ dim_subplot = [6, 5];
 % plot_alg1_over_nrpatents_weekly(year_start, year_end)
 
 
-% make_table_yearsstats(year_start, year_end)
-% copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\table_yearsstats.tex', ...
-%     'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\tables')
+make_table_yearsstats(year_start, year_end)
+copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\table_yearsstats.tex', ...
+    'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\tables')
 
 
 %% Link patents to industries
@@ -95,24 +95,24 @@ dim_subplot = [6, 5];
 
 
 %% Industry-level analysis
-load('pat2ind')
-
-manufacturing_ind_data = analyze_industries(1976, 2014, pat2ind);
-
-make_table_meancorr_laborm_patentm(manufacturing_ind_data)
-copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\table_meancorr_laborm_patentm.tex', ...
-    'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\tables')
-
-
-ix_patentmetric = 3;
-ix_labormvar = 5;
-subplot_patentm_vs_laborm(1976, 2014, manufacturing_ind_data, pat2ind, ...
-    ix_patentmetric, ix_labormvar)
-
-
+% load('pat2ind')
+% 
+% manufacturing_ind_data = analyze_industries(1976, 2014, pat2ind);
+% 
+% make_table_meancorr_laborm_patentm(manufacturing_ind_data)
+% % copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\table_meancorr_laborm_patentm.tex', ...
+% %     'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\tables')
+% 
+% 
+% ix_patentmetric = 3;
+% ix_labormvar = 5;
+% subplot_patentm_vs_laborm(1976, 2014, manufacturing_ind_data, pat2ind, ...
+%     ix_patentmetric, ix_labormvar)
 
 
-break
+
+
+% break
 
 
 
@@ -125,6 +125,7 @@ break
 
[…]

### 2015-08-20 specs/define_dictionary.m

@@ -6,4 +6,5 @@ find_dictionary = {'automat', 'robot', ...
     'self-generat', 'detect', 'independent', 'motor', 'engine', ...
     'communicat', 'semi-conductor', 'semiconductor', ...
     'chip', 'bus', 'circuit', 'circuitry', 'antigen', 'antigenic', ...
-    'chromatography', 'manual', 'mechaniz', 'system and method', 'machine'};
+    'chromatography', 'manual', 'mechaniz', 'system and method', ...
+    'machine', 'apparatus'};

### 2015-08-20 manual_coding_guidelines/manual_coding_guidelines.tex
Add superscript 1 to fmeasure in table + change name from handbook to guidelines
edit man. coding guideliens

--- 2015-08-17 manual_coding_handbook/manual_coding_handbook.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title {\textbf{Manual Coding Handbook\\[0.15cm]
+\title {\textbf{Manual Coding Guidelines\\[0.15cm]
 for Automation Patents}}
@@
 If you cannot find it (this happens rarely) or if the patent grant text looks incomplete (also rare), please try at the USPTO search interface.
+	\item An easy way to reach a patent is to adjust the following url (leave US and replace 6121900 by the patent number):\\[0.1cm]
+ \href{https://www.google.de/patents/US6121900}{\texttt{\textcolor{myred}{https://www.google.de/patents/US6121900}}}\\[0.1cm]
 	\item The right patent might not be the first one in the list.

### 2015-08-23 output/table_compare_classalg.tex
Add LICENSE

@@
  & \textbf{Algorithm1} & \textbf{automat} & \textbf{Bessen-Hunt} & \textbf{Always "No"} & \textbf{Always "Yes"}  \tabularnewline 
-Accuracy & 0.78 & 0.79 & 0.78 & 0.76 & 0.24 & & & &  \tabularnewline 
-Precision & 0.53 & 0.56 & 0.57 & NaN & 0.24 & & & &  \tabularnewline 
-Recall & 0.69 & 0.56 & 0.29 & 0.00 & 1.00 & & & &  \tabularnewline 
+Accuracy & 0.79 & 0.79 & 0.78 & 0.76 & 0.24 & & & &  \tabularnewline 
+Precision & 0.55 & 0.56 & 0.57 & NaN & 0.24 & & & &  \tabularnewline 
+Recall & 0.66 & 0.56 & 0.29 & 0.00 & 1.00 & & & &  \tabularnewline 
 F-measure & 0.60 & 0.56 & 0.38 & NaN & 0.39 & & & &  \tabularnewline 
-AUC & 0.75 & 0.71 & 0.61 & 0.50 & 0.50 & & & &  \tabularnewline 
-MCC & 0.45 & 0.42 & 0.28 & NaN & NaN & & & &  \tabularnewline 
-Number "Yes" & 137 & 106 & 53 & 0 & 438 & & & &  \tabularnewline 
+AUC & 0.74 & 0.71 & 0.61 & 0.50 & 0.50 & & & &  \tabularnewline 
+MCC & 0.46 & 0.42 & 0.28 & NaN & NaN & & & &  \tabularnewline 
+Number "Yes" & 125 & 106 & 53 & 0 & 438 & & & &  \tabularnewline 
 \bottomrule 

### 2015-08-23 output/table_meancorr_laborm_patentm.tex
Add LICENSE

@@
 \midrule \addlinespace[0.5em]
-\# Automation patents$^1$ & \textbf{-0.51} & -0.02 & 0.02 & 0.38 & 0.35 & 0.47 & \textbf{0.46} & \textbf{0.51} & \textbf{0.63} & \textbf{0.72}  \tabularnewline[0.0cm]
- & \scriptsize{\scriptsize{(0.44)}} & \scriptsize{\scriptsize{(0.44)}} & \scriptsize{(0.39)} & \scriptsize{(0.60)} & \scriptsize{(0.43)} & \scriptsize{(0.48)} & \scriptsize{(0.23)} & \scriptsize{(0.37)} & \scriptsize{(0.62)} & \scriptsize{(0.63)} \tabularnewline[0.1cm]
-Average match per patent & \textbf{-0.57} & 0 & 0.09 & 0.31 & 0.38 & 0.44 & \textbf{0.51} & \textbf{0.53} & 0.54 & \textbf{0.74}  \tabularnewline[0.0cm]
- & \scriptsize{\scriptsize{(0.48)}} & \scriptsize{\scriptsize{(0.49)}} & \scriptsize{(0.38)} & \scriptsize{(0.50)} & \scriptsize{(0.45)} & \scriptsize{(0.52)} & \scriptsize{(0.24)} & \scriptsize{(0.31)} & \scriptsize{(0.62)} & \scriptsize{(0.68)} \tabularnewline[0.1cm]
-Share of automation patents & \textbf{-0.61} & -0.01 & 0.13 & 0.37 & 0.43 & \textbf{0.53} & \textbf{0.57} & \textbf{0.63} & 0.61 & \textbf{0.83}  \tabularnewline[0.0cm]
- & \scriptsize{\scriptsize{(0.46)}} & \scriptsize{\scriptsize{(0.50)}} & \scriptsize{(0.41)} & \scriptsize{(0.55)} & \scriptsize{(0.45)} & \scriptsize{(0.50)} & \scriptsize{(0.17)} & \scriptsize{(0.35)} & \scriptsize{(0.67)} & \scriptsize{(0.72)} \tabularnewline[0.1cm]
-Automation index$^2$ & \textbf{-0.57} & 0 & 0.09 & 0.31 & 0.38 & 0.44 & \textbf{0.51} & \textbf{0.53} & 0.54 & \textbf{0.74}  \tabularnewline[0.0cm]
- & \scriptsize{\scriptsize{(0.48)}} & \scriptsize{\scriptsize{(0.49)}} & \scriptsize{(0.38)} & \scriptsize{(0.50)} & \scriptsize{(0.45)} & \scriptsize{(0.52)} & \scriptsize{(0.24)} & \scriptsize{(0.31)} & \scriptsize{(0.62)} & \scriptsize{(0.68)} \tabularnewline[0.1cm]
+\# Automation patents$^1$ & \textbf{-0.56} & -0.02 & 0.04 & 0.36 & 0.35 & 0.46 & \textbf{0.49} & \textbf{0.52} & 0.6 & \textbf{0.76}  \tabularnewline[0.0cm]
+ & \scriptsize{\scriptsize{(0.46)}} & \scriptsize{\scriptsize{(0.46)}} & \scriptsize{(0.41)} & \scriptsize{(0.59)} & \scriptsize{(0.44)} & \scriptsize{(0.50)} & \scriptsize{(0.23)} & \scriptsize{(0.38)} & \scriptsize{(0.62)} & \scriptsize{(0.65)} \tabularnewline[0.1cm]
+Average match per patent & \textbf{-0.59} & 0 & 0.1 & 0.33 & 0.4 & 0.46 & \textbf{0.52} & \textbf{0.55} & 0.56 & \textbf{0.77}  \tabularnewline[0.0cm]
+ & \scriptsize{\scriptsize{(0.48)}} & \scriptsize{\scriptsize{(0.50)}} & \scriptsize{(0.38)} & \scriptsize{(0.51)} & \scriptsize{(0.44)} & \scriptsize{(0.52)} & \scriptsize{(0.21)} & \scriptsize{(0.32)} & \scriptsize{(0.63)} & \scriptsize{(0.69)} \tabularnewline[0.1cm]
+Share of automation patents & \textbf{-0.67} & -0.02 & 0.14 & 0.34 & 0.4 & 0.48 & \textbf{0.59} & \textbf{0.6} & 0.55 & \textbf{0.87}  \tabularnewline[0.0cm]
+ & \scriptsize{\scriptsize{(0.49)}} & \scriptsize{\scriptsize{(0.52)}} & \scriptsize{(0.44)} & \scriptsize{(0.53)} & \scriptsize{(0.45)} & \scriptsize{(0.53)} & \scriptsize{(0.17)} & \scriptsize{(0.37)} & \scriptsize{(0.66)} & \scriptsize{(0.74)} \tabularnewline[0.1cm]
+Automation index$^2$ & \textbf{-0.59} & 0 & 0.1 & 0.33 & 0.4 & 0.46 & \textbf{0.52} & \textbf{0.55} & 0.56 & \textbf{0.77}  \tabularnewline[0.0cm]
+ & \scriptsize{\scriptsize{(0.48)}} & \scriptsize{\scriptsize{(0.50)}} & \scriptsize{(0.38)} & \scriptsize{(0.51)} & \scriptsize{(0.44)} & \scriptsize{(0.52)} & \scriptsize{(0.21)} & \scriptsize{(0.32)} & \scriptsize{(0.63)} & \scriptsize{(0.69)} \tabularnewline[0.1cm]
 \bottomrule

### 2015-08-23 run_patentsearch.m

@@ -53,10 +53,8 @@ years = year_start:year_end;
 
 
 %% Check matches for plausibility
-check_cleanedmatches_plausability(year_start, year_end)
+% check_cleanedmatches_plausability(year_start, year_end)
 
-
-break
 
 %% Transfer matches to CSV (for use in Stata)
 % transfer_cleaned_matches2csv(year_start, year_end)
@@ -67,7 +65,7 @@ break
 
 
 %% Make some visualizations 
-dim_subplot = [6, 5];
+% dim_subplot = [7, 5];
 
 % plot_matches_overtime(year_start, year_end, dim_subplot)
 % plot_matches_over_nrpatents_weekly(year_start, year_end, dim_subplot)
@@ -80,44 +78,43 @@ dim_subplot = [6, 5];
 % pick_k = 1; % 1: "automat"
 % plot_pat1m_over_nrpatents_weekly(year_start, year_end, pick_k)
 % plot_pat1m_overtime(year_start, year_end, pick_k)
-% 
+
 % plot_alg1_overtime(year_start, year_end)
+% copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\alg1_weekly_1976-2015.pdf', ...
+%     'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\figures')
+% 
 % plot_alg1_over_nrpatents_weekly(year_start, year_end)
-
-
-make_table_yearsstats(year_start, year_end)
-copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\table_yearsstats.tex', ...
-    'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\tables')
+% copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\alg1_over_nrpatents_weekly_1976-2015.pdf', ...
+%     'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\figures')
+% 
+% make_table_yearsstats(year_start, year_end)
+% copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\table_yearsstats.tex', ...
+%     'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\tables')
 
 
 %% Link patents to industries
-% pat2ind = conversion_patent2industry();
[…]

### 2015-08-24 output/table_compare_classalg.tex
Adapt positions of labels on plot showing yearly classifications

@@
  & \textbf{Algorithm1} & \textbf{automat} & \textbf{Bessen-Hunt} & \textbf{Always "No"} & \textbf{Always "Yes"}  \tabularnewline 
-Accuracy & 0.79 & 0.79 & 0.78 & 0.76 & 0.24 & & & &  \tabularnewline 
-Precision & 0.55 & 0.56 & 0.57 & NaN & 0.24 & & & &  \tabularnewline 
-Recall & 0.66 & 0.56 & 0.29 & 0.00 & 1.00 & & & &  \tabularnewline 
-F-measure & 0.60 & 0.56 & 0.38 & NaN & 0.39 & & & &  \tabularnewline 
-AUC & 0.74 & 0.71 & 0.61 & 0.50 & 0.50 & & & &  \tabularnewline 
-MCC & 0.46 & 0.42 & 0.28 & NaN & NaN & & & &  \tabularnewline 
-Number "Yes" & 125 & 106 & 53 & 0 & 438 & & & &  \tabularnewline 
+Accuracy & 0.78 & 0.78 & 0.77 & 0.73 & 0.27 & & & &  \tabularnewline 
+Precision & 0.57 & 0.58 & 0.62 & NaN & 0.27 & & & &  \tabularnewline 
+Recall & 0.68 & 0.57 & 0.32 & 0.00 & 1.00 & & & &  \tabularnewline 
+F-measure & 0.62 & 0.57 & 0.42 & NaN & 0.42 & & & &  \tabularnewline 
+AUC & 0.75 & 0.71 & 0.63 & 0.50 & 0.50 & & & &  \tabularnewline 
+MCC & 0.47 & 0.42 & 0.32 & NaN & NaN & & & &  \tabularnewline 
+Number "Yes" & 176 & 147 & 77 & 0 & 560 & & & &  \tabularnewline 
 \bottomrule 

### 2015-08-24 manual_classification/plot_classifstat_yrly.m

@@ -131,53 +131,46 @@ set(figureHandle, 'PaperPositionMode', 'Auto', 'PaperUnits', ...
 
 % Add annotations
 % -----------------------------------------------------------------------
-annotation(figureHandle,'textarrow',[0.730068997791874 0.737704918032789],...
-    [0.909060275272933 0.890988372093023],'TextEdgeColor','none',...
+annotation(figureHandle,'textarrow',[0.564408946023113 0.57377049180328],...
+    [0.933769577598514 0.917151162790698],'TextEdgeColor','none',...
     'HorizontalAlignment','left',...
     'String','Total',...
     'HeadStyle','none',...
     'FontSize', 10, ...
     'Color',color3_pick);
 
-annotation(figureHandle,'textarrow',[0.303500836820429 0.296807592752373],...
-    [0.79078191741818 0.768895348837209],'TextEdgeColor','none',...
+
+annotation(figureHandle,'textarrow',[0.308677713438203 0.301984469370147],...
+    [0.802409824394924 0.780523255813953],'TextEdgeColor','none',...
     'HorizontalAlignment','left',...
     'String','Manual "Yes"',...
     'HeadStyle','none',...
     'Color',color1_pick);
 
 
-annotation(figureHandle,'textarrow',[0.574614518380461 0.550474547023296],...
-    [0.782885619364074 0.75],'TextEdgeColor','none',...
+annotation(figureHandle,'textarrow',[0.556495450218254 0.540120793787749],...
+    [0.8192228286664 0.809593023255814],'TextEdgeColor','none',...
     'HorizontalAlignment','left',...
     'String','Computerized "Yes"',...
     'HeadStyle','none',...
     'Color',color2_pick);
 
 
-annotation(figureHandle,'textarrow',[0.309210424448302 0.297670405522002],...
-    [0.542757475083063 0.497093023255814],'TextEdgeColor','none',...
+annotation(figureHandle,'textarrow',[0.317515099223469 0.303710094909405],...
+    [0.545058139534884 0.489825581395349],'TextEdgeColor','none',...
     'HorizontalAlignment','left',...
     'String','Manual',...
     'HeadStyle','none',...
     'FontSize', 10, ...
     'Color', color1_pick);
 
-annotation(figureHandle, 'textarrow', [0.499956334546595 0.511647972389991],...
-    [0.59539155196963 0.575581395348837],'TextEdgeColor','none',...
[…]

### 2015-08-28 run_patentsearch.m
Delete description of baseline algorithm 1 in the Note: underneath the table comparing algorithms. We make a separate box describing this algorithm, so that isn't necessary.

@@ -65,7 +65,7 @@ years = year_start:year_end;
 
 
 %% Make some visualizations 
-% dim_subplot = [7, 5];
+dim_subplot = [7, 5];
 
 % plot_matches_overtime(year_start, year_end, dim_subplot)
 % plot_matches_over_nrpatents_weekly(year_start, year_end, dim_subplot)
@@ -113,7 +113,7 @@ fyr_end = 2014;
 
 
 %% Industry-level analysis
-load('pat2ind')
+% load('pat2ind')
 
 % subplot_industries_alg1(fyr_start, fyr_end, pat2ind.industry_sumstats, ...
 %     pat2ind.ind_corresp)
@@ -122,34 +122,31 @@ load('pat2ind')
 %     pat2ind.ind_corresp)
 
 
-idata = extract_idata(fyr_start, fyr_end, pat2ind.ind_corresp(:, 1));
-check_idata(idata)
+% idata = extract_idata(fyr_start, fyr_end, pat2ind.ind_corresp(:, 1));
+% check_idata(idata)
+% 
+% 
+% industry_sumstats = pat2ind.industry_sumstats;
+% laborm_series = idata.employment;
+% industry_list = pat2ind.ind_corresp(:, 2);
+% igroups = pat2ind.ind_corresp(:, 3);
+% make_bivariate_plot(fyr_start, fyr_end, industry_sumstats, ...
+%     laborm_series, industry_list, igroups)
+% copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\bivariate_autompat_vs_laborm.pdf', ...
+%     'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\figures')
+% 
+% 
+% make_table_meancorr_laborm_patentm(manufacturing_ind_data)
+% copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\table_meancorr_laborm_patentm.tex', ...
+%     'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\tables')
+% 
+% 
+% ix_patentmetric = 3;
+% ix_labormvar = 5;
+% subplot_patentm_vs_laborm(1976, 2014, manufacturing_ind_data, pat2ind, ...
+%     ix_patentmetric, ix_labormvar)
 
 
-industry_sumstats = pat2ind.industry_sumstats;
[…]

### 2015-08-28 manual_classification/make_contingency_table.m
Work on the two table next to each other

@@ -14,6 +14,7 @@ fprintf(FID, '\\parbox[t]{0mm}{\\multirow{2}{*}{\\rotatebox[origin=c]{90}{Manual
 fprintf(FID, ' & Yes & \\multicolumn{1}{|l}{%d} & \\multicolumn{1}{l|}{%d} & %d & \\tabularnewline\n', classifstat.false_negative, classifstat.true_positive, classifstat.false_negative + classifstat.true_positive);
 fprintf(FID, ' \\cline{3-5} \n');
 fprintf(FID, ' &  & \\multicolumn{1}{|l}{%d} & \\multicolumn{1}{l|}{%d} & %d & \\tabularnewline\n', classifstat.true_negative + classifstat.false_negative, classifstat.false_positive + classifstat.true_positive, classifstat.nr_codpt);
-fprintf(FID, '&  &  & & & \\tabularnewline[-0.1cm]\n');
+fprintf(FID, '  &  &  &  &  & \\tabularnewline\n');
+fprintf(FID, ' & \\multicolumn{5}{l}{\\scriptsize{``No": not automation patent}} &  &  &  & \\tabularnewline\n');
 fprintf(FID,'\\end{tabular}\n');
 fclose(FID); 

### 2015-08-28 manual_classification/make_table_evalstats.m

@@ -5,13 +5,12 @@ printname = 'output/table_evalstats.tex';
 
 FID = fopen(printname, 'w');
 
-fprintf(FID,'\\begin{tabular}{lrllll}\n');
-fprintf(FID, '\\rule{0pt}{12pt} & Accuracy & \\multicolumn{3}{r}{$\\frac{%d + %d}{%d} = %3.2f$} &  \\tabularnewline\n', classifstat.true_negative, classifstat.true_positive, classifstat.nr_codpt, classifstat.accuracy);
-fprintf(FID, '\\rule{0pt}{12pt}& Precision & \\multicolumn{3}{r}{$\\frac{%d}{%d} = %3.2f$} & \\tabularnewline\n', classifstat.true_positive, classifstat.false_positive + classifstat.true_positive, classifstat.precision);
-fprintf(FID, '\\rule{0pt}{12pt}& Recall & \\multicolumn{3}{r}{$\\frac{%d}{%d} = %3.2f$} &  \\tabularnewline\n', classifstat.true_positive, classifstat.false_negative + classifstat.true_positive, classifstat.recall);
-% Only print the beta once
-fprintf(FID, '\\rule{0pt}{12pt}& $F_1^1$ & \\multicolumn{3}{r}{%3.2f} & \\tabularnewline\n', classifstat.fmeasure);
-fprintf(FID, '\\rule{0pt}{12pt}& AUC$^2$ & \\multicolumn{3}{r}{%3.2f} & \\tabularnewline\n', classifstat.auc);
-fprintf(FID, '\\rule{0pt}{12pt}& MCC$^3$ & \\multicolumn{3}{r}{%3.2f} & \\tabularnewline\n', classifstat.matthewscorrcoeff);
+fprintf(FID,'\\begin{tabular}{rl}\n');
+fprintf(FID, '\\rule{0pt}{12pt} Accuracy & $= \\frac{%d + %d}{%d} = %3.2f$  \\tabularnewline\n', classifstat.true_negative, classifstat.true_positive, classifstat.nr_codpt, classifstat.accuracy);
+fprintf(FID, '\\rule{0pt}{12pt} Precision & $= \\frac{%d}{%d} = %3.2f$ \\tabularnewline\n', classifstat.true_positive, classifstat.false_positive + classifstat.true_positive, classifstat.precision);
[…]

### 2015-08-28 manual_classification/make_table_evalstats.m
Bug: too many &

@@ -11,6 +11,6 @@ fprintf(FID, '\\rule{0pt}{12pt} Precision & $= \\frac{%d}{%d} = %3.2f$ \\tabular
 fprintf(FID, '\\rule{0pt}{12pt} Recall & $= \\frac{%d}{%d} = %3.2f$  \\tabularnewline\n', classifstat.true_positive, classifstat.false_negative + classifstat.true_positive, classifstat.recall);
 fprintf(FID, '\\rule{0pt}{12pt} $F_1$ measure &= %3.2f \\tabularnewline\n', classifstat.fmeasure);
 fprintf(FID, '\\rule{0pt}{12pt} AUROC &= %3.2f \\tabularnewline\n', classifstat.auc);
-fprintf(FID, '\\rule{0pt}{12pt} Matthew''s Corr. Coeff.} & $= %3.2f$ \\tabularnewline\n', classifstat.matthewscorrcoeff);
+fprintf(FID, '\\rule{0pt}{12pt} Matthew''s Corr. Coeff. & $= %3.2f$ \\tabularnewline\n', classifstat.matthewscorrcoeff);
 fprintf(FID,'\\end{tabular}\n');
 fclose(FID); 

### 2015-09-02 industry_analysis/make_bivariate_plot.m
..

@@ -83,7 +83,7 @@ marker_size = 5;
 line_width = 1.5;
 font_size = 16;
 
-marker_list = {'s', 'o', 'd', '^', '>', 'x'};
+marker_list = {'s', 'o', 'd', '^', '>', 'v'};
 
 figureHandle = figure;
 
@@ -132,9 +132,9 @@ for ix_industry = 1:size(laborm_series, 2)
     hLegendEntry = get(hAnnotation', 'LegendInformation');
     set(hLegendEntry, 'IconDisplayStyle', 'off')
     
-    ylabel('Share of employees in manufacturing sector employed in industry', ...
+    ylabel('Industry share of manufacturing sector employment', ...
         'FontSize', font_size)
-    xlabel('Share of automation patents', 'FontSize', font_size)
+    xlabel('Automation patent share', 'FontSize', font_size)
     xlim([0, 1])
 end
 hold off
@@ -152,7 +152,7 @@ legend boxoff
 
 
 % Change position and size
-set(gcf, 'Position', [100 200 1200 800]) % in vector: left bottom width height
+set(gcf, 'Position', [100 200 1200 700]) % in vector: left bottom width height
 set(figureHandle, 'Units', 'Inches');
 pos = get(figureHandle, 'Position');
 set(figureHandle, 'PaperPositionMode', 'Auto', 'PaperUnits', ...

### 2015-09-02 manual_classification/make_table_evalstats.m

@@ -9,8 +9,8 @@ fprintf(FID,'\\begin{tabular}{rl}\n');
 fprintf(FID, '\\rule{0pt}{12pt} Accuracy & $= \\frac{%d + %d}{%d} = %3.2f$  \\tabularnewline\n', classifstat.true_negative, classifstat.true_positive, classifstat.nr_codpt, classifstat.accuracy);
 fprintf(FID, '\\rule{0pt}{12pt} Precision & $= \\frac{%d}{%d} = %3.2f$ \\tabularnewline\n', classifstat.true_positive, classifstat.false_positive + classifstat.true_positive, classifstat.precision);
 fprintf(FID, '\\rule{0pt}{12pt} Recall & $= \\frac{%d}{%d} = %3.2f$  \\tabularnewline\n', classifstat.true_positive, classifstat.false_negative + classifstat.true_positive, classifstat.recall);
-fprintf(FID, '\\rule{0pt}{12pt} $F_1$ measure &= %3.2f \\tabularnewline\n', classifstat.fmeasure);
-fprintf(FID, '\\rule{0pt}{12pt} AUROC &= %3.2f \\tabularnewline\n', classifstat.auc);
+fprintf(FID, '\\rule{0pt}{12pt} $F_1$ measure & $= %3.2f$ \\tabularnewline\n', classifstat.fmeasure);
+fprintf(FID, '\\rule{0pt}{12pt} AUROC &$= %3.2f$ \\tabularnewline\n', classifstat.auc);
 fprintf(FID, '\\rule{0pt}{12pt} Matthew''s Corr. Coeff. & $= %3.2f$ \\tabularnewline\n', classifstat.matthewscorrcoeff);
 fprintf(FID,'\\end{tabular}\n');
 fclose(FID); 

### 2015-09-02 manual_classification/plot_classifstat_yrly.m

@@ -52,7 +52,7 @@ box off
 % legend('Total', 'Manual "Yes"', ...
 %     'Computerized "Yes"', 'Location', 'North')
 % legend('boxoff')
-titleHandle = title('Number of manually classified patents', 'FontWeight', 'bold');
+titleHandle = title('(a) Number of manually classified patents', 'FontWeight', 'bold');
 
 set(titleHandle, 'horizontalAlignment', 'left')
 set(titleHandle, 'units', 'normalized')
@@ -78,7 +78,7 @@ box off
 %     'computerized', 'Location', 'North')
 % legend('boxoff')
 ylim([0, 1])
-titleHandle = title('Share classified as automation patents', 'FontWeight', 'bold');
+titleHandle = title('(b) Share classified as automation patents', 'FontWeight', 'bold');
 
 xlim([year_start, year_end])
 set(titleHandle, 'horizontalAlignment', 'left')
@@ -100,7 +100,7 @@ subplot(3,1,3)
 % hold on
 plot(plottime, classifstat_yrly.accuracy, 'Color', color4_pick, ...
     'Linewidth', lwidth)
-titleHandle = title('Accuracy', 'FontWeight', 'bold');
+titleHandle = title('(c) Accuracy', 'FontWeight', 'bold');
 
 set(titleHandle, 'horizontalAlignment', 'left')
 set(titleHandle, 'units', 'normalized')

### 2015-09-02 run_patentsearch.m

@@ -113,39 +113,43 @@ fyr_end = 2014;
 
 
 %% Industry-level analysis
-% load('pat2ind')
+load('pat2ind')
 
-% subplot_industries_alg1(fyr_start, fyr_end, pat2ind.industry_sumstats, ...
-%     pat2ind.ind_corresp)
+subplot_industries_alg1(fyr_start, fyr_end, pat2ind.industry_sumstats, ...
+    pat2ind.ind_corresp)
+copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\subplot_industries_alg1.pdf', ...
+    'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\figures')
 
-% subplot_industries_mean_alg1(fyr_start, fyr_end, pat2ind.industry_sumstats, ...
-%     pat2ind.ind_corresp)
+subplot_industries_mean_alg1(fyr_start, fyr_end, pat2ind.industry_sumstats, ...
+    pat2ind.ind_corresp)
+copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\subplot_industries_mean_alg1.pdf', ...
+    'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\figures')
+
+idata = extract_idata(fyr_start, fyr_end, pat2ind.ind_corresp(:, 1));
+check_idata(idata)
 
 
-% idata = extract_idata(fyr_start, fyr_end, pat2ind.ind_corresp(:, 1));
-% check_idata(idata)
-% 
-% 
-% industry_sumstats = pat2ind.industry_sumstats;
-% laborm_series = idata.employment;
-% industry_list = pat2ind.ind_corresp(:, 2);
-% igroups = pat2ind.ind_corresp(:, 3);
-% make_bivariate_plot(fyr_start, fyr_end, industry_sumstats, ...
-%     laborm_series, industry_list, igroups)
-% copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\bivariate_autompat_vs_laborm.pdf', ...
-%     'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\figures')
-% 
-% 
+industry_sumstats = pat2ind.industry_sumstats;
+laborm_series = idata.employment;
+industry_list = pat2ind.ind_corresp(:, 2);
[…]

### 2015-09-02 manual_coding_guidelines/manual_coding_guidelines.tex
Update manual coding guidelines + code all subclasses for patents that we haven't done this for yet
I also described the column 'Highly uncertain' in the manual coding guidelines. I also included a slide with some empirical frequencies/probabilities such that coders get idea of what to expect

@@
 	\item We randomly pick an equal number of patents from all years.
-	\item We assign each auditor patents. 50\% of patents are assigned to multiple auditors.
+	\item Every patent is reviewed by an additional auditor.
 	\item The list of patents is given to the auditor in random (not chronological) order.
+	\item We will not share your classifications with anybody, but instead save them with an anonymous coder ID.
 \end{itemize}
@@
 	\end{itemize}
-It can also be both. If you think it's neither, that's ok, but please indicate why in the comment box (we haven't encountered that case yet).
+Some remarks:
+\begin{itemize}
+	\item It can also be both or neither.
+	\item The drawings usually make this easy. A cognitive or software patent usually has flow charts while a manual machine usually has drawings of a physical machine or a plan of electronic circuits.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}\frametitle{The column ``Highly uncertain"}
+\begin{itemize}
+	\item If you're highly doubtful if you made the right decision, please enter 1 into the column ``Highly uncertain". If you're sure, you don't need to enter a 0.
+	\item Even if your not sure and you write a 1 to "Highly uncertain" please still make the decisions on whether the patent is an automation patent and whether it is manual or cognitive.
+	\item So far, we classified around 9\% of patents that we manually coded as "Highly uncertain".
+\end{itemize}
 \end{frame}
@@
 \begin{table}
-\begin{small}
+\begin{scriptsize}
   \begin{threeparttable}
-     \begin{tabular}{ccccl}
-        \textbf{Patent number} & \textbf{Classification} & \textbf{Cognitive} & \textbf{Manual} & \textbf{Comment}  \tabularnewline
+     \begin{tabular}{cccccl}
+        \textbf{Pat. num.} & \textbf{Classification} & \textbf{Manual} & \textbf{Cognitive} & \textbf{Highly uncertain}  & \textbf{Comment}  \tabularnewline
         \hline
-        8851703	& 0  &  &  &	\tabularnewline
-        7725116 & 	 &  &  &	Technical problem\tabularnewline
-        8975301 & 0	 &  &  &	\tabularnewline
-        4716621 & 1	 & 1 &  &	\tabularnewline
-        4789151 & 0	 &  &  & 	Not sure\tabularnewline
-        4116621 & 1	 & 1 & 1 &	\tabularnewline
-        6785151 & 0	 &  &  & 	\tabularnewline
+        8851703	& 0  &  & &  &	\tabularnewline
+        7725116 & 	 &  & &  &	Technical problem\tabularnewline
+        8975301 & 0	 &  & &  &	\tabularnewline
+        4716621 & 1	 & 1 & & 1 &	\tabularnewline
+        4789151 & 0	 &  &  & & 	Not sure\tabularnewline
+        4116621 & 1	 & 1 & 1 & &	\tabularnewline
+        6785151 & 0	 &  &  & &	\tabularnewline
         \hline
@@
   \end{threeparttable}
-\end{small}
+\end{scriptsize}
 \end{table}
@@
 \texttt{manclass\textunderscore LukasPuettmann\textunderscore 2015-05-11.xlsx}\\[0.3cm]
-		\item and then send it back to us in an email to\\[0.1cm] \hspace{1cm}\href{mailto:lukas.puettmann@uni-bonn.de}{\texttt{lukas.puettmann@uni-bonn.de}}\\[0.1cm]
+		\item and then send it back to us in an email to \href{mailto:katja.mann@uni-bonn.de}{\texttt{katja.mann@uni-bonn.de}} or \href{mailto:lukas.puettmann@uni-bonn.de}{\texttt{lukas.puettmann@uni-bonn.de}}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}\frametitle{Some empirical probabilities}
+So far, the different fields were marked the following frequencies:
+	\begin{itemize}	
+		\item Automation patent: 27\%, of those:
+		\begin{itemize}
+			\item manual: 42\%
+			\item cognitive: 46\%
+			\item both: 12\%
+			\item neither: 0\% (none so far)
+		\end{itemize}
 	\end{itemize}
@@
 	\item \textit{Can I enter something else like ``1?" if I'm not quite sure?}\\[0.1cm]
-	No, please write your remarks in the comment box if you're not sure. 
+	No, please write a ``1" into the field ``Highly uncertain" if you're not sure.
 	\end{itemize}
@@
 We only ask you to classify the patent as an automation patent if you are \textit{reasonably sure} that the patent is an automation patent.
-If you absolutely cannot figure it out, then consider writing that in the comment box.
+If you absolutely cannot figure it out, then mark ``Highly uncertain" or consider writing that in the comment box.
 	\end{itemize}
@@
 	\item \textit{How often do you expect me to use the comment box?}\\[0.1cm]
-	Please only use that box to mark if you encounter any problems or if you are absolutely not sure how to classify the patent.
+	Please only use that box to mark if you encounter any problems, if something is unusual or you think there is another reason to tell us about it.
 	\end{itemize}
@@
 	\item \textit{What if I don't understand what the patent is about?}\\[0.1cm]
-	No problem, just judge if you think this patent might have something to contribute to automation. If you're not at least reasonably sure, please indicate this in the comment box.
+	No problem, just judge if you think this patent might have something to contribute to automation. If you're not at least reasonably sure, please use the filed ``Highly uncertain".
 	\end{itemize}

### 2015-09-02 manual_coding_guidelines/manual_coding_guidelines.tex
Typo and formatting

@@
 \texttt{manclass\textunderscore LukasPuettmann\textunderscore 2015-05-11.xlsx}\\[0.3cm]
-		\item and then send it back to us in an email to \href{mailto:katja.mann@uni-bonn.de}{\texttt{katja.mann@uni-bonn.de}} or \href{mailto:lukas.puettmann@uni-bonn.de}{\texttt{lukas.puettmann@uni-bonn.de}}
+		\item and then send it back to us in an email to \href{mailto:katja.mann@uni-bonn.de}{\textcolor{myred}{\texttt{katja.mann@uni-bonn.de}}} or \href{mailto:lukas.puettmann@uni-bonn.de}{\textcolor{myred}{\texttt{lukas.puettmann@uni-bonn.de}}}
 	\end{itemize}
@@
 \begin{frame}\frametitle{Some empirical probabilities}
-So far, the different fields were marked the following frequencies:
+So far, the different fields were marked with the following frequencies:
 	\begin{itemize}	

### 2015-09-07 make_figures/make_table_yearsstats.m
Make a real link to the algorithm table in the Note section of the year stats.

@@ -65,7 +65,7 @@ fprintf(FID, '\\bottomrule');
 fprintf(FID,'\\end{tabular}\n');
 fprintf(FID,'\\begin{tablenotes}\n');
 fprintf(FID,'\\small\n');
-fprintf(FID,'\\item\\textit{Note:} \\#A: number of automation patents as classified by Algorithm1, \\#P: total number of patents, $^3$: up to 23.03.2015.\n');
+fprintf(FID,'\\item\\textit{Note:} \\#A: number of automation patents as classified by Algorithm~\\ref{alg:baseline_alg1}, \\#P: total number of patents, $^3$: up to 23.03.2015.\n');
 fprintf(FID,'\\item\\textit{Source:} USPTO, Google and own calculations.\n');
 fprintf(FID,'\\end{tablenotes}\n');
 fprintf(FID,'\\end{threeparttable}\n');

### 2015-09-07 manual_classification/classif_alg1.m
..

@@ -1,5 +1,5 @@
 function class_pat = classif_alg1(searchdict, title_matches, ...
-    abstract_matches, body_matches)
+    abstract_matches, body_matches, indic_exclclassnr)
     % Apply Algorithm1 to classify patents as automation patents
     %
     % (Anwhere:) "automat" OR "robot" OR "movable arm" OR "autonomous" OR 
@@ -20,6 +20,8 @@ function class_pat = classif_alg1(searchdict, title_matches, ...
     % Pick those words that contain any of those
     class_pat = max([mat_classif_1, mat_classif_2], [], 2);
 
+    % Exclude all patents with technology numbers that we chose to exclude
+    class_pat( find( indic_exclclassnr) ) = 0;
 end
 
 

### 2015-09-07 run_patentsearch.m

@@ -231,8 +231,8 @@ fyr_end = 2014;
 %% Compare classification with manually coded patents
 
 % Load and prepare the manually classified patents
-manclassData = prepare_manclass('manclass_consolidated_v10.xlsx');
-% manclassData = prepare_manclass('manclass_unseen_eval_alg1.xlsx');
+% manclassData = prepare_manclass('manclass_consolidated_v10.xlsx');
+manclassData = prepare_manclass('manclass_unseen_eval_alg1.xlsx');
 
 % Use patents classified by Bessen and Hunt (2007) 
     % patent: patent number
@@ -269,23 +269,21 @@ computerClass = classify_autom_algorith(automclassData);
 %% Compare manual vs. computer classification of patents
 
 
-break
-
 % Report contingency table for Algorithm1 only
 ix_alg = find( strcmp(computerClass.algorithm_name, 'Algorithm1') );
 classifstat = calculate_manclass_stats(manclassData.manAutomat, ...
     computerClass.compAutomat(:, ix_alg));
 make_contingency_table(classifstat)
 
-copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\table_contingency.tex', ...
-    'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\tables')
+% copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\table_contingency.tex', ...
+%     'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\tables')
 
 make_table_evalstats(classifstat)
 
-copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\table_evalstats.tex', ...
-    'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\tables')
+% copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\table_evalstats.tex', ...
+%     'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\tables')
 
-
+break
 
 compClass_Yes = computerClass.compAutomat(:, ix_alg);
 classifstat_yrly = calculate_classerror_overtime(manclassData, ...

### 2015-09-13 output/table_compare_classalg.tex
Delete description of baseline algorithm 1 in the Note: underneath the table comparing algorithms. We make a separate box describing this algorithm, so that isn't necessary.
There was an error in the footer of the table with the year stats. The 3 on 2015 was outdated.

@@
  & \textbf{Algorithm1} & \textbf{automat} & \textbf{Bessen-Hunt} & \textbf{Always "No"} & \textbf{Always "Yes"}  \tabularnewline 
-Accuracy & 0.78 & 0.78 & 0.77 & 0.73 & 0.27 & & & &  \tabularnewline 
-Precision & 0.57 & 0.58 & 0.62 & NaN & 0.27 & & & &  \tabularnewline 
-Recall & 0.68 & 0.57 & 0.32 & 0.00 & 1.00 & & & &  \tabularnewline 
-F-measure & 0.62 & 0.57 & 0.42 & NaN & 0.42 & & & &  \tabularnewline 
-AUC & 0.75 & 0.71 & 0.63 & 0.50 & 0.50 & & & &  \tabularnewline 
-MCC & 0.47 & 0.42 & 0.32 & NaN & NaN & & & &  \tabularnewline 
-Number "Yes" & 176 & 147 & 77 & 0 & 560 & & & &  \tabularnewline 
+Accuracy & 0.80 & 0.78 & 0.77 & 0.73 & 0.27 & & & &  \tabularnewline 
+Precision & 0.62 & 0.58 & 0.62 & NaN & 0.27 & & & &  \tabularnewline 
+Recall & 0.67 & 0.57 & 0.32 & 0.00 & 1.00 & & & &  \tabularnewline 
+F-measure & 0.64 & 0.57 & 0.42 & NaN & 0.42 & & & &  \tabularnewline 
+AUC & 0.76 & 0.71 & 0.63 & 0.50 & 0.50 & & & &  \tabularnewline 
+MCC & 0.51 & 0.42 & 0.32 & NaN & NaN & & & &  \tabularnewline 
+Number "Yes" & 162 & 147 & 77 & 0 & 560 & & & &  \tabularnewline 
 \bottomrule 
@@
 \small
-\item\textit{Note:} Classified as automation patents if at least one match of keywords in all parts of patent.
-\item Algorithm1: (anywhere in patent:) ``automat" OR ``robot" OR ``movable arm" OR ``autonomous" OR  ``adaptive" OR ``self-generat" OR (in title + abstract:) ``detect" OR ``program" OR ``computer".
-\item Bessen-Hunt: (anywhere in patent:) ``software" OR (``computer" AND ``program") ANDNOT ((in title:) ``chip" OR ``semiconductor" OR ``bus" OR ``circuit" OR ``circuitry") ANDNOT ((anwhere in patent:) ``antigen" OR ``antigenic" OR ``chromatography").
+\item\textit{Note:} "automat" classifies all patent as automation patent that include "automat" at least once.\item Bessen-Hunt: (anywhere in patent:) ``software" OR (``computer" AND ``program") ANDNOT ((in title:) ``chip" OR ``semiconductor" OR ``bus" OR ``circuit" OR ``circuitry") ANDNOT ((anwhere in patent:) ``antigen" OR ``antigenic" OR ``chromatography").
 \item F-measure: balanced F-measure which is the evenly weightened harmonic mean between Precision and Recall. 

### 2015-09-13 industry_analysis/subplot_industries_mean_alg1.m

@@ -8,7 +8,7 @@ set(0, 'DefaultTextFontName', 'Palatino')
 set(0, 'DefaultAxesFontName', 'Palatino')
 
 
-color1_pick = [49, 130, 189] ./ 255;
+color1_pick = [0.3, 0.3, 0.3];
 
 
 
@@ -36,9 +36,7 @@ for ix_industry=1:size(industry_sumstats, 1)
     plotseries = nr_alg1 ./ nr_pat; 
     
     subplot(dim_subplot(1), dim_subplot(2), ix_industry)
-    plot(plottime, plotseries, 'Color', color1_pick, 'Marker', 'o', ...
-        'MarkerEdgeColor', color1_pick, 'MarkerFaceColor', color1_pick, ...
-        'MarkerSize', 1.8)
+    plot(plottime, plotseries, 'Color', color1_pick)
     title(industry_name)
     box off
     set(gca,'TickDir','out') 

### 2015-09-13 make_figures/make_table_yearsstats.m

@@ -30,7 +30,7 @@ fprintf(FID,'\\begin{small}\n');
 fprintf(FID,'\\begin{threeparttable}\n');
 fprintf(FID,'\\caption{{\\normalsize Overview of yearly classified patents}}\n');
 fprintf(FID,'\\label{table:table_yearsstats}\n');
-fprintf(FID,'\\begin{tabular}{rrrrrrrrrrrrrr}\n'); 
+fprintf(FID,'\\begin{tabular}{lrrrrlrrrrlrrr}\n'); 
 fprintf(FID,'\\toprule \\addlinespace[0.5em]\n');
 fprintf(FID,' & \\textbf{\\#A} & \\textbf{\\#P} & \\textbf{\\%%} & \\phantom{aaa} & & \\textbf{\\#A} & \\textbf{\\#P} & \\textbf{\\%%} & \\phantom{aaa} & & \\textbf{\\#A} & \\textbf{\\#P} & \\textbf{\\%%}\\tabularnewline[0.1cm]\n');
 fprintf(FID,'\\midrule \\addlinespace[0.5em]\n');
@@ -53,7 +53,7 @@ for t=1:13
         addyear2)*100);
 end
  
-fprintf(FID,'& & & & & & & & & & 2015$^3$ & %d & %d & %3.1f  \\tabularnewline[0.1cm]\n', ...
+fprintf(FID,'& & & & & & & & & & 2015$^*$ & %d & %d & %3.1f  \\tabularnewline[0.1cm]\n', ...
     total_alg1_per_year(end), nr_patents_per_year(end), ...
     total_alg1_per_year(end)/nr_patents_per_year(end)*100);
 fprintf(FID,'& & & & & & & & & & \\textbf{Total} & \\textbf{%d} & \\textbf{%d} & \\textbf{%3.1f} \\tabularnewline[0.1cm]\n', ...
@@ -65,7 +65,7 @@ fprintf(FID, '\\bottomrule');
 fprintf(FID,'\\end{tabular}\n');
 fprintf(FID,'\\begin{tablenotes}\n');
 fprintf(FID,'\\small\n');
-fprintf(FID,'\\item\\textit{Note:} \\#A: number of automation patents as classified by Algorithm~\\ref{alg:baseline_alg1}, \\#P: total number of patents, $^3$: up to 23.03.2015.\n');
[…]

### 2015-09-13 manual_classification/make_table_evalstats.m

@@ -9,7 +9,7 @@ fprintf(FID,'\\begin{tabular}{rl}\n');
 fprintf(FID, '\\rule{0pt}{12pt} Accuracy & $= \\frac{%d + %d}{%d} = %3.2f$  \\tabularnewline\n', classifstat.true_negative, classifstat.true_positive, classifstat.nr_codpt, classifstat.accuracy);
 fprintf(FID, '\\rule{0pt}{12pt} Precision & $= \\frac{%d}{%d} = %3.2f$ \\tabularnewline\n', classifstat.true_positive, classifstat.false_positive + classifstat.true_positive, classifstat.precision);
 fprintf(FID, '\\rule{0pt}{12pt} Recall & $= \\frac{%d}{%d} = %3.2f$  \\tabularnewline\n', classifstat.true_positive, classifstat.false_negative + classifstat.true_positive, classifstat.recall);
-fprintf(FID, '\\rule{0pt}{12pt} $F_1$ measure & $= %3.2f$ \\tabularnewline\n', classifstat.fmeasure);
+fprintf(FID, '\\rule{0pt}{12pt} $F_1$-measure & $= %3.2f$ \\tabularnewline\n', classifstat.fmeasure);
 fprintf(FID, '\\rule{0pt}{12pt} AUROC &$= %3.2f$ \\tabularnewline\n', classifstat.auc);
 fprintf(FID, '\\rule{0pt}{12pt} Matthew''s Corr. Coeff. & $= %3.2f$ \\tabularnewline\n', classifstat.matthewscorrcoeff);
 fprintf(FID,'\\end{tabular}\n');

### 2015-09-15 output/table_compare_classalg.tex
Some typos

@@
 Recall & 0.67 & 0.57 & 0.32 & 0.00 & 1.00 & & & &  \tabularnewline 
-F-measure & 0.64 & 0.57 & 0.42 & NaN & 0.42 & & & &  \tabularnewline 
+$F_1$-measure & 0.64 & 0.57 & 0.42 & NaN & 0.42 & & & &  \tabularnewline 
 AUC & 0.76 & 0.71 & 0.63 & 0.50 & 0.50 & & & &  \tabularnewline 
@@
 \small
-\item\textit{Note:} "automat" classifies all patent as automation patent that include "automat" at least once.\item Bessen-Hunt: (anywhere in patent:) ``software" OR (``computer" AND ``program") ANDNOT ((in title:) ``chip" OR ``semiconductor" OR ``bus" OR ``circuit" OR ``circuitry") ANDNOT ((anwhere in patent:) ``antigen" OR ``antigenic" OR ``chromatography").
-\item F-measure: balanced F-measure which is the evenly weightened harmonic mean between Precision and Recall. 
+\item\textit{Note:} "automat" classifies all patents as automation patent that include "automat" at least once.\item Bessen-Hunt: (anywhere in patent:) ``software" OR (``computer" AND ``program") ANDNOT ((in title:) ``chip" OR ``semiconductor" OR ``bus" OR ``circuit" OR ``circuitry") ANDNOT ((anwhere in patent:) ``antigen" OR ``antigenic" OR ``chromatography").
+\item $F_1$-measure: balanced F-measure which is the evenly weightened harmonic mean between Precision and Recall. 
 \item AUC: Area under (the receiver operating) curve.

### 2015-09-15 manual_classification/make_table_compare_classalg.m

@@ -75,7 +75,7 @@ if nr_rem > 0
         classalg_comparison.precision(split_start:split_end));
     fprintf(FID, ['Recall ', num_restinsert], ...
         classalg_comparison.recall(split_start:split_end));
-    fprintf(FID, ['F-measure ', num_restinsert], ...
+    fprintf(FID, ['$F_1$-measure ', num_restinsert], ...
         classalg_comparison.fmeasure(split_start:split_end));
     fprintf(FID, ['AUC ', num_restinsert], ...
         classalg_comparison.auc(split_start:split_end));
@@ -90,9 +90,9 @@ end
 fprintf(FID,'\\end{tabular} \n');
 fprintf(FID, '\\begin{tablenotes}\n');
 fprintf(FID, '\\small\n');
-fprintf(FID,'\\item\\textit{Note:} "automat" classifies all patent as automation patent that include "automat" at least once.');
+fprintf(FID,'\\item\\textit{Note:} "automat" classifies all patents as automation patent that include "automat" at least once.');
 fprintf(FID,'\\item Bessen-Hunt: (anywhere in patent:) ``software" OR (``computer" AND ``program") ANDNOT ((in title:) ``chip" OR ``semiconductor" OR ``bus" OR ``circuit" OR ``circuitry") ANDNOT ((anwhere in patent:) ``antigen" OR ``antigenic" OR ``chromatography").\n');
-fprintf(FID,'\\item F-measure: balanced F-measure which is the evenly weightened harmonic mean between Precision and Recall. \n');
+fprintf(FID,'\\item $F_1$-measure: balanced F-measure which is the evenly weightened harmonic mean between Precision and Recall. \n');
 fprintf(FID,'\\item AUC: Area under (the receiver operating) curve.\n');
 fprintf(FID,'\\item MCC: Matthew''s correlation coefficient.\n');
 fprintf(FID,'\\item\\textit{Source:} USPTO, Google and own calculations.\n');

### 2015-09-15 run_patentsearch.m

@@ -90,7 +90,7 @@ dim_subplot = [7, 5];
 make_table_yearsstats(year_start, year_end)
 % copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\table_yearsstats.tex', ...
 %     'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\tables')
-break
+
 
 %% Prepare conversion table
 fyr_start = 1976;
@@ -127,17 +127,16 @@ load('pat2ind')
 
 
 
-subplot_industries_alg1(fyr_start, fyr_end, pat2ind.industry_sumstats, ...
-    pat2ind.ind_corresp)
-copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\subplot_industries_alg1.pdf', ...
-    'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\figures')
+% subplot_industries_alg1(fyr_start, fyr_end, pat2ind.industry_sumstats, ...
+%     pat2ind.ind_corresp)
+% copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\subplot_industries_alg1.pdf', ...
+%     'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\figures')
+% 
+% subplot_industries_mean_alg1(fyr_start, fyr_end, pat2ind.industry_sumstats, ...
+%     pat2ind.ind_corresp)
+% copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\subplot_industries_mean_alg1.pdf', ...
+%     'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\figures')
 
-subplot_industries_mean_alg1(fyr_start, fyr_end, pat2ind.industry_sumstats, ...
-    pat2ind.ind_corresp)
-copyfile('D:\Dropbox\0_Lukas\econ\projects\PatentSearch_Automation\patent-automat\output\subplot_industries_mean_alg1.pdf', ...
-    'D:\Dropbox\MannPuettmann\2_writing\paper-patent-automat\figures')
-
-break
 
 % idata = extract_idata(fyr_start, fyr_end, pat2ind.ind_corresp(:, 1));
 % check_idata(idata)
@@ -282,8 +281,8 @@ make_contingency_table(classifstat)
 
 make_table_evalstats(classifstat)
 
[…]

### 2015-10-23 manual_coding_guidelines/manual_coding_guidelines.tex
Include Michael Böhm's comments in manual coding guidelines
Typo

@@
 	\begin{itemize}	
-	\item We study all U.S. utility patents 1976-2015.
+	\item We study all U.S. patents 1976-2015. 
+	\item We only look at *utility patents* which are what we normally think of as patents. Other types of patents we exclude are design patents or plant patents.
 	\item We randomly pick an equal number of patents from all years.
-	\item Every patent is reviewed by an additional auditor.
+	\item Every patent is reviewed by an additional human auditor.
 	\item The list of patents is given to the auditor in random (not chronological) order.
@@
 			\item parts of machines (e.g. a tube) that does not automate or that is not a part of an automat
-			\item parts of computers or of sofware that does not directly contribute to automation
+			\item parts of computers or of software that does not directly contribute to automation
 			\item highly abstract algorithms (a potential application in automation should be recognizable)

### 2015-10-23 manual_coding_guidelines/manual_coding_guidelines.tex
Parenthesis

@@
 	\item If you're highly doubtful if you made the right decision, please enter 1 into the column ``Highly uncertain". If you're sure, you don't need to enter a 0.
-	\item Even if your not sure and you write a 1 to "Highly uncertain" please still make the decisions on whether the patent is an automation patent and whether it is manual or cognitive.
-	\item So far, we classified around 9\% of patents that we manually coded as "Highly uncertain".
+	\item Even if your not sure and you write a 1 to ``ighly uncertain" please still make the decisions on whether the patent is an automation patent and whether it is manual or cognitive.
+	\item So far, we classified around 9\% of patents that we manually coded as ``Highly uncertain".
 \end{itemize}

### 2015-11-25 conversion_ipc2sic/plot_automix_vs_rti.m
..

@@ -1,0 +1,86 @@
+function plot_automix_vs_rti(year_start, year_end, sic_summary)
+
+pick_series1 = sic_summary.automix_use_log_sum;
+pick_series2 = sic_summary.rti60;
+pick_series3 = sic_summary.rel_automix_mean;
+
+ix_color = find( sic_summary.ix_manufact );
+
+
+plot_settings_global()
+
+figureHandle = figure;
+
+set(gca,'FontSize', 16) % change default font size of axis labels
+set(gcf, 'Color', 'w');
+box off
+
+subplot(2, 2, 1)
+scatter(pick_series1, pick_series2, ...
+    'Marker', '.', 'MarkerEdgeColor', [0.6, 0.6, 0.6])
+
+hold on
+ylabel('Share of routine labor 1960')
+xlabel('log( total automation index )')
+set(gca,'TickDir','out')
+ylim([0, 1])
+
+subplot(2, 2, 2)
+scatter(pick_series3( not( ix_color ) ), ...
+    pick_series2( not( ix_color ) ), ...
+    'Marker', '.', 'MarkerEdgeColor', color_list(8,:))
+hold on
+scatter(pick_series3(ix_color), pick_series2(ix_color), ...
+    'Marker', '.', 'MarkerEdgeColor', color_list(5,:))
+hold on
+xpush = linspace(0, 1, 100);
+mdl = fitlm(pick_series3(ix_color), ...
+    pick_series2(ix_color));
+plot(xpush, mdl.Coefficients{1,1} + xpush * mdl.Coefficients{2,1}, ...
+    'LineWidth', 1.5, 'Color', color_list(4,:));
+
+ylabel('Share of routine labor 1960')
+xlabel('Relative automation index')
+set(gca,'TickDir','out')
+xlim([0, 1])
+ylim([0, 1])
+
+subplot(2, 2, 3)
+scatter(pick_series3( not( ix_color ) ), ...
+    pick_series2( not( ix_color ) ), ...
+    'Marker', '.', 'MarkerEdgeColor', color_list(8,:))
+title('Not manufacturing')
+
+ylabel('Share of routine labor 1960')
+xlabel('Relative automation index')
+set(gca,'TickDir','out')
+ylim([0, 1])
+
+subplot(2, 2, 4)
+scatter(pick_series3(ix_color), ...
+    pick_series2(ix_color), ...
+    'Marker', '.', 'MarkerEdgeColor', color_list(5,:))
+title('Manufacturing')
+
+ylabel('Share of routine labor 1960')
[…]

### 2015-11-25 manual_classification/make_table_evalstats.m

@@ -12,5 +12,6 @@ fprintf(FID, '\\rule{0pt}{12pt} Recall & $= \\frac{%d}{%d} = %3.2f$  \\tabularne
 fprintf(FID, '\\rule{0pt}{12pt} $F_1$-measure & $= %3.2f$ \\tabularnewline\n', classifstat.fmeasure);
 fprintf(FID, '\\rule{0pt}{12pt} AUROC &$= %3.2f$ \\tabularnewline\n', classifstat.auc);
 fprintf(FID, '\\rule{0pt}{12pt} Matthew''s Corr. Coeff. & $= %3.2f$ \\tabularnewline\n', classifstat.matthewscorrcoeff);
+fprintf(FID, '\\rule{0pt}{12pt} Cohen''s $\\kappa$ & $= %3.2f$ \\tabularnewline\n', classifstat.cohenskappa);
 fprintf(FID,'\\end{tabular}\n');
 fclose(FID); 

### 2015-11-25 manual_classification/plot_classifstat_yrly.m

@@ -94,12 +94,12 @@ ygrid_lines(find(ygrid_lines==yLimits(1))) = []; % remove bottom grid line
 handle_ygrid = gridxy([], ygrid_lines, 'Color', my_gray , 'linewidth', grid_linewidth);
 
 subplot(3,1,3)
-% plot(plottime, repmat(classifstat.accuracy, size(plottime)), ...
-%     '-', 'Color', color4_pick, 'LineWidth', 1)
-% hold on
 plot(plottime, classifstat_yrly.accuracy, 'Color', color4_pick, ...
     'Linewidth', lwidth)
-titleHandle = title('(c) Accuracy', 'FontWeight', 'bold');
+hold on
+plot(plottime, classifstat_yrly.fmeasure, 'Color', color2_pick, ...
+    'Linewidth', lwidth)
+titleHandle = title('(c) Evaluation statistics over time', 'FontWeight', 'bold');
 
 set(titleHandle, 'horizontalAlignment', 'left')
 set(titleHandle, 'units', 'normalized')
@@ -171,6 +171,21 @@ annotation(figureHandle, 'textarrow', [0.544822598567307 0.536669542709233],...
     'Color', color2_pick, ...
     'FontSize', 10);
 
+annotation(figureHandle,'textarrow',[0.829936305732484 0.821656050955414],...
+    [0.326691871455579 0.310018903591683],'TextEdgeColor','none',...
+    'HorizontalAlignment','left',...
+    'String','Accuracy',...
+    'HeadStyle','none',...
+    'FontSize', 10, ...
+    'Color', color4_pick);
+
+annotation(figureHandle,'textarrow',[0.750955414012738 0.723566878980892],...
+    [0.190964083175806 0.245746691871456],'TextEdgeColor','none',...
+    'HorizontalAlignment','left',...
+    'String','F1-measure',...
+    'HeadStyle','none',...
+    'FontSize', 10, ...
+    'Color', color2_pick);
 
 
 % Export to pdf

### 2015-11-25 run_patentsearch.m

@@ -105,21 +105,14 @@ year_end = 2015;
 % %   - usefrq: frequency of patents in IPC assigned to SIC of use
 % ipcsicfinalv5.Properties.VariableNames = {'ipc', 'sic', 'mfgfrq', 'usefrq'};
 % 
-% AA = unique( ipcsicfinalv5.ipc );
-
-
 % construct_sic_automix(years, ipcsicfinalv5)
 
 
-% %% Compile SIC automatix
+%% Compile SIC automatix
 % sic_automix_allyears = compile_sic_automix_table(year_start, year_end);
 % 
 % savename = 'output/sic_automix_allyears.mat';
 % save(savename, 'sic_automix_allyears')
-% fprintf('Saved: %s.\n', savename)
-% 
-% savename = 'output/sic_automix_allyears.csv';
-% writetable(sic_automix_allyears, savename)
 % fprintf('Saved: %s.\n', savename)
 
 
@@ -127,44 +120,25 @@ year_end = 2015;
 % ========================================================================
 load('output/sic_automix_allyears.mat')
 
-sic_automix_allyears.overcat = assign_sic_overcategories( ....
-    sic_automix_allyears.sic);
+% Get some summary series for over-categories of industries
+% [sic_overcategories, aggr_automix, aggr_automix_share] = ...
+%     get_sic_ocat_automix_data(year_start, year_end, sic_automix_allyears);
 
-sic_overcategories = define_sic_overcategories();
-
-for ix_year=year_start:year_end
-    t = ix_year - year_start + 1;    
-    
-    year_data = sic_automix_allyears( find( sic_automix_allyears.year ...
-        == ix_year ), :);
-    
-    for i=1:length(sic_overcategories.letter)
-        pick_sic_overcat = sic_overcategories.letter{i};
-
-        find_ix = find( strcmp( year_data.overcat, ...
-            pick_sic_overcat) );
-        aggr_automix(t, i) = nansum( year_data.automix_use(find_ix));
-        
-        aggr_automix_share(t, i) = nanmean( year_data.automix_use(find_ix) ./ ...
-            year_data.patents_use(find_ix));
-    end
-end
 
 
 %%
-close all
 
 % Sort the series for plotting
[…]
